### 2018-11-02 paper.Rmd
Initial commit

---
title: |
  |
  | 
  | \vspace{1cm}Writing a reproducible paper
  | in R Markdown*^[*Corresponding address: mail@paulcbauer.eu. Acknowledgments: I am grateful to all those generous people that invest their time into open-source software.]\vspace{0.5cm}
  |
author: |
  | Paul C. Bauer
  | Mannheim Centre for European Social Research
date: |
  |       
  |
  | `r gsub("^0", "", format(Sys.time(), "%d %B, %Y"))`
  |
  | Feedback? 
  | mail@paulcbauer.eu
  |
linestretch: 1.2
colorlinks: true
abstract: \noindent\setstretch{1}The present paper provides a template for a reproducable scientific paper written in R Markdown. Below I outline some of the "tricks"/code (e.g., referencing tables, sections etc.) I had to figure out to produce this document. The underlying files which produce this document can be downloaded [here](https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing). I think I got pretty far but there is always room for improvement and more automatization, in parallel to the incredible developments in R and Rstudio (bookdown etc.). My last paper is almost entirely based on R Markdown [see @Bauer2018-hd and [reproduction files](https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/DUMGLT)]. I intend to update this file when I discover more convenient code.\vspace{.8cm}
bibliography: references.bib
csl: american-sociological-association.csl
output: 
  bookdown::pdf_document2:
    includes:
      in_header: header.tex
    toc: no
    keep_tex: true
mainfont: Times New Roman
sansfont: Times New Roman
fontsize: 12pt
link-citations: true
documentclass: article
geometry: margin=1in
always_allow_html: yes
header-includes:
   - \usepackage{dcolumn}
   - \usepackage{color}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = FALSE)
# Use chache = TRUE if you want to speed up compilation

# A function to allow for showing some of the inline code
rinline <- function(code){
  html <- '<code  class="r">``` `r CODE` ```</code>'
  sub("CODE", code, html)
}
```

\clearpage

\renewcommand{\baselinestretch}{0.5}\normalsize
\tableofcontents
\renewcommand{\baselinestretch}{1.1}\normalsize

\clearpage

# Why reproducible research (in R)?
Some arguments...

* **Access**: Research is normally funded by taxpayers (researchers are also taxpayers). Hence, it should be freely accessible to everyone without any barriers, e.g., without requiring commercial software. Importantly, researchers from developing countries are even more dependent on free access to knowledge [@Kirsop2005-ro].
* **Reproducability**: Even if you have written a study and analyzed the data yourself you will forget what you did after a few months. A fully reproducable setup will help you to trace back your own steps. Obviously, the same is true for other researchers who may want to understand your work and built on it. It may sound like a joke but why not aim for a document that can be used to reproduce your findings in in 500 years. 
* **Errors**: Manual steps in data analysis (e.g., manually copy/pasting values into a table etc.) may introduce errors. R Markdown allows you to **automatize** such steps and/or avoid them.
* **Revisions**: Revising a paper takes much less time if you have all the code you need in one place, i.e., one `.rmd` file. For instance, if you decide to exclude a subset of your data you simply need to insert one line of your code at the beginning and everything is rebuilt/re-estimated automatically.

# Prerequesites
I assume that you are using R on a day-to-day basis. You may have even started to work a little in R Markdown but you don't write your complete paper in R Markdown. If you don't know what R Markdown is watch [this short video](https://vimeo.com/178485416). Then...

* ...install [R](https://www.r-project.org/) and [Rstudio](https://www.rstudio.com/) (most recent versions) [@R2017; @Rstudio2015].
* ...install [tinytex](https://yihui.name/tinytex/), a lightweight version of Tex Live [@markdown2017; @tinytex].
```{r eval=FALSE, include=TRUE}
install.packages(c('tinytex', 'rmarkdown'))
tinytex::install_tinytex()
```
* ...install the packages below using the code below [@bookdown1; @bookdown2; @knitr1; @knitr2; @knitr3; @kableextra; @plotly].
```{r eval=FALSE, include=TRUE}
install.packages(c("rmarkdown", "knitr", "kableExtra",
                   "stargazer", "plotly", "knitr",
                   "bookdown"))
```
* ...download the 4 input files I created (see below) from [this folder](https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing).

* ...learn R and read about the other underlying components namely [Markdown](https://en.wikipedia.org/wiki/Markdown), [R Markdown](https://rmarkdown.rstudio.com/lesson-1.html) and [Latex](https://en.wikipedia.org/wiki/LaTeX).

# Basics: Input and output files
All the files you need to produce the present PDF file are 4 input files...

* ...a `paper.rmd` file (the underlying R Markdown file).
* ...a `header.tex` file (a tex file for document structure).
* ...a `references.bib` file (the bibliography).
    + I use paperpile to manage my references and export the `.bib` file into the folder that contains my `.rmd` file.
* ...a `data.csv` file (some raw data).
* ... a `american-sociological-association.csl` file that defines the style of your bibliography.^[You can download various citation style files from this webpage: https://github.com/citation-style-language/styles.]

[Download these files](https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing) and save them into a folder. Close R/Rstudio and directly open `paper.rmd` with RStudio. Doing so assures that the working directory is set to the folder that contains `paper.rmd` and the other files.^[You can always check your working directory in R with `getwd()`.]

Once you run/compile the `paper.rmd` file in Rstudio it creates mainly two output files:

* `paper.tex`
* `paper.pdf` (the one you are reading right now)

In addition, there may be files that you generate and store locally in the folder during the compilation process. This is the case for some of the Plotly graphs below.

Ideally, we can simply provide others with a `zip` folder that contains both our input files and our output files. Then it's possible to reproduce the process from managing/analyzing some raw data to producing the final scientific article.

Below we always display the R code in the chunks that produce the output. In your paper you will normally only present outputs (e.g., tables, figures etc.) by choosing the chunk option "Show output only" in R Studio. The chunk commands itself are not displayed but they do matter for referencing etc. So simply orient yourself at the underlying `paper.rmd` file.

# Referencing within your document

To see how referencing works simply see the different examples for figures, tables and sections below. For instance in Section \@ref(sec:tables) you can find different ways of referencing tables. The code of the underlying `paper.rmd` will show you how I referenced Section \@ref(sec:tables) right here namely with '`Section \@ref(sec:tables)`'.

# Software versioning
Software changes and gets updated, especially with an active developer community like that of R. Luckily you can always access [old versions of R](https://cran.r-project.org/bin/windows/base/old/) and old version of R packages in [the archive](https://cran.r-project.org/src/contrib/Archive/). In the archive you need to choose a particular package, e.g dplyr and search for the right version, e.g., `dplyr_0.2.tar.gz`. Then insert the path in the following function: `install.packages("https://....../dplyr_0.2.tar.gz", repos=NULL, type="source")`. Ideally, however, results will be simply reproducible in the most current R and package versions.

I would recommend to use the command below and copy/paste the output into the first R chunk in your `paper.rmd` file. Normally we would do this when we compile/generate the paper for the last time. For more advanced tools see [packrat](https://rstudio.github.io/packrat/).

```{r fig-versioning, echo=TRUE}
cat(paste("#", capture.output(sessionInfo()), "\n", collapse ="")) 
  # or use message() instead of cat()
```

# Data
## Import
```{r, echo=TRUE}
data <- read.csv("data.csv")
head(data)
```

## Putting your entire data into the .rmd file
Applying the function `dput()` to an object gives you the code needed to reproduce that object. So you could paste that code into your `.rmd` file if you don't want to have extra data files. This makes sense were data files are small.

```{r}
dput(data)
```

You can then insert the dput output in your `.rmd` as below.

```{r eval=FALSE, include=TRUE}
data <- structure(list(X = 1:50, speed = c(4L, 4L, 7L, 7L, 8L, 9L, 10L, 
10L, 10L, 11L, 11L, 12L, 12L, 12L, 12L, 13L, 13L, 13L, 13L, 14L, 
14L, 14L, 14L, 15L, 15L, 15L, 16L, 16L, 17L, 17L, 17L, 18L, 18L, 
18L, 18L, 19L, 19L, 19L, 20L, 20L, 20L, 20L, 20L, 22L, 23L, 24L, 
24L, 24L, 24L, 25L), dist = c(2L, 10L, 4L, 22L, 16L, 10L, 18L, 
26L, 34L, 17L, 28L, 14L, 20L, 24L, 28L, 26L, 34L, 34L, 46L, 26L, 
36L, 60L, 80L, 20L, 26L, 54L, 32L, 40L, 32L, 40L, 50L, 42L, 56L, 
76L, 84L, 36L, 46L, 68L, 32L, 48L, 52L, 56L, 64L, 66L, 54L, 70L, 
92L, 93L, 120L, 85L)), 
class = "data.frame", row.names = c(NA, 
-50L))
```

# Tables {#sec:tables}
Producing good tables and referencing these tables within a R Markdown PDF has been a hassle but got much better. Examples that you may use are shown below. The way you reference tables is slightly different, e.g., for `stargazer` the label is contained in the function, for `kable` it's contained in the chunk name.

## stargazer(): Summary and regression tables

Table \@ref(tab-summarystats) shows summary stats of your data. I normally use `stargazer()` [@hlavac2013stargazer] which offers extreme flexibility regarding table output (see `?stargazer`).

```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE, results="asis"}
library(stargazer)
stargazer(cars, 
          title = "Summary table with stargazer",
          label="tab-summarystats", 
          table.placement = "H", 
          header=FALSE)
```

Table \@ref(tab-regression) shows the output for a regression table. Make sure you name all your models and explicitly refer to model names (M1, M2 etc.) in the text.

```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE, results="asis"}
library(stargazer)
model1 <- lm(speed ~ dist, data = cars)
model2 <- lm(speed ~ dist, data = cars)
model3 <- lm(dist ~ speed, data = cars)
stargazer(model1, model2, model3,
          title = "Regression table with stargazer",
          label="tab-regression", 
          table.placement = "H", 
          column.labels = c("M1", "M2", "M3"),
          model.numbers = FALSE,
          header=FALSE)
```

## kable() and kable_styling()

Another great function is `kable()` (`knitr` package) in combination with `kableExtra`. Table \@ref(tab:tab-kabletable) provides an example. Again you can modify so many things in both the `kable()` and the `kable_styling()` function. See [this overview](https://haozhu233.github.io/kableExtra/awesome_table_in_pdf.pdf) of all the kable stylings that are possible provided by the package author himself.

```{r tab-kabletable, echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE, results="asis"}
library(knitr)
library(kableExtra)
kable(cars[1:10,], row.names = TRUE, caption = 'Table with kable() and kablestyling()', 
      format = "latex", booktabs = T) %>%
        kable_styling(full_width = T, 
                      latex_options = c("striped", 
                                        "scale_down",
                                        "HOLD_position"),
                      font_size = 10)
```

# Inline code & results
Reproduction reaches new heights when you work with inline code. For instance, you can automatize the display of certain coefficients within the text. An example is to include estimates, e.g., the coefficient of `dist` of the model we ran above. `r rinline("round(coef(model1)[2], 2)")` will insert the coefficient as follows: `r round(coef(model1)[2], 2)`. Or `r rinline("3 + 7")` will insert a `r 3 + 7` in the text.      
Inline code/results that depend on earlier objects in your document will automatically be updated once you change those objects. For instance, imagine a reviewer asks you to omit certain observations from your sample. You can simply do so in the beginning of your code and push play subsequently.. at time you might have to set `cache = FALSE` at the beginning so that all the code chungs are rerun.    
Researchers often avoid referring to results intext etc. because you easily forget to change them when revising a manuscript. At the same it can make an article much more informative and easier to read, e.g., if you discuss a coefficient in the text you can directly show it in the section in which you discuss it. Inline code allows you to do just that. R Markdown allows you to that do so in a reproducible and automatized manner.

# Figures

## R base graphs
Inserting figures can be slightly more complicated. Ideally, we would produce and insert them directly in the `.rmd` file. It's relatively simple to insert R base graphs as you can see in Figure \@ref(fig:fig-1).

```{r fig-1, fig.align="center", fig.cap="Scatterplot of Speed and Distance", fig.pos="H", message=FALSE, warning=FALSE, paged.print=FALSE}
plot(cars$speed, cars$dist)
```

But it turns out that it doesn't always work so well.

## ggplot2 graphs
Same is true for ggplot2 as you can see in Figure \@ref(fig:fig-2).

```{r fig-2, fig.align="center", fig.cap="Miles per gallon according to the weight", fig.pos="H", fig.width=6, fig.height=3, message=FALSE, warning=FALSE, paged.print=FALSE}
mtcars$cyl <- as.factor(mtcars$cyl) # Convert cyl to factor
library(ggplot2)
ggplot(mtcars, aes(x=wt, y=mpg, shape=cyl)) + geom_point() +
  labs(x="Weight (lb/1000)", y = "Miles/(US) gallon", 
       shape="Number of \n Cylinders") + theme_classic()
```

## Plotly graphs
Plotly is a popular graph engine that let's you also produce interactive graphs that you can embed in html webpages or documents (e.g., see [here](https://paulcbauer.shinyapps.io/visualizing-causal-scenarios/)). I am a big fan, however, right now there is no easy, automatic way to insert high resolution Plotly graphs into your R Markdown PDF. See Figure \@ref(fig:fig-3) below.      
There seems to be a new engine for exporting graphs locally without relying on the plotly server --- which you wanna avoid for a properly reproducible PDF --- called orca (`?orca`). However, the [installation](https://github.com/plotly/orca#installation) is too challenging for the average user at the moment.

```{r fig-3, fig.align="center", fig.cap="Scatterplot of Speed and Distance", fig.pos="H", message=FALSE, warning=FALSE}
library(plotly)
plot_ly(cars, type = "scatter", mode="markers",
        x=~speed, 
        y=~dist)
```

# Good practices
Every researcher has his own optimized setup. Currently I would recommend the following:

* Keep all files of your project (that matter for producing the PDF) in one folder without subfolders. You can zip and directly upload that folder to the [Harvard dataverse](https://dataverse.harvard.edu/)).
* Make sure that filenames have a logic to them.
    + Main file with text/code: "paper.rmd", "report.rmd" 
    + Data files: "data_xxxxxx.*"
    + Image files: "fig_xxxxxx.*"
    + Tables files: "table_xxxx.*"
    + etc.
    + Ideally, your filenames will correspond to the names in the paper. For instance, Figure 1 in the paper may have a corresponding file called `fig_1_xxxxx.pdf`.
* Use document the document outline in R studio (Ctrl + Shift + O) when you work with R Markdown.
* Name rchunks according to what they do or produce:
    + "`fig-...`" for chunks producing figures
    + "`table-...`" for chunks producing tables
    + "`model-...`" for chunks producing model estimates
    + "`import-...`" for chunks importing data
    + "`recoding-...`" for chunks in which data is recoded
* Use "really" informative variable names:
    + Q: What do you think does the variable *trstep* measure? It actually measures trust in the European parliament. 
        + How could we call this variable instead? Yes, `trust.european.parliament` which is longer but will probably be understood by one of your descendants in 100 years.
    + If your setup is truly reproducible you will probably re-use the variable names that you generate as variable names in the tables you produce. Hence, there is an incentive to use good names.
* Use unique identifiers in the final document:
    + e.g., name the models you estimate "M1", "M2" etc.
    + These unique names should also appear in the published paper.
    + Think of someone who wants to produce Figure 1/Model 1 in your paper but doesn't find it in your code...

# Citation styles
If your study needs to follow a particular citation style, you can set the corresponding style in the header of your `.rmd` document. To do so you have to download the corresponding `.csl` file.

In the present document we use the style of the American Sociological Association and set it in the preamble with `csl: american-sociological-association.csl`. However, you also need to download the respective `.csl` file from the following github page: https://github.com/citation-style-language/styles and copy it into your working directory for it to work.

The github directory contains a wide variety of citation style files depending on what discipline your work in.

# Appendix

## All the code in the paper

To simply attach all the code you used in the PDF file in the appendix see the R chunk in the underlying `.rmd` file:

```{r, ref.label=knitr::all_labels(),echo=TRUE,eval=FALSE}
```

# References

### 2018-11-02 paper.tex
Initial commit

\documentclass[12pt,]{article}
\usepackage{lmodern}
\usepackage{setspace}
\setstretch{1.2}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
    \setmainfont[]{Times New Roman}
    \setsansfont[]{Times New Roman}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref
\hypersetup{unicode=true,
            colorlinks=true,
            linkcolor=Maroon,
            citecolor=Blue,
            urlcolor=Blue,
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\usepackage{longtable,booktabs}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

%%% Change title format to be more compact
\usepackage{titling}

% Create subtitle command for use in maketitle
\newcommand{\subtitle}[1]{
  \posttitle{
    \begin{center}\large#1\end{center}
    }
}

\setlength{\droptitle}{-2em}

  \title{\vspace{1cm}Writing a reproducible paper\\
in R Markdown*\footnote{*Corresponding address:
  \href{mailto:mail@paulcbauer.eu}{\nolinkurl{mail@paulcbauer.eu}}.
  Acknowledgments: I am grateful to all those generous people that
  invest their time into open-source software.}\vspace{0.5cm}\\}
    \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
    \author{Paul C. Bauer\\
Mannheim Centre for European Social Research}
    \preauthor{\centering\large\emph}
  \postauthor{\par}
      \predate{\centering\large\emph}
  \postdate{\par}
    \date{2 November, 2018\\[2\baselineskip]Feedback?\\
\href{mailto:mail@paulcbauer.eu}{\nolinkurl{mail@paulcbauer.eu}}\\}

\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage{float}
\usepackage{lmodern}
\usepackage{graphicx}
\usepackage{url}
\usepackage{array}
\usepackage{setspace}
\usepackage{graphics}
%\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{longtable}
\usepackage{natbib}
\usepackage{pdflscape}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{fullpage}
\usepackage{multicol}
\usepackage{dcolumn}
\usepackage{lscape}
\usepackage{array}
\usepackage{color}
\usepackage{setspace}

\usepackage{cleveref}[2012/02/15]
\usepackage{fullpage}
\usepackage[charter]{mathdesign}
\usepackage{bm}
\usepackage{tabu}
\usepackage{wrapfig}

\crefformat{footnote}{#2\footnotemark[#1]#3}
\usepackage{color}
\usepackage{hyperref}

\newenvironment{tightcenter}{%
  \setlength\topsep{0pt}
  \setlength\parskip{0pt}
  \begin{center}
}{%
  \end{center}
}

%\setstretch{1.1}
% Dutch style of paragraph formatting
\parskip 5pt
\makeatletter
% Separation between lines
\doublerulesep 1pt

\usepackage[table]{xcolor}

\definecolor{lightred}{rgb}{0.7,0,0}
\definecolor{darkgreen}{rgb}{0,0.8,0}
\definecolor{lightblue}{rgb}{0,0,0.7}

\hypersetup{colorlinks,
  linkcolor = lightred,
  filecolor = lightred,
  urlcolor = lightblue,
  citecolor = lightred}

% Spaces in bibliography
\let\oldthebibliography=\thebibliography
\let\endoldthebibliography=\endthebibliography
\renewenvironment{thebibliography}[1]{%
  \begin{oldthebibliography}{#1}%
    \setlength{\parskip}{0ex}%
    \setlength{\itemsep}{0.1ex}%
  }%
  {%
  \end{oldthebibliography}%
}

\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

\setlength{\parindent}{0pt} % no indentation
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage[table]{xcolor}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}

\usepackage{dcolumn}
\usepackage{color}

\usepackage{amsthm}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\newtheorem{corollary}{Corollary}[section]
\newtheorem{proposition}{Proposition}[section]
\theoremstyle{definition}
\newtheorem{example}{Example}[section]
\theoremstyle{definition}
\newtheorem{exercise}{Exercise}[section]
\theoremstyle{remark}
\newtheorem*{remark}{Remark}
\newtheorem*{solution}{Solution}
\begin{document}
\maketitle
\begin{abstract}
\noindent\setstretch{1}The present paper provides a template for a
reproducable scientific paper written in R Markdown. Below I outline
some of the ``tricks''/code (e.g., referencing tables, sections etc.) I
had to figure out to produce this document. The underlying files which
produce this document can be downloaded
\href{https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing}{here}.
I think I got pretty far but there is always room for improvement and
more automatization, in parallel to the incredible developments in R and
Rstudio (bookdown etc.). My last paper is almost entirely based on R
Markdown (see Bauer \protect\hyperlink{ref-Bauer2018-hd}{2018} and
\href{https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/DUMGLT}{reproduction
files}). I intend to update this file when I discover more convenient
code.\vspace{.8cm}
\end{abstract}

\clearpage

\renewcommand{\baselinestretch}{0.5}

\normalsize
\tableofcontents
\renewcommand{\baselinestretch}{1.1}\normalsize

\clearpage

\section{Why reproducible research (in
R)?}\label{why-reproducible-research-in-r}

Some arguments\ldots{}

\begin{itemize}
\tightlist
\item
  \textbf{Access}: Research is normally funded by taxpayers (researchers
  are also taxpayers). Hence, it should be freely accessible to everyone
  without any barriers, e.g., without requiring commercial software.
  Importantly, researchers from developing countries are even more
  dependent on free access to knowledge (Kirsop and Chan
  \protect\hyperlink{ref-Kirsop2005-ro}{2005}).
\item
  \textbf{Reproducability}: Even if you have written a study and
  analyzed the data yourself you will forget what you did after a few
  months. A fully reproducable setup will help you to trace back your
  own steps. Obviously, the same is true for other researchers who may
  want to understand your work and built on it. It may sound like a joke
  but why not aim for reproducability in 500 years.
\item
  \textbf{Errors}: Manual steps in data analysis (e.g., manually
  copy/pasting values into a table etc.) may introduce errors. R
  Markdown allows you to \textbf{automatize} such steps and/or avoid
  them.
\item
  \textbf{Revisions}: Revising a paper takes much less time, if you have
  all the code you need in one place, i.e., one \texttt{.rmd} file. For
  instance, if you decide to exclude a subset of your data you simply
  need to insert one line of your code at the beginning and everything
  is rebuilt/re-estimated automatically.
\end{itemize}

\section{Prerequesites}\label{prerequesites}

I assume that you are using R on a day-to-day basis. You may have even
started to work a little in R Markdown but you don't write your complete
paper in R Markdown. If you don't know what R Markdown is watch
\href{https://vimeo.com/178485416}{this short video}. Then\ldots{}

\begin{itemize}
\tightlist
\item
  \ldots{}install \href{https://www.r-project.org/}{R} and
  \href{https://www.rstudio.com/}{Rstudio} (most recent versions) (R
  Core Team \protect\hyperlink{ref-R2017}{2017}; RStudio Team
  \protect\hyperlink{ref-Rstudio2015}{2015}).
\item
  \ldots{}install \href{https://yihui.name/tinytex/}{tinytex}, a
  lightweight version of Tex Live (Allaire et al.
  \protect\hyperlink{ref-markdown2017}{2017}; Xie
  \protect\hyperlink{ref-tinytex}{2018}\protect\hyperlink{ref-tinytex}{b}).
\end{itemize}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{install.packages}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{'tinytex'}\NormalTok{, }\StringTok{'rmarkdown'}\NormalTok{))}
\NormalTok{tinytex}\OperatorTok{::}\KeywordTok{install_tinytex}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\begin{itemize}
\tightlist
\item
  \ldots{}install the packages below using the code below (Sievert et
  al. \protect\hyperlink{ref-plotly}{2017}; Xie
  \protect\hyperlink{ref-knitr3}{2014},
  \protect\hyperlink{ref-knitr2}{2015},
  \protect\hyperlink{ref-bookdown2}{2016},
  \protect\hyperlink{ref-bookdown1}{2017},
  \protect\hyperlink{ref-knitr1}{2018}\protect\hyperlink{ref-knitr1}{a};
  Zhu \protect\hyperlink{ref-kableextra}{2017}).
\end{itemize}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{install.packages}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"rmarkdown"}\NormalTok{, }\StringTok{"knitr"}\NormalTok{, }\StringTok{"kableExtra"}\NormalTok{,}
                   \StringTok{"stargazer"}\NormalTok{, }\StringTok{"plotly"}\NormalTok{, }\StringTok{"knitr"}\NormalTok{,}
                   \StringTok{"bookdown"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\begin{itemize}
\item
  \ldots{}download the 4 input files I created (see below) from
  \href{https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing}{this
  folder}.
\item
  \ldots{}learn R and read about the other underlying components namely
  \href{https://en.wikipedia.org/wiki/Markdown}{Markdown},
  \href{https://rmarkdown.rstudio.com/lesson-1.html}{R Markdown} and
  \href{https://en.wikipedia.org/wiki/LaTeX}{Latex}.
\end{itemize}

\section{Basics: Input and output
files}\label{basics-input-and-output-files}

All the files you need to produce the present PDF file are 4 input
files\ldots{}

\begin{itemize}
\tightlist
\item
  \ldots{}a \texttt{paper.rmd} file (the underlying R Markdown file).
\item
  \ldots{}a \texttt{header.tex} file (a tex file for document
  structure).
\item
  \ldots{}a \texttt{references.bib} file (the bibliography).

  \begin{itemize}
  \tightlist
  \item
    I use paperpile to manage my references and export the \texttt{.bib}
    file into the folder that contains my \texttt{.rmd} file.
  \end{itemize}
\item
  \ldots{}a \texttt{data.csv} file (some raw data).
\item
  \ldots{} a \texttt{american-sociological-association.csl} file that
  defines the style of your bibliography.\footnote{You can download
    various citation style files from this webpage:
    \url{https://github.com/citation-style-language/styles}.}
\end{itemize}

\href{https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing}{Download
these files} and save them into a folder. Close R/Rstudio and directly
open \texttt{paper.rmd} with RStudio. Doing so assures that the working
directory is set to the folder that contains \texttt{paper.rmd} and the
other files.\footnote{You can always check your working directory in R
  with \texttt{getwd()}.}

Once you run/compile the \texttt{paper.rmd} file in Rstudio it creates
mainly two output files:

\begin{itemize}
\tightlist
\item
  \texttt{paper.tex}
\item
  \texttt{paper.pdf} (the one you are reading right now)
\end{itemize}

In addition, there may be files that you generate and store locally in
the folder during the compilation process. This is the case for some of
the Plotly graphs below.

Ideally, we can simply provide others with a \texttt{zip} folder that
contains both our input files and our output files. Then it's possible
to reproduce the process from managing/analyzing some raw data to
producing the final scientific article.

Below we always display the R code in the chunks that produce the
output. In your paper you will normally only present outputs (e.g.,
tables, figures etc.) by choosing the chunk option ``Show output only''
in R Studio. The chunk commands itself are not displayed but they do
matter for referencing etc. So simply orient yourself at the underlying
\texttt{paper.rmd} file.

\section{Referencing within your
document}\label{referencing-within-your-document}

To see how referencing works simply see the different examples for
figures, tables and sections below. For instance in Section
\ref{sec:tables} you can find different ways of referencing tables. The
code of the underlying \texttt{paper.rmd} will show you how I referenced
Section \ref{sec:tables} right here namely with
`\texttt{Section\ \textbackslash{}@ref(sec:tables)}'.

\section{Software versioning}\label{software-versioning}

Software changes and gets updated, especially with an active developer
community like that of R. Luckily you can always access
\href{https://cran.r-project.org/bin/windows/base/old/}{old versions of
R} and old version of R packages in
\href{https://cran.r-project.org/src/contrib/Archive/}{the archive}. In
the archive you need to choose a particular package, e.g dplyr and
search for the right version, e.g., \texttt{dplyr\_0.2.tar.gz}. Then
insert the path in the following function:
\texttt{install.packages("https://....../dplyr\_0.2.tar.gz",\ repos=NULL,\ type="source")}.
Ideally, however, results will be simply reproducible in the most
current R and package versions.

I would recommend to use the command below and copy/paste the output
into the first R chunk in your \texttt{paper.rmd} file. Normally we
would do this when we compile/generate the paper for the last time. For
more advanced tools see
\href{https://rstudio.github.io/packrat/}{packrat}.

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{cat}\NormalTok{(}\KeywordTok{paste}\NormalTok{(}\StringTok{"#"}\NormalTok{, }\KeywordTok{capture.output}\NormalTok{(}\KeywordTok{sessionInfo}\NormalTok{()), }\StringTok{"}\CharTok{\textbackslash{}n}\StringTok{"}\NormalTok{, }\DataTypeTok{collapse =}\StringTok{""}\NormalTok{)) }
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## # R version 3.5.1 (2018-07-02) 
## # Platform: x86_64-w64-mingw32/x64 (64-bit) 
## # Running under: Windows 10 x64 (build 17134) 
## #  
## # Matrix products: default 
## #  
## # locale: 
## # [1] LC_COLLATE=English_Germany.1252  LC_CTYPE=English_Germany.1252    
## # [3] LC_MONETARY=English_Germany.1252 LC_NUMERIC=C                     
## # [5] LC_TIME=English_Germany.1252     
## #  
## # attached base packages: 
## # [1] stats     graphics  grDevices utils     datasets  methods   base      
## #  
## # loaded via a namespace (and not attached): 
## #  [1] compiler_3.5.1  backports_1.1.2 magrittr_1.5    bookdown_0.7    
## #  [5] rprojroot_1.3-2 tools_3.5.1     htmltools_0.3.6 yaml_2.2.0      
## #  [9] Rcpp_0.12.19    stringi_1.1.7   rmarkdown_1.10  knitr_1.20      
## # [13] stringr_1.3.1   xfun_0.3        digest_0.6.18   evaluate_0.12
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
  \CommentTok{# or use message() instead of cat()}
\end{Highlighting}
\end{Shaded}

\section{Data}\label{data}

\subsection{Import}\label{import}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{data <-}\StringTok{ }\KeywordTok{read.csv}\NormalTok{(}\StringTok{"data.csv"}\NormalTok{)}
\KeywordTok{head}\NormalTok{(data)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##   X speed dist
## 1 1     4    2
## 2 2     4   10
## 3 3     7    4
## 4 4     7   22
## 5 5     8   16
## 6 6     9   10
\end{verbatim}

\subsection{Putting your entire data into the .rmd
file}\label{putting-your-entire-data-into-the-.rmd-file}

Applying the function \texttt{dput()} to an object gives you the code
needed to reproduce that object. So you could paste that code into your
\texttt{.rmd} file if you don't want to have extra data files. This
makes sense were data files are small.

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{dput}\NormalTok{(data)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## structure(list(X = 1:50, speed = c(4L, 4L, 7L, 7L, 8L, 9L, 10L, 
## 10L, 10L, 11L, 11L, 12L, 12L, 12L, 12L, 13L, 13L, 13L, 13L, 14L, 
## 14L, 14L, 14L, 15L, 15L, 15L, 16L, 16L, 17L, 17L, 17L, 18L, 18L, 
## 18L, 18L, 19L, 19L, 19L, 20L, 20L, 20L, 20L, 20L, 22L, 23L, 24L, 
## 24L, 24L, 24L, 25L), dist = c(2L, 10L, 4L, 22L, 16L, 10L, 18L, 
## 26L, 34L, 17L, 28L, 14L, 20L, 24L, 28L, 26L, 34L, 34L, 46L, 26L, 
## 36L, 60L, 80L, 20L, 26L, 54L, 32L, 40L, 32L, 40L, 50L, 42L, 56L, 
## 76L, 84L, 36L, 46L, 68L, 32L, 48L, 52L, 56L, 64L, 66L, 54L, 70L, 
## 92L, 93L, 120L, 85L)), class = "data.frame", row.names = c(NA, 
## -50L))
\end{verbatim}

You can then insert the dput output in your \texttt{.rmd} as below.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{data <-}\StringTok{ }\KeywordTok{structure}\NormalTok{(}\KeywordTok{list}\NormalTok{(}\DataTypeTok{X =} \DecValTok{1}\OperatorTok{:}\DecValTok{50}\NormalTok{, }\DataTypeTok{speed =} \KeywordTok{c}\NormalTok{(4L, 4L, 7L, 7L, 8L, 9L, 10L, }
\NormalTok{10L, 10L, 11L, 11L, 12L, 12L, 12L, 12L, 13L, 13L, 13L, 13L, 14L, }
\NormalTok{14L, 14L, 14L, 15L, 15L, 15L, 16L, 16L, 17L, 17L, 17L, 18L, 18L, }
\NormalTok{18L, 18L, 19L, 19L, 19L, 20L, 20L, 20L, 20L, 20L, 22L, 23L, 24L, }
\NormalTok{24L, 24L, 24L, 25L), }\DataTypeTok{dist =} \KeywordTok{c}\NormalTok{(2L, 10L, 4L, 22L, 16L, 10L, 18L, }
\NormalTok{26L, 34L, 17L, 28L, 14L, 20L, 24L, 28L, 26L, 34L, 34L, 46L, 26L, }
\NormalTok{36L, 60L, 80L, 20L, 26L, 54L, 32L, 40L, 32L, 40L, 50L, 42L, 56L, }
\NormalTok{76L, 84L, 36L, 46L, 68L, 32L, 48L, 52L, 56L, 64L, 66L, 54L, 70L, }
\NormalTok{92L, 93L, 120L, 85L)), }
\DataTypeTok{class =} \StringTok{"data.frame"}\NormalTok{, }\DataTypeTok{row.names =} \KeywordTok{c}\NormalTok{(}\OtherTok{NA}\NormalTok{, }
\OperatorTok{-}\NormalTok{50L))}
\end{Highlighting}
\end{Shaded}

\section{Tables}\label{sec:tables}

Producing good tables and referencing these tables within a R Markdown
PDF has been a hassle but got much better. Examples that you may use are
shown below. The way you reference tables is slightly different, e.g.,
for \texttt{stargazer} the label is contained in the function, for
\texttt{kable} it's contained in the chunk name.

\subsection{stargazer(): Summary and regression
tables}\label{stargazer-summary-and-regression-tables}

Table \ref{tab-summarystats} shows summary stats of your data. I
normally use \texttt{stargazer()} (Hlavac
\protect\hyperlink{ref-hlavac2013stargazer}{2013}) which offers extreme
flexibility regarding table output (see \texttt{?stargazer}).

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{library}\NormalTok{(stargazer)}
\KeywordTok{stargazer}\NormalTok{(cars, }
          \DataTypeTok{title =} \StringTok{"Summary table with stargazer"}\NormalTok{,}
          \DataTypeTok{label=}\StringTok{"tab-summarystats"}\NormalTok{, }
          \DataTypeTok{table.placement =} \StringTok{"H"}\NormalTok{, }
          \DataTypeTok{header=}\OtherTok{FALSE}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{table}[H] \centering 
  \caption{Summary table with stargazer} 
  \label{tab-summarystats} 
\begin{tabular}{@{\extracolsep{5pt}}lccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
Statistic & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{St. Dev.} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Pctl(25)} & \multicolumn{1}{c}{Pctl(75)} & \multicolumn{1}{c}{Max} \\ 
\hline \\[-1.8ex] 
speed & 50 & 15.400 & 5.288 & 4 & 12 & 19 & 25 \\ 
dist & 50 & 42.980 & 25.769 & 2 & 26 & 56 & 120 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

Table \ref{tab-regression} shows the output for a regression table. Make
sure you name all your models and explicitly refer to model names (M1,
M2 etc.) in the text.

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{library}\NormalTok{(stargazer)}
\NormalTok{model1 <-}\StringTok{ }\KeywordTok{lm}\NormalTok{(speed }\OperatorTok{~}\StringTok{ }\NormalTok{dist, }\DataTypeTok{data =}\NormalTok{ cars)}
\NormalTok{model2 <-}\StringTok{ }\KeywordTok{lm}\NormalTok{(speed }\OperatorTok{~}\StringTok{ }\NormalTok{dist, }\DataTypeTok{data =}\NormalTok{ cars)}
\NormalTok{model3 <-}\StringTok{ }\KeywordTok{lm}\NormalTok{(dist }\OperatorTok{~}\StringTok{ }\NormalTok{speed, }\DataTypeTok{data =}\NormalTok{ cars)}
\KeywordTok{stargazer}\NormalTok{(model1, model2, model3,}
          \DataTypeTok{title =} \StringTok{"Regression table with stargazer"}\NormalTok{,}
          \DataTypeTok{label=}\StringTok{"tab-regression"}\NormalTok{, }
          \DataTypeTok{table.placement =} \StringTok{"H"}\NormalTok{, }
          \DataTypeTok{column.labels =} \KeywordTok{c}\NormalTok{(}\StringTok{"M1"}\NormalTok{, }\StringTok{"M2"}\NormalTok{, }\StringTok{"M3"}\NormalTok{),}
          \DataTypeTok{model.numbers =} \OtherTok{FALSE}\NormalTok{,}
          \DataTypeTok{header=}\OtherTok{FALSE}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{table}[H] \centering 
  \caption{Regression table with stargazer} 
  \label{tab-regression} 
\begin{tabular}{@{\extracolsep{5pt}}lccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{3}{c}{\textit{Dependent variable:}} \\ 
\cline{2-4} 
\\[-1.8ex] & \multicolumn{2}{c}{speed} & dist \\ 
 & M1 & M2 & M3 \\ 
\hline \\[-1.8ex] 
 dist & 0.166$^{***}$ & 0.166$^{***}$ &  \\ 
  & (0.017) & (0.017) &  \\ 
  & & & \\ 
 speed &  &  & 3.932$^{***}$ \\ 
  &  &  & (0.416) \\ 
  & & & \\ 
 Constant & 8.284$^{***}$ & 8.284$^{***}$ & $-$17.579$^{**}$ \\ 
  & (0.874) & (0.874) & (6.758) \\ 
  & & & \\ 
\hline \\[-1.8ex] 
Observations & 50 & 50 & 50 \\ 
R$^{2}$ & 0.651 & 0.651 & 0.651 \\ 
Adjusted R$^{2}$ & 0.644 & 0.644 & 0.644 \\ 
Residual Std. Error (df = 48) & 3.156 & 3.156 & 15.380 \\ 
F Statistic (df = 1; 48) & 89.567$^{***}$ & 89.567$^{***}$ & 89.567$^{***}$ \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{3}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

\subsection{kable() and kable\_styling()}\label{kable-and-kable_styling}

Another great function is \texttt{kable()} (\texttt{knitr} package) in
combination with \texttt{kableExtra}. Table \ref{tab:tab-kabletable}
provides an example. Again you can modify so many things in both the
\texttt{kable()} and the \texttt{kable\_styling()} function. See
\href{https://haozhu233.github.io/kableExtra/awesome_table_in_pdf.pdf}{this
overview} of all the kable stylings that are possible provided by the
package author himself.

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{library}\NormalTok{(knitr)}
\KeywordTok{library}\NormalTok{(kableExtra)}
\KeywordTok{kable}\NormalTok{(cars[}\DecValTok{1}\OperatorTok{:}\DecValTok{10}\NormalTok{,], }\DataTypeTok{row.names =} \OtherTok{TRUE}\NormalTok{, }\DataTypeTok{caption =} \StringTok{'Table with kable() and kablestyling()'}\NormalTok{, }
      \DataTypeTok{format =} \StringTok{"latex"}\NormalTok{, }\DataTypeTok{booktabs =}\NormalTok{ T) }\OperatorTok{%>%}
\StringTok{        }\KeywordTok{kable_styling}\NormalTok{(}\DataTypeTok{full_width =}\NormalTok{ T, }
                      \DataTypeTok{latex_options =} \KeywordTok{c}\NormalTok{(}\StringTok{"striped"}\NormalTok{, }
                                        \StringTok{"scale_down"}\NormalTok{,}
                                        \StringTok{"HOLD_position"}\NormalTok{),}
                      \DataTypeTok{font_size =} \DecValTok{10}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\rowcolors{2}{gray!6}{white}

\begin{table}[H]

\caption{\label{tab:tab-kabletable}Table with kable() and kablestyling()}
\centering
\resizebox{\linewidth}{!}{
\fontsize{10}{12}\selectfont
\begin{tabu} to \linewidth {>{\raggedright}X>{\raggedleft}X>{\raggedleft}X}
\hiderowcolors
\toprule
  & speed & dist\\
\midrule
\showrowcolors
1 & 4 & 2\\
2 & 4 & 10\\
3 & 7 & 4\\
4 & 7 & 22\\
5 & 8 & 16\\
\addlinespace
6 & 9 & 10\\
7 & 10 & 18\\
8 & 10 & 26\\
9 & 10 & 34\\
10 & 11 & 17\\
\bottomrule
\end{tabu}}
\end{table}

\rowcolors{2}{white}{white}

\section{Inline code \& results}\label{inline-code-results}

Reproduction reaches new heights when you work with inline code. For
instance, you can automatize the display of certain coefficients within
the text. An example is to include estimates, e.g., the coefficient of
\texttt{dist} of the model we ran above.
\texttt{\textasciigrave{}r\ round(coef(model1){[}2{]},\ 2)\textasciigrave{}}
will insert the coefficient as follows: 0.17. Or
\texttt{\textasciigrave{}r\ 3\ +\ 7\textasciigrave{}} will insert a 10
in the text.\\
Inline code/results that depend on earlier objects in your document will
automatically be updated once you change those objects. For instance,
imagine a reviewer asks you to omit certain observations from your
sample. You can simply do so in the beginning of your code and push play
subsequently.. at time you might have to set \texttt{cache\ =\ FALSE} at
the beginning so that all the code chungs are rerun.\\
Researchers often avoid referring to results intext etc. because you
easily forget to change them when revising a manuscript. At the same it
can make an article much more informative and easier to read, e.g., if
you discuss a coefficient in the text you can directly show it in the
section in which you discuss it. Inline code allows you to do just that.
R Markdown allows you to that do so in a reproducible and automatized
manner.

\section{Figures}\label{figures}

\subsection{R base graphs}\label{r-base-graphs}

Inserting figures can be slightly more complicated. Ideally, we would
produce and insert them directly in the \texttt{.rmd} file. It's
relatively simple to insert R base graphs as you can see in Figure
\ref{fig:fig-1}.

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot}\NormalTok{(cars}\OperatorTok{$}\NormalTok{speed, cars}\OperatorTok{$}\NormalTok{dist)}
\end{Highlighting}
\end{Shaded}

\begin{figure}[H]

{\centering \includegraphics{paper_files/figure-latex/fig-1-1}

}

\caption{Scatterplot of Speed and Distance}\label{fig:fig-1}
\end{figure}

But it turns out that it doesn't always work so well.

\subsection{ggplot2 graphs}\label{ggplot2-graphs}

Same is true for ggplot2 as you can see in Figure \ref{fig:fig-2}.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{mtcars}\OperatorTok{$}\NormalTok{cyl <-}\StringTok{ }\KeywordTok{as.factor}\NormalTok{(mtcars}\OperatorTok{$}\NormalTok{cyl) }\CommentTok{# Convert cyl to factor}
\KeywordTok{library}\NormalTok{(ggplot2)}
\KeywordTok{ggplot}\NormalTok{(mtcars, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x=}\NormalTok{wt, }\DataTypeTok{y=}\NormalTok{mpg, }\DataTypeTok{shape=}\NormalTok{cyl)) }\OperatorTok{+}\StringTok{ }\KeywordTok{geom_point}\NormalTok{() }\OperatorTok{+}
\StringTok{  }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{x=}\StringTok{"Weight (lb/1000)"}\NormalTok{, }\DataTypeTok{y =} \StringTok{"Miles/(US) gallon"}\NormalTok{, }
       \DataTypeTok{shape=}\StringTok{"Number of }\CharTok{\textbackslash{}n}\StringTok{ Cylinders"}\NormalTok{) }\OperatorTok{+}\StringTok{ }\KeywordTok{theme_classic}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\begin{figure}[H]

{\centering \includegraphics{paper_files/figure-latex/fig-2-1}

}

\caption{Miles per gallon according to the weight}\label{fig:fig-2}
\end{figure}

\subsection{Plotly graphs}\label{plotly-graphs}

Plotly is a popular graph engine that let's you also produce interactive
graphs that you can embed in html webpages or documents (e.g., see
\href{https://paulcbauer.shinyapps.io/visualizing-causal-scenarios/}{here}).
I am a big fan, however, right now there is no easy, automatic way to
insert high resolution Plotly graphs into your R Markdown PDF. See
Figure \ref{fig:fig-3} below.\\
There seems to be a new engine for exporting graphs locally without
relying on the plotly server --- which you wanna avoid for a properly
reproducible PDF --- called orca (\texttt{?orca}). However, the
\href{https://github.com/plotly/orca\#installation}{installation} is too
challenging for the average user at the moment.

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{library}\NormalTok{(plotly)}
\KeywordTok{plot_ly}\NormalTok{(cars, }\DataTypeTok{type =} \StringTok{"scatter"}\NormalTok{, }\DataTypeTok{mode=}\StringTok{"markers"}\NormalTok{,}
        \DataTypeTok{x=}\OperatorTok{~}\NormalTok{speed, }
        \DataTypeTok{y=}\OperatorTok{~}\NormalTok{dist)}
\end{Highlighting}
\end{Shaded}

\begin{figure}[H]

{\centering \includegraphics{paper_files/figure-latex/fig-3-1}

}

\caption{Scatterplot of Speed and Distance}\label{fig:fig-3}
\end{figure}

\section{Good practices}\label{good-practices}

Every researcher has his own optimized setup. Currently I would
recommend the following:

\begin{itemize}
\tightlist
\item
  Keep all files of your project (that matter for producing the PDF) in
  one folder without subfolders. You can zip and directly upload that
  folder to the \href{https://dataverse.harvard.edu/}{Harvard
  dataverse}).
\item
  Make sure that filenames have a logic to them.

  \begin{itemize}
  \tightlist
  \item
    Main file with text/code: ``paper.rmd'', ``report.rmd''
  \item
    Data files: ``data\_xxxxxx.*"
  \item
    Image files: ``fig\_xxxxxx.*"
  \item
    Tables files: ``table\_xxxx.*"
  \item
    etc.
  \item
    Ideally, your filenames will correspond to the names in the paper.
    For instance, Figure 1 in the paper may have a corresponding file
    called \texttt{fig\_1\_xxxxx.pdf}.
  \end{itemize}
\item
  Use document the document outline in R studio (Ctrl + Shift + O) when
  you work with R Markdown.
\item
  Name rchunks according to what they do or produce:

  \begin{itemize}
  \tightlist
  \item
    ``\texttt{fig-...}'' for chunks producing figures
  \item
    ``\texttt{table-...}'' for chunks producing tables
  \item
    ``\texttt{model-...}'' for chunks producing model estimates
  \item
    ``\texttt{import-...}'' for chunks importing data
  \item
    ``\texttt{recoding-...}'' for chunks in which data is recoded
  \end{itemize}
\item
  Use ``really'' informative variable names:

  \begin{itemize}
  \tightlist
  \item
    Q: What do you think does the variable \emph{trstep} measure? It
    actually measures trust in the European parliament.

    \begin{itemize}
    \tightlist
    \item
      How could we call this variable instead? Yes,
      \texttt{trust.european.parliament} which is longer but will
      probably be understood by one of your descendants in 100 years.
    \end{itemize}
  \item
    If your setup is truly reproducible you will probably re-use the
    variable names that you generate as variable names in the tables you
    produce. Hence, there is an incentive to use good names.
  \end{itemize}
\item
  Use unique identifiers in the final document:

  \begin{itemize}
  \tightlist
  \item
    e.g., name the models you estimate ``M1'', ``M2'' etc.
  \item
    These unique names should also appear in the published paper.
  \item
    Think of someone who wants to produce Figure 1/Model 1 in your paper
    but doesn't find it in your code\ldots{}
  \end{itemize}
\end{itemize}

\section{Citation styles}\label{citation-styles}

If your study needs to follow a particular citation style, you can set
the corresponding style in the header of your \texttt{.rmd} document. To
do so you have to download the corresponding \texttt{.csl} file.

In the present document we use the style of the American Sociological
Association and set it in the preamble with
\texttt{csl:\ american-sociological-association.csl}. However, you also
need to download the respective \texttt{.csl} file from the following
github page: \url{https://github.com/citation-style-language/styles} and
copy it into your working directory for it to work.

The github directory contains a wide variety of citation style files
depending on what discipline your work in.

\section{Appendix}\label{appendix}

\subsection{All the code in the paper}\label{all-the-code-in-the-paper}

To simply attach all the code you used in the PDF file in the appendix
see the R chunk in the underlying \texttt{.rmd} file:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{knitr}\OperatorTok{::}\NormalTok{opts_chunk}\OperatorTok{$}\KeywordTok{set}\NormalTok{(}\DataTypeTok{cache =} \OtherTok{FALSE}\NormalTok{)}
\CommentTok{# Use chache = TRUE if you want to speed up compilation}

\CommentTok{# A function to allow for showing some of the inline code}
\NormalTok{rinline <-}\StringTok{ }\ControlFlowTok{function}\NormalTok{(code)\{}
\NormalTok{  html <-}\StringTok{ '<code  class="r">``` `r CODE` ```</code>'}
  \KeywordTok{sub}\NormalTok{(}\StringTok{"CODE"}\NormalTok{, code, html)}
\NormalTok{\}}
\KeywordTok{install.packages}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{'tinytex'}\NormalTok{, }\StringTok{'rmarkdown'}\NormalTok{))}
\NormalTok{tinytex}\OperatorTok{::}\KeywordTok{install_tinytex}\NormalTok{()}
\KeywordTok{install.packages}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"rmarkdown"}\NormalTok{, }\StringTok{"knitr"}\NormalTok{, }\StringTok{"kableExtra"}\NormalTok{,}
                   \StringTok{"stargazer"}\NormalTok{, }\StringTok{"plotly"}\NormalTok{, }\StringTok{"knitr"}\NormalTok{,}
                   \StringTok{"bookdown"}\NormalTok{))}
\KeywordTok{cat}\NormalTok{(}\KeywordTok{paste}\NormalTok{(}\StringTok{"#"}\NormalTok{, }\KeywordTok{capture.output}\NormalTok{(}\KeywordTok{sessionInfo}\NormalTok{()), }\StringTok{"}\CharTok{\textbackslash{}n}\StringTok{"}\NormalTok{, }\DataTypeTok{collapse =}\StringTok{""}\NormalTok{)) }
  \CommentTok{# or use message() instead of cat()}
\NormalTok{data <-}\StringTok{ }\KeywordTok{read.csv}\NormalTok{(}\StringTok{"data.csv"}\NormalTok{)}
\KeywordTok{head}\NormalTok{(data)}
\KeywordTok{dput}\NormalTok{(data)}
\NormalTok{data <-}\StringTok{ }\KeywordTok{structure}\NormalTok{(}\KeywordTok{list}\NormalTok{(}\DataTypeTok{X =} \DecValTok{1}\OperatorTok{:}\DecValTok{50}\NormalTok{, }\DataTypeTok{speed =} \KeywordTok{c}\NormalTok{(4L, 4L, 7L, 7L, 8L, 9L, 10L, }
\NormalTok{10L, 10L, 11L, 11L, 12L, 12L, 12L, 12L, 13L, 13L, 13L, 13L, 14L, }
\NormalTok{14L, 14L, 14L, 15L, 15L, 15L, 16L, 16L, 17L, 17L, 17L, 18L, 18L, }
\NormalTok{18L, 18L, 19L, 19L, 19L, 20L, 20L, 20L, 20L, 20L, 22L, 23L, 24L, }
\NormalTok{24L, 24L, 24L, 25L), }\DataTypeTok{dist =} \KeywordTok{c}\NormalTok{(2L, 10L, 4L, 22L, 16L, 10L, 18L, }
\NormalTok{26L, 34L, 17L, 28L, 14L, 20L, 24L, 28L, 26L, 34L, 34L, 46L, 26L, }
\NormalTok{36L, 60L, 80L, 20L, 26L, 54L, 32L, 40L, 32L, 40L, 50L, 42L, 56L, }
\NormalTok{76L, 84L, 36L, 46L, 68L, 32L, 48L, 52L, 56L, 64L, 66L, 54L, 70L, }
\NormalTok{92L, 93L, 120L, 85L)), }
\DataTypeTok{class =} \StringTok{"data.frame"}\NormalTok{, }\DataTypeTok{row.names =} \KeywordTok{c}\NormalTok{(}\OtherTok{NA}\NormalTok{, }
\OperatorTok{-}\NormalTok{50L))}
\KeywordTok{library}\NormalTok{(stargazer)}
\KeywordTok{stargazer}\NormalTok{(cars, }
          \DataTypeTok{title =} \StringTok{"Summary table with stargazer"}\NormalTok{,}
          \DataTypeTok{label=}\StringTok{"tab-summarystats"}\NormalTok{, }
          \DataTypeTok{table.placement =} \StringTok{"H"}\NormalTok{, }
          \DataTypeTok{header=}\OtherTok{FALSE}\NormalTok{)}
\KeywordTok{library}\NormalTok{(stargazer)}
\NormalTok{model1 <-}\StringTok{ }\KeywordTok{lm}\NormalTok{(speed }\OperatorTok{~}\StringTok{ }\NormalTok{dist, }\DataTypeTok{data =}\NormalTok{ cars)}
\NormalTok{model2 <-}\StringTok{ }\KeywordTok{lm}\NormalTok{(speed }\OperatorTok{~}\StringTok{ }\NormalTok{dist, }\DataTypeTok{data =}\NormalTok{ cars)}
\NormalTok{model3 <-}\StringTok{ }\KeywordTok{lm}\NormalTok{(dist }\OperatorTok{~}\StringTok{ }\NormalTok{speed, }\DataTypeTok{data =}\NormalTok{ cars)}
\KeywordTok{stargazer}\NormalTok{(model1, model2, model3,}
          \DataTypeTok{title =} \StringTok{"Regression table with stargazer"}\NormalTok{,}
          \DataTypeTok{label=}\StringTok{"tab-regression"}\NormalTok{, }
          \DataTypeTok{table.placement =} \StringTok{"H"}\NormalTok{, }
          \DataTypeTok{column.labels =} \KeywordTok{c}\NormalTok{(}\StringTok{"M1"}\NormalTok{, }\StringTok{"M2"}\NormalTok{, }\StringTok{"M3"}\NormalTok{),}
          \DataTypeTok{model.numbers =} \OtherTok{FALSE}\NormalTok{,}
          \DataTypeTok{header=}\OtherTok{FALSE}\NormalTok{)}
\KeywordTok{library}\NormalTok{(knitr)}
\KeywordTok{library}\NormalTok{(kableExtra)}
\KeywordTok{kable}\NormalTok{(cars[}\DecValTok{1}\OperatorTok{:}\DecValTok{10}\NormalTok{,], }\DataTypeTok{row.names =} \OtherTok{TRUE}\NormalTok{, }\DataTypeTok{caption =} \StringTok{'Table with kable() and kablestyling()'}\NormalTok{, }
      \DataTypeTok{format =} \StringTok{"latex"}\NormalTok{, }\DataTypeTok{booktabs =}\NormalTok{ T) }\OperatorTok{%>%}
\StringTok{        }\KeywordTok{kable_styling}\NormalTok{(}\DataTypeTok{full_width =}\NormalTok{ T, }
                      \DataTypeTok{latex_options =} \KeywordTok{c}\NormalTok{(}\StringTok{"striped"}\NormalTok{, }
                                        \StringTok{"scale_down"}\NormalTok{,}
                                        \StringTok{"HOLD_position"}\NormalTok{),}
                      \DataTypeTok{font_size =} \DecValTok{10}\NormalTok{)}
\KeywordTok{plot}\NormalTok{(cars}\OperatorTok{$}\NormalTok{speed, cars}\OperatorTok{$}\NormalTok{dist)}
\NormalTok{mtcars}\OperatorTok{$}\NormalTok{cyl <-}\StringTok{ }\KeywordTok{as.factor}\NormalTok{(mtcars}\OperatorTok{$}\NormalTok{cyl) }\CommentTok{# Convert cyl to factor}
\KeywordTok{library}\NormalTok{(ggplot2)}
\KeywordTok{ggplot}\NormalTok{(mtcars, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x=}\NormalTok{wt, }\DataTypeTok{y=}\NormalTok{mpg, }\DataTypeTok{shape=}\NormalTok{cyl)) }\OperatorTok{+}\StringTok{ }\KeywordTok{geom_point}\NormalTok{() }\OperatorTok{+}
\StringTok{  }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{x=}\StringTok{"Weight (lb/1000)"}\NormalTok{, }\DataTypeTok{y =} \StringTok{"Miles/(US) gallon"}\NormalTok{, }
       \DataTypeTok{shape=}\StringTok{"Number of }\CharTok{\textbackslash{}n}\StringTok{ Cylinders"}\NormalTok{) }\OperatorTok{+}\StringTok{ }\KeywordTok{theme_classic}\NormalTok{()}
\KeywordTok{library}\NormalTok{(plotly)}
\KeywordTok{plot_ly}\NormalTok{(cars, }\DataTypeTok{type =} \StringTok{"scatter"}\NormalTok{, }\DataTypeTok{mode=}\StringTok{"markers"}\NormalTok{,}
        \DataTypeTok{x=}\OperatorTok{~}\NormalTok{speed, }
        \DataTypeTok{y=}\OperatorTok{~}\NormalTok{dist)}
\end{Highlighting}
\end{Shaded}

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\hypertarget{ref-markdown2017}{}
Allaire, JJ, Jeffrey Horner, Vicent Marti, and Natacha Porte. 2017.
\emph{Markdown: 'Markdown' Rendering for R}.

\hypertarget{ref-Bauer2018-hd}{}
Bauer, Paul C. 2018. ``Unemployment, Trust in Government, and
Satisfaction with Democracy: An Empirical Investigation.'' \emph{Socius}
4:1--14.

\hypertarget{ref-hlavac2013stargazer}{}
Hlavac, Marek. 2013. ``Stargazer: LaTeX Code and Ascii Text for
Well-Formatted Regression and Summary Statistics Tables.'' \emph{URL:
Http://CRAN. R-Project. Org/Package= Stargazer}.

\hypertarget{ref-Kirsop2005-ro}{}
Kirsop, Barbara and Leslie Chan. 2005. ``Transforming Access to Research
Literature for Developing Countries.'' \emph{Serials Review}
31(4):246--55.

\hypertarget{ref-R2017}{}
R Core Team. 2017. \emph{R: A Language and Environment for Statistical
Computing}. Vienna, Austria: R Foundation for Statistical Computing.

\hypertarget{ref-Rstudio2015}{}
RStudio Team. 2015. \emph{RStudio: Integrated Development Environment
for R}. Boston, MA: RStudio, Inc.

\hypertarget{ref-plotly}{}
Sievert, Carson, Chris Parmer, Toby Hocking, Scott Chamberlain, Karthik
Ram, Marianne Corvellec, and Pedro Despouy. 2017. \emph{Plotly: Create
Interactive Web Graphics via 'Plotly.js'}.

\hypertarget{ref-knitr3}{}
Xie, Yihui. 2014. ``Knitr: A Comprehensive Tool for Reproducible
Research in R.'' in \emph{Implementing reproducible computational
research}, edited by V. Stodden, F. Leisch, and R. D. Peng. Chapman;
Hall/CRC.

\hypertarget{ref-knitr2}{}
Xie, Yihui. 2015. \emph{Dynamic Documents with R and Knitr}. 2nd ed.
Boca Raton, Florida: Chapman; Hall/CRC.

\hypertarget{ref-bookdown2}{}
Xie, Yihui. 2016. \emph{Bookdown: Authoring Books and Technical
Documents with R Markdown}. Boca Raton, Florida: Chapman; Hall/CRC.

\hypertarget{ref-bookdown1}{}
Xie, Yihui. 2017. \emph{Bookdown: Authoring Books and Technical
Documents with R Markdown}.

\hypertarget{ref-knitr1}{}
Xie, Yihui. 2018a. \emph{Knitr: A General-Purpose Package for Dynamic
Report Generation in R}.

\hypertarget{ref-tinytex}{}
Xie, Yihui. 2018b. \emph{Tinytex: Helper Functions to Install and
Maintain 'Tex Live', and Compile 'Latex' Documents}.

\hypertarget{ref-kableextra}{}
Zhu, Hao. 2017. \emph{KableExtra: Construct Complex Table with 'Kable'
and Pipe Syntax}.

\end{document}

### 2018-11-02 paper.Rmd
A few small changes.

@@
 
-Table \@ref(tab-summarystats) shows summary stats of your data. I normally use `stargazer()` [@hlavac2013stargazer] which offers extreme flexibility regarding table output (see `?stargazer`).
+Table \@ref(tab1) shows summary stats of your data.^[To reference the table where you set the identifier in the stargazer function you only need to use the actual label, i.e., ´tab1´.] I normally use `stargazer()` [@hlavac2013stargazer] which offers extreme flexibility regarding table output (see `?stargazer`).
 
@@
           title = "Summary table with stargazer",
-          label="tab-summarystats", 
+          label="tab1", 
           table.placement = "H", 
@@
 
-Table \@ref(tab-regression) shows the output for a regression table. Make sure you name all your models and explicitly refer to model names (M1, M2 etc.) in the text.
+Table \@ref(tab2) shows the output for a regression table. Make sure you name all your models and explicitly refer to model names (M1, M2 etc.) in the text.
 
@@
           title = "Regression table with stargazer",
-          label="tab-regression", 
+          label="tab2", 
           table.placement = "H", 
@@
 Another great function is `kable()` (`knitr` package) in combination with `kableExtra`.
-Table \@ref(tab:tab-kabletable) provides an example.
-Again you can modify so many things in both the `kable()` and the `kable_styling()` function.
+Table \@ref(tab:tab3) provides an example.^[To reference the table produced by the chunk you need to add ´tab:´ to the chunk name, i.e., ´tab:tab3´.] Again you can modify so many things in both the `kable()` and the `kable_styling()` function.
 See [this overview](https://haozhu233.github.io/kableExtra/awesome_table_in_pdf.pdf) of all the kable stylings that are possible provided by the package author himself.
 
-```{r tab-kabletable, echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE, results="asis"}
+```{r tab3, echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE, results="asis"}
 library(knitr)
 library(kableExtra)
-kable(cars[1:10,], row.names = TRUE, caption = 'Table with kable() and kablestyling()', 
+kable(cars[1:10,], row.names = TRUE, 
+      caption = 'Table with kable() and kablestyling()', 
       format = "latex", booktabs = T) %>%

### 2018-11-02 paper.tex
A few small changes.

@@
   want to understand your work and built on it. It may sound like a joke
-  but why not aim for reproducability in 500 years.
+  but why not aim for a document that can be used to reproduce your
+  findings in in 500 years.
 \item
@@
 \item
-  \textbf{Revisions}: Revising a paper takes much less time, if you have
+  \textbf{Revisions}: Revising a paper takes much less time if you have
   all the code you need in one place, i.e., one \texttt{.rmd} file. For
@@
 
-Table \ref{tab-summarystats} shows summary stats of your data. I
-normally use \texttt{stargazer()} (Hlavac
+Table \ref{tab1} shows summary stats of your data.\footnote{To reference
+  the table where you set the identifier in the stargazer function you
+  only need to use the actual label, i.e., ´tab1´.} I normally use
+\texttt{stargazer()} (Hlavac
 \protect\hyperlink{ref-hlavac2013stargazer}{2013}) which offers extreme
@@
           \DataTypeTok{title =} \StringTok{"Summary table with stargazer"}\NormalTok{,}
-          \DataTypeTok{label=}\StringTok{"tab-summarystats"}\NormalTok{, }
+          \DataTypeTok{label=}\StringTok{"tab1"}\NormalTok{, }
           \DataTypeTok{table.placement =} \StringTok{"H"}\NormalTok{, }
@@
   \caption{Summary table with stargazer} 
-  \label{tab-summarystats} 
+  \label{tab1} 
 \begin{tabular}{@{\extracolsep{5pt}}lccccccc} 
@@
 
-Table \ref{tab-regression} shows the output for a regression table. Make
-sure you name all your models and explicitly refer to model names (M1,
-M2 etc.) in the text.
+Table \ref{tab2} shows the output for a regression table. Make sure you
+name all your models and explicitly refer to model names (M1, M2 etc.)
+in the text.
 
@@
           \DataTypeTok{title =} \StringTok{"Regression table with stargazer"}\NormalTok{,}
-          \DataTypeTok{label=}\StringTok{"tab-regression"}\NormalTok{, }
+          \DataTypeTok{label=}\StringTok{"tab2"}\NormalTok{, }
           \DataTypeTok{table.placement =} \StringTok{"H"}\NormalTok{, }
@@
   \caption{Regression table with stargazer} 
-  \label{tab-regression} 
+  \label{tab2} 
 \begin{tabular}{@{\extracolsep{5pt}}lccc} 
@@
 Another great function is \texttt{kable()} (\texttt{knitr} package) in
-combination with \texttt{kableExtra}. Table \ref{tab:tab-kabletable}
-provides an example. Again you can modify so many things in both the
-\texttt{kable()} and the \texttt{kable\_styling()} function. See
+combination with \texttt{kableExtra}. Table \ref{tab:tab3} provides an
+example.\footnote{To reference the table produced by the chunk you need
+  to add ´tab:´ to the chunk name, i.e., ´tab:tab3´.} Again you can
+modify so many things in both the \texttt{kable()} and the
+\texttt{kable\_styling()} function. See
 \href{https://haozhu233.github.io/kableExtra/awesome_table_in_pdf.pdf}{this
@@
 \KeywordTok{library}\NormalTok{(kableExtra)}
-\KeywordTok{kable}\NormalTok{(cars[}\DecValTok{1}\OperatorTok{:}\DecValTok{10}\NormalTok{,], }\DataTypeTok{row.names =} \OtherTok{TRUE}\NormalTok{, }\DataTypeTok{caption =} \StringTok{'Table with kable() and kablestyling()'}\NormalTok{, }
+\KeywordTok{kable}\NormalTok{(cars[}\DecValTok{1}\OperatorTok{:}\DecValTok{10}\NormalTok{,], }\DataTypeTok{row.names =} \OtherTok{TRUE}\NormalTok{, }
+      \DataTypeTok{caption =} \StringTok{'Table with kable() and kablestyling()'}\NormalTok{, }
       \DataTypeTok{format =} \StringTok{"latex"}\NormalTok{, }\DataTypeTok{booktabs =}\NormalTok{ T) }\OperatorTok{%>%}
@@
 
-\caption{\label{tab:tab-kabletable}Table with kable() and kablestyling()}
+\caption{\label{tab:tab3}Table with kable() and kablestyling()}
 \centering

### 2018-11-02 paper.Rmd
Added README.

@@
 ```
-* ...download the 4 input files I created (see below) from [this folder](https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing).
+* ...download the 5 input files I created --- `paper.rmd`, `header.tex`, `references.bib`, `data.csv` and `american-sociological-association.csl` --- from [this folder](https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing).
+Ignore the other files.
 
@@
 # Basics: Input and output files
-All the files you need to produce the present PDF file are 4 input files...
+All the files you need to produce the present PDF file are the input files...
 

### 2018-11-02 paper.tex
Added README.

@@
 \item
-  \ldots{}download the 4 input files I created (see below) from
+  \ldots{}download the 5 input files I created --- \texttt{paper.rmd},
+  \texttt{header.tex}, \texttt{references.bib}, \texttt{data.csv} and
+  \texttt{american-sociological-association.csl} --- from
   \href{https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing}{this
-  folder}.
+  folder}. Ignore the other files.
 \item
@@
 
-All the files you need to produce the present PDF file are 4 input
+All the files you need to produce the present PDF file are the input
 files\ldots{}

### 2018-11-07 paper.Rmd
Deleted files and updated text.

@@
 colorlinks: true
-abstract: \noindent\setstretch{1}The present paper provides a template for a reproducable scientific paper written in R Markdown.
+abstract: \noindent\setstretch{1}The present paper provides a template for a reproducible scientific paper written in R Markdown.
 Below I outline some of the "tricks"/code (e.g., referencing tables, sections etc.) I had to figure out to produce this document.
@@
 I think I got pretty far but there is always room for improvement and more automatization, in parallel to the incredible developments in R and Rstudio (bookdown etc.).
-My last paper is almost entirely based on R Markdown [see @Bauer2018-hd and [reproduction files](https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/DUMGLT)].
 I intend to update this file when I discover more convenient code.\vspace{.8cm}
@@
 * **Reproducability**: Even if you have written a study and analyzed the data yourself you will forget what you did after a few months.
-A fully reproducable setup will help you to trace back your own steps.
+A fully reproducible setup will help you to trace back your own steps.
 Obviously, the same is true for other researchers who may want to understand your work and built on it.
@@
 You can simply do so in the beginning of your code and push play subsequently..
-at time you might have to set `cache = FALSE` at the beginning so that all the code chungs are rerun.
-Researchers often avoid referring to results intext etc.
+at time you might have to set `cache = FALSE` at the beginning so that all the code chunks are rerun.
+Researchers often avoid referring to results in-text etc.
 because you easily forget to change them when revising a manuscript.
@@
 
-The github directory contains a wide variety of citation style files depending on what discipline your work in.
+The github directory contains a wide variety of citation style files depending on what discipline you work in.
 

### 2018-11-07 paper.tex
Deleted files and updated text.

@@
   \postdate{\par}
-    \date{2 November, 2018\\[2\baselineskip]Feedback?\\
+    \date{5 November, 2018\\[2\baselineskip]Feedback?\\
 \href{mailto:mail@paulcbauer.eu}{\nolinkurl{mail@paulcbauer.eu}}\\}
@@
 \noindent\setstretch{1}The present paper provides a template for a
-reproducable scientific paper written in R Markdown. Below I outline
+reproducible scientific paper written in R Markdown. Below I outline
 some of the ``tricks''/code (e.g., referencing tables, sections etc.) I
@@
 more automatization, in parallel to the incredible developments in R and
-Rstudio (bookdown etc.). My last paper is almost entirely based on R
-Markdown (see Bauer \protect\hyperlink{ref-Bauer2018-hd}{2018} and
-\href{https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/DUMGLT}{reproduction
-files}). I intend to update this file when I discover more convenient
-code.\vspace{.8cm}
+Rstudio (bookdown etc.). I intend to update this file when I discover
+more convenient code.\vspace{.8cm}
 \end{abstract}
@@
   analyzed the data yourself you will forget what you did after a few
-  months. A fully reproducable setup will help you to trace back your
+  months. A fully reproducible setup will help you to trace back your
   own steps. Obviously, the same is true for other researchers who may
@@
 subsequently.. at time you might have to set \texttt{cache\ =\ FALSE} at
-the beginning so that all the code chungs are rerun.\\
-Researchers often avoid referring to results intext etc. because you
+the beginning so that all the code chunks are rerun.\\
+Researchers often avoid referring to results in-text etc. because you
 easily forget to change them when revising a manuscript. At the same it
@@
 The github directory contains a wide variety of citation style files
-depending on what discipline your work in.
+depending on what discipline you work in.
 
@@
 
-\hypertarget{ref-Bauer2018-hd}{}
-Bauer, Paul C. 2018. ``Unemployment, Trust in Government, and
-Satisfaction with Democracy: An Empirical Investigation.'' \emph{Socius}
-4:1--14.
-
 \hypertarget{ref-hlavac2013stargazer}{}

### 2018-12-13 paper.Rmd
Added orca exported graph.

@@
 Plotly is a popular graph engine that let's you also produce interactive graphs that you can embed in html webpages or documents (e.g., see [here](https://paulcbauer.shinyapps.io/visualizing-causal-scenarios/)).
-I am a big fan, however, right now there is no easy, automatic way to insert high resolution Plotly graphs into your R Markdown PDF.
-See Figure \@ref(fig:fig-3) below.
-There seems to be a new engine for exporting graphs locally without relying on the plotly server --- which you wanna avoid for a properly reproducible PDF --- called orca (`?orca`).
-However, the [installation](https://github.com/plotly/orca#installation) is too challenging for the average user at the moment.
+I am a big fan.
+For some time there was no easy, automatic way to insert high resolution Plotly graphs into your R Markdown PDF.
+However, this changed since Plotly provided Orca, a command line application for generating static images from Plotly graphs.
+The installation is a bit tricky (see here: https://github.com/plotly/orca#installation) but once you get it running you can produce beautiful graphs and include them in your RMarkdown PDF using some simple latex as shown below in Figure \@ref(fig:fig-3).
 
-```{r fig-3, fig.align="center", fig.cap="Scatterplot of Speed and Distance", fig.pos="H", message=FALSE, warning=FALSE}
+```{r fig-3, message=FALSE, warning=FALSE}
 library(plotly)
-plot_ly(cars, type = "scatter", mode="markers",
+p <- plot_ly(cars, type = "scatter", mode="markers",
         x=~speed, 
         y=~dist)
+Sys.setenv('MAPBOX_TOKEN' = '12423423') # set arbitrary token
+orca(p, "plotly-plot.pdf")
 ```
+
+\begin{figure}[H]
+\centering
+\caption{An plotly plot that was exported as PDF with orca before}\label{fig:fig-3}
+		\includegraphics[width=0.9\linewidth]{plotly-plot.pdf}
+\begin{flushleft}
+\end{flushleft}
+\end{figure}
+\vspace{-1.2cm}
 

### 2018-12-13 paper.tex
Added orca exported graph.

@@
   \postdate{\par}
-    \date{5 November, 2018\\[2\baselineskip]Feedback?\\
+    \date{13 December, 2018\\[2\baselineskip]Feedback?\\
 \href{mailto:mail@paulcbauer.eu}{\nolinkurl{mail@paulcbauer.eu}}\\}
@@
 \href{https://paulcbauer.shinyapps.io/visualizing-causal-scenarios/}{here}).
-I am a big fan, however, right now there is no easy, automatic way to
-insert high resolution Plotly graphs into your R Markdown PDF. See
-Figure \ref{fig:fig-3} below.\\
-There seems to be a new engine for exporting graphs locally without
-relying on the plotly server --- which you wanna avoid for a properly
-reproducible PDF --- called orca (\texttt{?orca}). However, the
-\href{https://github.com/plotly/orca\#installation}{installation} is too
-challenging for the average user at the moment.
+I am a big fan. For some time there was no easy, automatic way to insert
+high resolution Plotly graphs into your R Markdown PDF. However, this
+changed since Plotly provided Orca, a command line application for
+generating static images from Plotly graphs. The installation is a bit
+tricky (see here: \url{https://github.com/plotly/orca\#installation})
+but once you get it running you can produce beautiful graphs and include
+them in your RMarkdown PDF using some simple latex as shown below in
+Figure \ref{fig:fig-3}.
 
@@
 \KeywordTok{library}\NormalTok{(plotly)}
-\KeywordTok{plot_ly}\NormalTok{(cars, }\DataTypeTok{type =} \StringTok{"scatter"}\NormalTok{, }\DataTypeTok{mode=}\StringTok{"markers"}\NormalTok{,}
+\NormalTok{p <-}\StringTok{ }\KeywordTok{plot_ly}\NormalTok{(cars, }\DataTypeTok{type =} \StringTok{"scatter"}\NormalTok{, }\DataTypeTok{mode=}\StringTok{"markers"}\NormalTok{,}
         \DataTypeTok{x=}\OperatorTok{~}\NormalTok{speed, }
         \DataTypeTok{y=}\OperatorTok{~}\NormalTok{dist)}
+\KeywordTok{Sys.setenv}\NormalTok{(}\StringTok{'MAPBOX_TOKEN'}\NormalTok{ =}\StringTok{ '12423423'}\NormalTok{) }\CommentTok{# set arbitrary token}
+\KeywordTok{orca}\NormalTok{(p, }\StringTok{"plotly-plot.pdf"}\NormalTok{)}
 \end{Highlighting}
@@
 \begin{figure}[H]
-
-{\centering \includegraphics{paper_files/figure-latex/fig-3-1}
-
-}
-
-\caption{Scatterplot of Speed and Distance}\label{fig:fig-3}
+\centering
+\caption{An plotly plot that was exported as PDF with orca before}\label{fig:fig-3}
+        \includegraphics[width=0.9\linewidth]{plotly-plot.pdf}
+\begin{flushleft}
+\end{flushleft}
 \end{figure}
+
+\vspace{-1.2cm}
 

### 2018-12-14 paper.Rmd
Corrected typos and added orca() function.

@@
 Obviously, the same is true for other researchers who may want to understand your work and built on it.
-It may sound like a joke but why not aim for a document that can be used to reproduce your findings in in 500 years.
+It may sound like a joke but why not aim for a document that can be used to reproduce your findings in 500 years.
 * **Errors**: Manual steps in data analysis (e.g., manually copy/pasting values into a table etc.) may introduce errors. R Markdown allows you to **automatize** such steps and/or avoid them.
@@
 The installation is a bit tricky (see here: https://github.com/plotly/orca#installation) but once you get it running you can produce beautiful graphs and include them in your RMarkdown PDF using some simple latex as shown below in Figure \@ref(fig:fig-3).
+Potentially, in case you did not install the command line application this part may fail.
+If so simply exclude the chunk and the latex code.
 
@@
 * Keep all files of your project (that matter for producing the PDF) in one folder without subfolders.
-You can zip and directly upload that folder to the [Harvard dataverse](https://dataverse.harvard.edu/)).
+You can zip and directly upload that folder to the [Harvard dataverse](https://dataverse.harvard.edu/).
 * Make sure that filenames have a logic to them.
@@
     + Ideally, your filenames will correspond to the names in the paper. For instance, Figure 1 in the paper may have a corresponding file called `fig_1_xxxxx.pdf`.
-* Use document the document outline in R studio (Ctrl + Shift + O) when you work with R Markdown.
+* Use the document outline in R studio (Ctrl + Shift + O) when you work with R Markdown.
 * Name rchunks according to what they do or produce:
@@
     + Q: What do you think does the variable *trstep* measure? It actually measures trust in the European parliament. 
-        + How could we call this variable instead? Yes, `trust.european.parliament` which is longer but will probably be understood by one of your descendants in 100 years.
+        + How could we call this variable instead? Yes, `trust.european.parliament` which is longer but will probably be understood by another researcher. 
     + If your setup is truly reproducible you will probably re-use the variable names that you generate as variable names in the tables you produce. Hence, there is an incentive to use good names.

### 2018-12-14 paper.tex
Corrected typos and added orca() function.

@@
   \postdate{\par}
-    \date{13 December, 2018\\[2\baselineskip]Feedback?\\
+    \date{14 December, 2018\\[2\baselineskip]Feedback?\\
 \href{mailto:mail@paulcbauer.eu}{\nolinkurl{mail@paulcbauer.eu}}\\}
@@
   but why not aim for a document that can be used to reproduce your
-  findings in in 500 years.
+  findings in 500 years.
 \item
@@
 them in your RMarkdown PDF using some simple latex as shown below in
-Figure \ref{fig:fig-3}.
+Figure \ref{fig:fig-3}. Potentially, in case you did not install the
+command line application this part may fail. If so simply exclude the
+chunk and the latex code.
 
@@
   folder to the \href{https://dataverse.harvard.edu/}{Harvard
-  dataverse}).
+  dataverse}.
 \item
@@
 \item
-  Use document the document outline in R studio (Ctrl + Shift + O) when
-  you work with R Markdown.
+  Use the document outline in R studio (Ctrl + Shift + O) when you work
+  with R Markdown.
 \item
@@
       \texttt{trust.european.parliament} which is longer but will
-      probably be understood by one of your descendants in 100 years.
+      probably be understood by another researcher.
     \end{itemize}

### 2020-04-05 paper.Rmd
Took out plotly/orca.
Needs complicated installation...

@@
 always_allow_html: yes
-header-includes:
-   - \usepackage{dcolumn}
-   - \usepackage{color}
 ---
@@
 
-I would recommend to use the command below and copy/paste the output into the first R chunk in your `paper.rmd` file.
-Normally we would do this when we compile/generate the paper for the last time.
+I would recommend to use the command below and simply add it to the appendix as I did here in Appendix \@ref(sec:rsessioninfo).
+This will make sure you always provide the package versions that you used in the last compilation of your paper.
 For more advanced tools see [packrat](https://rstudio.github.io/packrat/).
 
-```{r fig-versioning, echo=TRUE}
+```{r fig-versioning, echo=TRUE, eval=FALSE}
 cat(paste("#", capture.output(sessionInfo()), "\n", collapse ="")) 
@@
 
-## Plotly graphs
-Plotly is a popular graph engine that let's you also produce interactive graphs that you can embed in html webpages or documents (e.g., see [here](https://paulcbauer.shinyapps.io/visualizing-causal-scenarios/)).
-I am a big fan.
-For some time there was no easy, automatic way to insert high resolution Plotly graphs into your R Markdown PDF.
-However, this changed since Plotly provided Orca, a command line application for generating static images from Plotly graphs.
-The installation is a bit tricky (see here: https://github.com/plotly/orca#installation) but once you get it running you can produce beautiful graphs and include them in your RMarkdown PDF using some simple latex as shown below in Figure \@ref(fig:fig-3).
-Potentially, in case you did not install the command line application this part may fail.
-If so simply exclude the chunk and the latex code.
-
-```{r fig-3, message=FALSE, warning=FALSE}
-library(plotly)
-p <- plot_ly(cars, type = "scatter", mode="markers",
-        x=~speed, 
-        y=~dist)
-Sys.setenv('MAPBOX_TOKEN' = '12423423') # set arbitrary token
-orca(p, "plotly-plot.pdf")
-```
-
-\begin{figure}[H]
-\centering
-\caption{An plotly plot that was exported as PDF with orca before}\label{fig:fig-3}
-		\includegraphics[width=0.9\linewidth]{plotly-plot.pdf}
-\begin{flushleft}
-\end{flushleft}
-\end{figure}
-\vspace{-1.2cm}
-
 # Good practices
@@
 
+## Attach R session info in appendix {#sec:rsessioninfo}
+
+Since R and R packages are constantly evolving you might want to add the R session info that contains information on the R version as well as the packages that are loaded.
+
+```{r echo=FALSE}
+print(sessionInfo(), local = FALSE)
+```
+
 ## All the code in the paper

### 2020-04-05 paper.tex
Took out plotly/orca.
Needs complicated installation...

@@
-\documentclass[12pt,]{article}
+% Options for packages loaded elsewhere
+\PassOptionsToPackage{unicode}{hyperref}
+\PassOptionsToPackage{hyphens}{url}
+\PassOptionsToPackage{dvipsnames,svgnames*,x11names*}{xcolor}
+%
+\documentclass[
+  12pt,
+]{article}
 \usepackage{lmodern}
 \usepackage{setspace}
-\setstretch{1.2}
 \usepackage{amssymb,amsmath}
 \usepackage{ifxetex,ifluatex}
-\usepackage{fixltx2e} % provides \textsubscript
 \ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
@@
   \usepackage[utf8]{inputenc}
-\else % if luatex or xelatex
-  \ifxetex
-    \usepackage{mathspec}
-  \else
-    \usepackage{fontspec}
-  \fi
-  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
+  \usepackage{textcomp} % provide euro and other symbols
+\else % if luatex or xetex
+  \usepackage{unicode-math}
+  \defaultfontfeatures{Scale=MatchLowercase}
+  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
   \setmainfont[]{Times New Roman}
@@
 \fi
-% use upquote if available, for straight quotes in verbatim environments
+% Use upquote if available, for straight quotes in verbatim environments
 \IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-% use microtype if available
-\IfFileExists{microtype.sty}{%
-\usepackage{microtype}
+\IfFileExists{microtype.sty}{% use microtype if available
+  \usepackage[]{microtype}
   \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
 }{}
-\usepackage[margin=1in]{geometry}
-\usepackage{hyperref}
-\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref
-\hypersetup{unicode=true,
+\makeatletter
+\@ifundefined{KOMAClassName}{% if non-KOMA class
+  \IfFileExists{parskip.sty}{%
+    \usepackage{parskip}
+  }{% else
+    \setlength{\parindent}{0pt}
+    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
+}{% if KOMA class
+  \KOMAoptions{parskip=half}}
+\makeatother
+\usepackage{xcolor}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\hypersetup{
   colorlinks=true,
   linkcolor=Maroon,
+  filecolor=Maroon,
   citecolor=Blue,
   urlcolor=Blue,
-            breaklinks=true}
-\urlstyle{same}  % don't use monospace font for urls
+  pdfcreator={LaTeX via pandoc}}
+\urlstyle{same} % disable monospaced font for URLs
+\usepackage[margin=1in]{geometry}
 \usepackage{color}
@@
 \newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
-\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
+\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
+\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
+\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\BuiltInTok}[1]{#1}
+\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
+\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
 \newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
 \newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
+\newcommand{\ExtensionTok}[1]{#1}
 \newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\ImportTok}[1]{#1}
+\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
+\newcommand{\NormalTok}[1]{#1}
+\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
+\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
+\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
+\newcommand{\RegionMarkerTok}[1]{#1}
 \newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
 \newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
 \newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\ImportTok}[1]{#1}
-\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
-\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
-\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
-\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
-\newcommand{\BuiltInTok}[1]{#1}
-\newcommand{\ExtensionTok}[1]{#1}
-\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
-\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
-\newcommand{\RegionMarkerTok}[1]{#1}
-\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
 \newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
-\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
-\newcommand{\NormalTok}[1]{#1}
 \usepackage{longtable,booktabs}
+% Correct order of tables after \paragraph or \subparagraph
+\usepackage{etoolbox}
+\makeatletter
+\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
+\makeatother
+% Allow footnotes in longtable head/foot
+\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
+\makesavenoteenv{longtable}
 \usepackage{graphicx,grffile}
@@
 \setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-\IfFileExists{parskip.sty}{%
-\usepackage{parskip}
-}{% else
-\setlength{\parindent}{0pt}
-\setlength{\parskip}{6pt plus 2pt minus 1pt}
-}
+% Set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
 \setlength{\emergencystretch}{3em} % prevent overfull lines
@@
 \setcounter{secnumdepth}{5}
-% Redefines (sub)paragraphs to behave more like sections
-\ifx\paragraph\undefined\else
-\let\oldparagraph\paragraph
-\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
-\fi
-\ifx\subparagraph\undefined\else
-\let\oldsubparagraph\subparagraph
-\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
-\fi
-
-%%% Use protect on footnotes to avoid problems with footnotes in titles
-\let\rmarkdownfootnote\footnote%
-\def\footnote{\protect\rmarkdownfootnote}
-
-%%% Change title format to be more compact
-\usepackage{titling}
-
-% Create subtitle command for use in maketitle
-\newcommand{\subtitle}[1]{
-  \posttitle{
-    \begin{center}\large#1\end{center}
-    }
-}
-
-\setlength{\droptitle}{-2em}
-
-  \title{\vspace{1cm}Writing a reproducible paper\\
-in R Markdown*\footnote{*Corresponding address:
-  \href{mailto:mail@paulcbauer.eu}{\nolinkurl{mail@paulcbauer.eu}}.
-  Acknowledgments: I am grateful to all those generous people that
-  invest their time into open-source software.}\vspace{0.5cm}\\}
-    \pretitle{\vspace{\droptitle}\centering\huge}
-  \posttitle{\par}
-    \author{Paul C. Bauer\\
-Mannheim Centre for European Social Research}
-    \preauthor{\centering\large\emph}
-  \postauthor{\par}
-      \predate{\centering\large\emph}
-  \postdate{\par}
-    \date{14 December, 2018\\[2\baselineskip]Feedback?\\
-\href{mailto:mail@paulcbauer.eu}{\nolinkurl{mail@paulcbauer.eu}}\\}
-
 \usepackage[english]{babel}
@@
 
-\usepackage[table]{xcolor}
-
 \definecolor{lightred}{rgb}{0.7,0,0}
@@
 \usepackage{multirow}
-\usepackage[table]{xcolor}
 \usepackage{wrapfig}
@@
 \usepackage{makecell}
+\usepackage{xcolor}
 
-\usepackage{dcolumn}
-\usepackage{color}
+\title{\vspace{1cm}Writing a reproducible paper\\
+in R Markdown*\footnote{*Corresponding address: \href{mailto:mail@paulcbauer.eu}{\nolinkurl{mail@paulcbauer.eu}}.
+Acknowledgments: I am grateful to all those generous people that invest their time into open-source software.}\vspace{0.5cm}\\}
+\author{Paul C. Bauer\\
+Mannheim Centre for European Social Research}
+\date{5 April, 2020\\
+~\\
+Feedback?\\
+\href{mailto:mail@paulcbauer.eu}{\nolinkurl{mail@paulcbauer.eu}}\\}
 
-\usepackage{amsthm}
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{lemma}{Lemma}[section]
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}[section]
-\newtheorem{corollary}{Corollary}[section]
-\newtheorem{proposition}{Proposition}[section]
-\theoremstyle{definition}
-\newtheorem{example}{Example}[section]
-\theoremstyle{definition}
-\newtheorem{exercise}{Exercise}[section]
-\theoremstyle{remark}
-\newtheorem*{remark}{Remark}
-\newtheorem*{solution}{Solution}
 \begin{document}
@@
 \begin{abstract}
-\noindent\setstretch{1}The present paper provides a template for a
-reproducible scientific paper written in R Markdown. Below I outline
-some of the ``tricks''/code (e.g., referencing tables, sections etc.) I
-had to figure out to produce this document. The underlying files which
-produce this document can be downloaded
-\href{https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing}{here}.
-I think I got pretty far but there is always room for improvement and
-more automatization, in parallel to the incredible developments in R and
-Rstudio (bookdown etc.). I intend to update this file when I discover
-more convenient code.\vspace{.8cm}
+\noindent\setstretch{1}The present paper provides a template for a reproducible scientific paper written in R Markdown.
+Below I outline some of the ``tricks''/code (e.g., referencing tables, sections etc.) I had to figure out to produce this document.
+The underlying files which produce this document can be downloaded \href{https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing}{here}.
+I think I got pretty far but there is always room for improvement and more automatization, in parallel to the incredible developments in R and Rstudio (bookdown etc.).
+I intend to update this file when I discover more convenient code.\vspace{.8cm}
 \end{abstract}
 
+\setstretch{1.2}
 \clearpage
 
-\renewcommand{\baselinestretch}{0.5}
-
-\normalsize
+\renewcommand{\baselinestretch}{0.5}\normalsize
 \tableofcontents
@@
 
-\section{Why reproducible research (in
-R)?}\label{why-reproducible-research-in-r}
+\hypertarget{why-reproducible-research-in-r}{%
+\section{Why reproducible research (in R)?}\label{why-reproducible-research-in-r}}
 
@@
 \item
-  \textbf{Access}: Research is normally funded by taxpayers (researchers
-  are also taxpayers). Hence, it should be freely accessible to everyone
-  without any barriers, e.g., without requiring commercial software.
-  Importantly, researchers from developing countries are even more
-  dependent on free access to knowledge (Kirsop and Chan
-  \protect\hyperlink{ref-Kirsop2005-ro}{2005}).
+  \textbf{Access}: Research is normally funded by taxpayers (researchers are also taxpayers).
+Hence, it should be freely accessible to everyone without any barriers, e.g., without requiring commercial software.
+Importantly, researchers from developing countries are even more dependent on free access to knowledge (Kirsop and Chan \protect\hyperlink{ref-Kirsop2005-ro}{2005}).
 \item
-  \textbf{Reproducability}: Even if you have written a study and
-  analyzed the data yourself you will forget what you did after a few
-  months. A fully reproducible setup will help you to trace back your
-  own steps. Obviously, the same is true for other researchers who may
-  want to understand your work and built on it. It may sound like a joke
-  but why not aim for a document that can be used to reproduce your
-  findings in 500 years.
+  \textbf{Reproducability}: Even if you have written a study and analyzed the data yourself you will forget what you did after a few months.
+A fully reproducible setup will help you to trace back your own steps.
+Obviously, the same is true for other researchers who may want to understand your work and built on it.
+It may sound like a joke but why not aim for a document that can be used to reproduce your findings in 500 years.
 \item
-  \textbf{Errors}: Manual steps in data analysis (e.g., manually
-  copy/pasting values into a table etc.) may introduce errors. R
-  Markdown allows you to \textbf{automatize} such steps and/or avoid
-  them.
+  \textbf{Errors}: Manual steps in data analysis (e.g., manually copy/pasting values into a table etc.) may introduce errors. R Markdown allows you to \textbf{automatize} such steps and/or avoid them.
 \item
-  \textbf{Revisions}: Revising a paper takes much less time if you have
-  all the code you need in one place, i.e., one \texttt{.rmd} file. For
-  instance, if you decide to exclude a subset of your data you simply
-  need to insert one line of your code at the beginning and everything
-  is rebuilt/re-estimated automatically.
+  \textbf{Revisions}: Revising a paper takes much less time if you have all the code you need in one place, i.e., one \texttt{.rmd} file.
+For instance, if you decide to exclude a subset of your data you simply need to insert one line of your code at the beginning and everything is rebuilt/re-estimated automatically.
 \end{itemize}
 
-\section{Prerequesites}\label{prerequesites}
+\hypertarget{prerequesites}{%
+\section{Prerequesites}\label{prerequesites}}
 
-I assume that you are using R on a day-to-day basis. You may have even
-started to work a little in R Markdown but you don't write your complete
-paper in R Markdown. If you don't know what R Markdown is watch
-\href{https://vimeo.com/178485416}{this short video}. Then\ldots{}
+I assume that you are using R on a day-to-day basis.
+You may have even started to work a little in R Markdown but you don't write your complete paper in R Markdown.
+If you don't know what R Markdown is watch \href{https://vimeo.com/178485416}{this short video}.
+Then\ldots{}
 
@@
 \item
-  \ldots{}install \href{https://www.r-project.org/}{R} and
-  \href{https://www.rstudio.com/}{Rstudio} (most recent versions) (R
-  Core Team \protect\hyperlink{ref-R2017}{2017}; RStudio Team
-  \protect\hyperlink{ref-Rstudio2015}{2015}).
+  \ldots install \href{https://www.r-project.org/}{R} and \href{https://www.rstudio.com/}{Rstudio} (most recent versions) (R Core Team \protect\hyperlink{ref-R2017}{2017}; RStudio Team \protect\hyperlink{ref-Rstudio2015}{2015}).
 \item
-  \ldots{}install \href{https://yihui.name/tinytex/}{tinytex}, a
-  lightweight version of Tex Live (Allaire et al.
-  \protect\hyperlink{ref-markdown2017}{2017}; Xie
-  \protect\hyperlink{ref-tinytex}{2018}\protect\hyperlink{ref-tinytex}{b}).
+  \ldots install \href{https://yihui.name/tinytex/}{tinytex}, a lightweight version of Tex Live (Allaire et al.
+\protect\hyperlink{ref-markdown2017}{2017}; Xie \protect\hyperlink{ref-tinytex}{2018}\protect\hyperlink{ref-tinytex}{b}).
 \end{itemize}
@@
 \item
-  \ldots{}install the packages below using the code below (Sievert et
-  al. \protect\hyperlink{ref-plotly}{2017}; Xie
-  \protect\hyperlink{ref-knitr3}{2014},
-  \protect\hyperlink{ref-knitr2}{2015},
-  \protect\hyperlink{ref-bookdown2}{2016},
-  \protect\hyperlink{ref-bookdown1}{2017},
-  \protect\hyperlink{ref-knitr1}{2018}\protect\hyperlink{ref-knitr1}{a};
-  Zhu \protect\hyperlink{ref-kableextra}{2017}).
+  \ldots install the packages below using the code below (Sievert et al.
+\protect\hyperlink{ref-plotly}{2017}; Xie \protect\hyperlink{ref-knitr3}{2014}, \protect\hyperlink{ref-knitr2}{2015}, \protect\hyperlink{ref-bookdown2}{2016}, \protect\hyperlink{ref-bookdown1}{2017}, \protect\hyperlink{ref-knitr1}{2018}\protect\hyperlink{ref-knitr1}{a}; Zhu \protect\hyperlink{ref-kableextra}{2017}).
 \end{itemize}
@@
 \item
-  \ldots{}download the 5 input files I created --- \texttt{paper.rmd},
-  \texttt{header.tex}, \texttt{references.bib}, \texttt{data.csv} and
-  \texttt{american-sociological-association.csl} --- from
-  \href{https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing}{this
-  folder}. Ignore the other files.
+  \ldots download the 5 input files I created --- \texttt{paper.rmd}, \texttt{header.tex}, \texttt{references.bib}, \texttt{data.csv} and \texttt{american-sociological-association.csl} --- from \href{https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing}{this folder}.
+Ignore the other files.
 \item
-  \ldots{}learn R and read about the other underlying components namely
-  \href{https://en.wikipedia.org/wiki/Markdown}{Markdown},
-  \href{https://rmarkdown.rstudio.com/lesson-1.html}{R Markdown} and
-  \href{https://en.wikipedia.org/wiki/LaTeX}{Latex}.
+  \ldots learn R and read about the other underlying components namely \href{https://en.wikipedia.org/wiki/Markdown}{Markdown}, \href{https://rmarkdown.rstudio.com/lesson-1.html}{R Markdown} and \href{https://en.wikipedia.org/wiki/LaTeX}{Latex}.
 \end{itemize}
 
-\section{Basics: Input and output
-files}\label{basics-input-and-output-files}
+\hypertarget{basics-input-and-output-files}{%
+\section{Basics: Input and output files}\label{basics-input-and-output-files}}
 
-All the files you need to produce the present PDF file are the input
-files\ldots{}
+All the files you need to produce the present PDF file are the input files\ldots{}
 
@@
 \item
-  \ldots{}a \texttt{paper.rmd} file (the underlying R Markdown file).
+  \ldots a \texttt{paper.rmd} file (the underlying R Markdown file).
 \item
-  \ldots{}a \texttt{header.tex} file (a tex file for document
-  structure).
+  \ldots a \texttt{header.tex} file (a tex file for document structure).
 \item
-  \ldots{}a \texttt{references.bib} file (the bibliography).
+  \ldots a \texttt{references.bib} file (the bibliography).
 
@@
   \item
-    I use paperpile to manage my references and export the \texttt{.bib}
-    file into the folder that contains my \texttt{.rmd} file.
+    I use paperpile to manage my references and export the \texttt{.bib} file into the folder that contains my \texttt{.rmd} file.
   \end{itemize}
 \item
-  \ldots{}a \texttt{data.csv} file (some raw data).
+  \ldots a \texttt{data.csv} file (some raw data).
 \item
-  \ldots{} a \texttt{american-sociological-association.csl} file that
-  defines the style of your bibliography.\footnote{You can download
-    various citation style files from this webpage:
-    \url{https://github.com/citation-style-language/styles}.}
+  \ldots{} a \texttt{american-sociological-association.csl} file that defines the style of your bibliography.\footnote{You can download various citation style files from this webpage: \url{https://github.com/citation-style-language/styles}.}
 \end{itemize}
 
-\href{https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing}{Download
-these files} and save them into a folder. Close R/Rstudio and directly
-open \texttt{paper.rmd} with RStudio. Doing so assures that the working
-directory is set to the folder that contains \texttt{paper.rmd} and the
-other files.\footnote{You can always check your working directory in R
-  with \texttt{getwd()}.}
+\href{https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing}{Download these files} and save them into a folder.
+Close R/Rstudio and directly open \texttt{paper.rmd} with RStudio.
+Doing so assures that the working directory is set to the folder that contains \texttt{paper.rmd} and the other files.\footnote{You can always check your working directory in R with \texttt{getwd()}.}
 
-Once you run/compile the \texttt{paper.rmd} file in Rstudio it creates
-mainly two output files:
+Once you run/compile the \texttt{paper.rmd} file in Rstudio it creates mainly two output files:
 
@@
 
-In addition, there may be files that you generate and store locally in
-the folder during the compilation process. This is the case for some of
-the Plotly graphs below.
+In addition, there may be files that you generate and store locally in the folder during the compilation process. This is the case for some of the Plotly graphs below.
 
-Ideally, we can simply provide others with a \texttt{zip} folder that
-contains both our input files and our output files. Then it's possible
-to reproduce the process from managing/analyzing some raw data to
-producing the final scientific article.
+Ideally, we can simply provide others with a \texttt{zip} folder that contains both our input files and our output files.
+Then it's possible to reproduce the process from managing/analyzing some raw data to producing the final scientific article.
 
-Below we always display the R code in the chunks that produce the
-output. In your paper you will normally only present outputs (e.g.,
-tables, figures etc.) by choosing the chunk option ``Show output only''
-in R Studio. The chunk commands itself are not displayed but they do
-matter for referencing etc. So simply orient yourself at the underlying
-\texttt{paper.rmd} file.
+Below we always display the R code in the chunks that produce the output.
+In your paper you will normally only present outputs (e.g., tables, figures etc.) by choosing the chunk option ``Show output only'' in R Studio.
+The chunk commands itself are not displayed but they do matter for referencing etc.
+So simply orient yourself at the underlying \texttt{paper.rmd} file.
 
-\section{Referencing within your
-document}\label{referencing-within-your-document}
+\hypertarget{referencing-within-your-document}{%
+\section{Referencing within your document}\label{referencing-within-your-document}}
 
-To see how referencing works simply see the different examples for
-figures, tables and sections below. For instance in Section
-\ref{sec:tables} you can find different ways of referencing tables. The
-code of the underlying \texttt{paper.rmd} will show you how I referenced
-Section \ref{sec:tables} right here namely with
-`\texttt{Section\ \textbackslash{}@ref(sec:tables)}'.
+To see how referencing works simply see the different examples for figures, tables and sections below.
+For instance in Section \ref{sec:tables} you can find different ways of referencing tables.
+The code of the underlying \texttt{paper.rmd} will show you how I referenced Section \ref{sec:tables} right here namely with `\texttt{Section\ \textbackslash{}@ref(sec:tables)}'.
 
-\section{Software versioning}\label{software-versioning}
+\hypertarget{software-versioning}{%
+\section{Software versioning}\label{software-versioning}}
 
-Software changes and gets updated, especially with an active developer
-community like that of R. Luckily you can always access
-\href{https://cran.r-project.org/bin/windows/base/old/}{old versions of
-R} and old version of R packages in
-\href{https://cran.r-project.org/src/contrib/Archive/}{the archive}. In
-the archive you need to choose a particular package, e.g dplyr and
-search for the right version, e.g., \texttt{dplyr\_0.2.tar.gz}. Then
-insert the path in the following function:
-\texttt{install.packages("https://....../dplyr\_0.2.tar.gz",\ repos=NULL,\ type="source")}.
-Ideally, however, results will be simply reproducible in the most
-current R and package versions.
+Software changes and gets updated, especially with an active developer community like that of R.
+Luckily you can always access \href{https://cran.r-project.org/bin/windows/base/old/}{old versions of R} and old version of R packages in \href{https://cran.r-project.org/src/contrib/Archive/}{the archive}.
+In the archive you need to choose a particular package, e.g dplyr and search for the right version, e.g., \texttt{dplyr\_0.2.tar.gz}.
+Then insert the path in the following function: \texttt{install.packages("https://....../dplyr\_0.2.tar.gz",\ repos=NULL,\ type="source")}.
+Ideally, however, results will be simply reproducible in the most current R and package versions.
 
-I would recommend to use the command below and copy/paste the output
-into the first R chunk in your \texttt{paper.rmd} file. Normally we
-would do this when we compile/generate the paper for the last time. For
-more advanced tools see
-\href{https://rstudio.github.io/packrat/}{packrat}.
+I would recommend to use the command below and simply add it to the appendix as I did here in Appendix \ref{sec:rsessioninfo}.
+This will make sure you always provide the package versions that you used in the last compilation of your paper.
+For more advanced tools see \href{https://rstudio.github.io/packrat/}{packrat}.
 
@@
 \KeywordTok{cat}\NormalTok{(}\KeywordTok{paste}\NormalTok{(}\StringTok{"#"}\NormalTok{, }\KeywordTok{capture.output}\NormalTok{(}\KeywordTok{sessionInfo}\NormalTok{()), }\StringTok{"}\CharTok{\textbackslash{}n}\StringTok{"}\NormalTok{, }\DataTypeTok{collapse =}\StringTok{""}\NormalTok{)) }
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## # R version 3.5.1 (2018-07-02) 
-## # Platform: x86_64-w64-mingw32/x64 (64-bit) 
-## # Running under: Windows 10 x64 (build 17134) 
-## #  
-## # Matrix products: default 
-## #  
-## # locale: 
-## # [1] LC_COLLATE=English_Germany.1252  LC_CTYPE=English_Germany.1252    
-## # [3] LC_MONETARY=English_Germany.1252 LC_NUMERIC=C                     
-## # [5] LC_TIME=English_Germany.1252     
-## #  
-## # attached base packages: 
-## # [1] stats     graphics  grDevices utils     datasets  methods   base      
-## #  
-## # loaded via a namespace (and not attached): 
-## #  [1] compiler_3.5.1  backports_1.1.2 magrittr_1.5    bookdown_0.7    
-## #  [5] rprojroot_1.3-2 tools_3.5.1     htmltools_0.3.6 yaml_2.2.0      
-## #  [9] Rcpp_0.12.19    stringi_1.1.7   rmarkdown_1.10  knitr_1.20      
-## # [13] stringr_1.3.1   xfun_0.3        digest_0.6.18   evaluate_0.12
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
   \CommentTok{# or use message() instead of cat()}
@@
 
-\section{Data}\label{data}
+\hypertarget{data}{%
+\section{Data}\label{data}}
 
-\subsection{Import}\label{import}
+\hypertarget{import}{%
+\subsection{Import}\label{import}}
 
@@
 
-\subsection{Putting your entire data into the .rmd
-file}\label{putting-your-entire-data-into-the-.rmd-file}
+\hypertarget{putting-your-entire-data-into-the-.rmd-file}{%
+\subsection{Putting your entire data into the .rmd file}\label{putting-your-entire-data-into-the-.rmd-file}}
 
-Applying the function \texttt{dput()} to an object gives you the code
-needed to reproduce that object. So you could paste that code into your
-\texttt{.rmd} file if you don't want to have extra data files. This
-makes sense were data files are small.
+Applying the function \texttt{dput()} to an object gives you the code needed to reproduce that object.
+So you could paste that code into your \texttt{.rmd} file if you don't want to have extra data files.
+This makes sense were data files are small.
 
@@
 
-\section{Tables}\label{sec:tables}
+\hypertarget{sec:tables}{%
+\section{Tables}\label{sec:tables}}
 
-Producing good tables and referencing these tables within a R Markdown
-PDF has been a hassle but got much better. Examples that you may use are
-shown below. The way you reference tables is slightly different, e.g.,
-for \texttt{stargazer} the label is contained in the function, for
-\texttt{kable} it's contained in the chunk name.
+Producing good tables and referencing these tables within a R Markdown PDF has been a hassle but got much better.
+Examples that you may use are shown below.
+The way you reference tables is slightly different, e.g., for \texttt{stargazer} the label is contained in the function, for \texttt{kable} it's contained in the chunk name.
 
-\subsection{stargazer(): Summary and regression
-tables}\label{stargazer-summary-and-regression-tables}
+\hypertarget{stargazer-summary-and-regression-tables}{%
+\subsection{stargazer(): Summary and regression tables}\label{stargazer-summary-and-regression-tables}}
 
-Table \ref{tab1} shows summary stats of your data.\footnote{To reference
-  the table where you set the identifier in the stargazer function you
-  only need to use the actual label, i.e., ´tab1´.} I normally use
-\texttt{stargazer()} (Hlavac
-\protect\hyperlink{ref-hlavac2013stargazer}{2013}) which offers extreme
-flexibility regarding table output (see \texttt{?stargazer}).
+Table \ref{tab1} shows summary stats of your data.\footnote{To reference the table where you set the identifier in the stargazer function you only need to use the actual label, i.e., ´tab1´.} I normally use \texttt{stargazer()} (Hlavac \protect\hyperlink{ref-hlavac2013stargazer}{2013}) which offers extreme flexibility regarding table output (see \texttt{?stargazer}).
 
@@
 
-Table \ref{tab2} shows the output for a regression table. Make sure you
-name all your models and explicitly refer to model names (M1, M2 etc.)
-in the text.
+Table \ref{tab2} shows the output for a regression table. Make sure you name all your models and explicitly refer to model names (M1, M2 etc.) in the text.
 
@@
 
-\subsection{kable() and kable\_styling()}\label{kable-and-kable_styling}
+\hypertarget{kable-and-kable_styling}{%
+\subsection{kable() and kable\_styling()}\label{kable-and-kable_styling}}
 
-Another great function is \texttt{kable()} (\texttt{knitr} package) in
-combination with \texttt{kableExtra}. Table \ref{tab:tab3} provides an
-example.\footnote{To reference the table produced by the chunk you need
-  to add ´tab:´ to the chunk name, i.e., ´tab:tab3´.} Again you can
-modify so many things in both the \texttt{kable()} and the
-\texttt{kable\_styling()} function. See
-\href{https://haozhu233.github.io/kableExtra/awesome_table_in_pdf.pdf}{this
-overview} of all the kable stylings that are possible provided by the
-package author himself.
+Another great function is \texttt{kable()} (\texttt{knitr} package) in combination with \texttt{kableExtra}.
+Table \ref{tab:tab3} provides an example.\footnote{To reference the table produced by the chunk you need to add ´tab:´ to the chunk name, i.e., ´tab:tab3´.} Again you can modify so many things in both the \texttt{kable()} and the \texttt{kable\_styling()} function.
+See \href{https://haozhu233.github.io/kableExtra/awesome_table_in_pdf.pdf}{this overview} of all the kable stylings that are possible provided by the package author himself.
 
@@
 
-\rowcolors{2}{gray!6}{white}
-
 \begin{table}[H]
@@
 \begin{tabu} to \linewidth {>{\raggedright}X>{\raggedleft}X>{\raggedleft}X}
-\hiderowcolors
 \toprule
@@
 \midrule
-\showrowcolors
-1 & 4 & 2\\
+\rowcolor{gray!6}  1 & 4 & 2\\
 2 & 4 & 10\\
-3 & 7 & 4\\
+\rowcolor{gray!6}  3 & 7 & 4\\
 4 & 7 & 22\\
-5 & 8 & 16\\
+\rowcolor{gray!6}  5 & 8 & 16\\
 \addlinespace
 6 & 9 & 10\\
-7 & 10 & 18\\
+\rowcolor{gray!6}  7 & 10 & 18\\
 8 & 10 & 26\\
-9 & 10 & 34\\
+\rowcolor{gray!6}  9 & 10 & 34\\
 10 & 11 & 17\\
@@
 
-\rowcolors{2}{white}{white}
+\hypertarget{inline-code-results}{%
+\section{Inline code \& results}\label{inline-code-results}}
 
-\section{Inline code \& results}\label{inline-code-results}
+Reproduction reaches new heights when you work with inline code.
+For instance, you can automatize the display of certain coefficients within the text.
+An example is to include estimates, e.g., the coefficient of \texttt{dist} of the model we ran above.
+\texttt{\textasciigrave{}r\ round(coef(model1){[}2{]},\ 2)\textasciigrave{}} will insert the coefficient as follows: 0.17.
+Or \texttt{\textasciigrave{}r\ 3\ +\ 7\textasciigrave{}} will insert a 10 in the text.\\
+Inline code/results that depend on earlier objects in your document will automatically be updated once you change those objects.
+For instance, imagine a reviewer asks you to omit certain observations from your sample.
+You can simply do so in the beginning of your code and push play subsequently..
+at time you might have to set \texttt{cache\ =\ FALSE} at the beginning so that all the code chunks are rerun.\\
+Researchers often avoid referring to results in-text etc.
+because you easily forget to change them when revising a manuscript.
+At the same it can make an article much more informative and easier to read, e.g., if you discuss a coefficient in the text you can directly show it in the section in which you discuss it.
+Inline code allows you to do just that.
+R Markdown allows you to that do so in a reproducible and automatized manner.
 
-Reproduction reaches new heights when you work with inline code. For
-instance, you can automatize the display of certain coefficients within
-the text. An example is to include estimates, e.g., the coefficient of
-\texttt{dist} of the model we ran above.
-\texttt{\textasciigrave{}r\ round(coef(model1){[}2{]},\ 2)\textasciigrave{}}
-will insert the coefficient as follows: 0.17. Or
-\texttt{\textasciigrave{}r\ 3\ +\ 7\textasciigrave{}} will insert a 10
-in the text.\\
-Inline code/results that depend on earlier objects in your document will
-automatically be updated once you change those objects. For instance,
-imagine a reviewer asks you to omit certain observations from your
-sample. You can simply do so in the beginning of your code and push play
-subsequently.. at time you might have to set \texttt{cache\ =\ FALSE} at
-the beginning so that all the code chunks are rerun.\\
-Researchers often avoid referring to results in-text etc. because you
-easily forget to change them when revising a manuscript. At the same it
-can make an article much more informative and easier to read, e.g., if
-you discuss a coefficient in the text you can directly show it in the
-section in which you discuss it. Inline code allows you to do just that.
-R Markdown allows you to that do so in a reproducible and automatized
-manner.
+\hypertarget{figures}{%
+\section{Figures}\label{figures}}
 
-\section{Figures}\label{figures}
+\hypertarget{r-base-graphs}{%
+\subsection{R base graphs}\label{r-base-graphs}}
 
-\subsection{R base graphs}\label{r-base-graphs}
-
-Inserting figures can be slightly more complicated. Ideally, we would
-produce and insert them directly in the \texttt{.rmd} file. It's
-relatively simple to insert R base graphs as you can see in Figure
-\ref{fig:fig-1}.
+Inserting figures can be slightly more complicated.
+Ideally, we would produce and insert them directly in the \texttt{.rmd} file.
+It's relatively simple to insert R base graphs as you can see in Figure \ref{fig:fig-1}.
 
@@
 
-\subsection{ggplot2 graphs}\label{ggplot2-graphs}
+\hypertarget{ggplot2-graphs}{%
+\subsection{ggplot2 graphs}\label{ggplot2-graphs}}
 
@@
 
-\subsection{Plotly graphs}\label{plotly-graphs}
+\hypertarget{good-practices}{%
+\section{Good practices}\label{good-practices}}
 
-Plotly is a popular graph engine that let's you also produce interactive
-graphs that you can embed in html webpages or documents (e.g., see
-\href{https://paulcbauer.shinyapps.io/visualizing-causal-scenarios/}{here}).
-I am a big fan. For some time there was no easy, automatic way to insert
-high resolution Plotly graphs into your R Markdown PDF. However, this
-changed since Plotly provided Orca, a command line application for
-generating static images from Plotly graphs. The installation is a bit
-tricky (see here: \url{https://github.com/plotly/orca\#installation})
-but once you get it running you can produce beautiful graphs and include
-them in your RMarkdown PDF using some simple latex as shown below in
-Figure \ref{fig:fig-3}. Potentially, in case you did not install the
-command line application this part may fail. If so simply exclude the
-chunk and the latex code.
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\KeywordTok{library}\NormalTok{(plotly)}
-\NormalTok{p <-}\StringTok{ }\KeywordTok{plot_ly}\NormalTok{(cars, }\DataTypeTok{type =} \StringTok{"scatter"}\NormalTok{, }\DataTypeTok{mode=}\StringTok{"markers"}\NormalTok{,}
-        \DataTypeTok{x=}\OperatorTok{~}\NormalTok{speed, }
-        \DataTypeTok{y=}\OperatorTok{~}\NormalTok{dist)}
-\KeywordTok{Sys.setenv}\NormalTok{(}\StringTok{'MAPBOX_TOKEN'}\NormalTok{ =}\StringTok{ '12423423'}\NormalTok{) }\CommentTok{# set arbitrary token}
-\KeywordTok{orca}\NormalTok{(p, }\StringTok{"plotly-plot.pdf"}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{figure}[H]
-\centering
-\caption{An plotly plot that was exported as PDF with orca before}\label{fig:fig-3}
-        \includegraphics[width=0.9\linewidth]{plotly-plot.pdf}
-\begin{flushleft}
-\end{flushleft}
-\end{figure}
-
-\vspace{-1.2cm}
-
-\section{Good practices}\label{good-practices}
-
-Every researcher has his own optimized setup. Currently I would
-recommend the following:
+Every researcher has his own optimized setup. Currently I would recommend the following:
 
@@
 \item
-  Keep all files of your project (that matter for producing the PDF) in
-  one folder without subfolders. You can zip and directly upload that
-  folder to the \href{https://dataverse.harvard.edu/}{Harvard
-  dataverse}.
+  Keep all files of your project (that matter for producing the PDF) in one folder without subfolders.
+You can zip and directly upload that folder to the \href{https://dataverse.harvard.edu/}{Harvard dataverse}.
 \item
@@
   \item
-    Data files: ``data\_xxxxxx.*"
+    Data files: "data\_xxxxxx.*"
   \item
-    Image files: ``fig\_xxxxxx.*"
+    Image files: "fig\_xxxxxx.*"
   \item
-    Tables files: ``table\_xxxx.*"
+    Tables files: "table\_xxxx.*"
   \item
@@
   \item
-    Ideally, your filenames will correspond to the names in the paper.
-    For instance, Figure 1 in the paper may have a corresponding file
-    called \texttt{fig\_1\_xxxxx.pdf}.
+    Ideally, your filenames will correspond to the names in the paper. For instance, Figure 1 in the paper may have a corresponding file called \texttt{fig\_1\_xxxxx.pdf}.
   \end{itemize}
 \item
-  Use the document outline in R studio (Ctrl + Shift + O) when you work
-  with R Markdown.
+  Use the document outline in R studio (Ctrl + Shift + O) when you work with R Markdown.
 \item
@@
   \item
-    Q: What do you think does the variable \emph{trstep} measure? It
-    actually measures trust in the European parliament.
+    Q: What do you think does the variable \emph{trstep} measure? It actually measures trust in the European parliament.
 
@@
     \item
-      How could we call this variable instead? Yes,
-      \texttt{trust.european.parliament} which is longer but will
-      probably be understood by another researcher.
+      How could we call this variable instead? Yes, \texttt{trust.european.parliament} which is longer but will probably be understood by another researcher.
     \end{itemize}
   \item
-    If your setup is truly reproducible you will probably re-use the
-    variable names that you generate as variable names in the tables you
-    produce. Hence, there is an incentive to use good names.
+    If your setup is truly reproducible you will probably re-use the variable names that you generate as variable names in the tables you produce. Hence, there is an incentive to use good names.
   \end{itemize}
@@
   \item
-    Think of someone who wants to produce Figure 1/Model 1 in your paper
-    but doesn't find it in your code\ldots{}
+    Think of someone who wants to produce Figure 1/Model 1 in your paper but doesn't find it in your code\ldots{}
   \end{itemize}
@@
 
-\section{Citation styles}\label{citation-styles}
+\hypertarget{citation-styles}{%
+\section{Citation styles}\label{citation-styles}}
 
-If your study needs to follow a particular citation style, you can set
-the corresponding style in the header of your \texttt{.rmd} document. To
-do so you have to download the corresponding \texttt{.csl} file.
+If your study needs to follow a particular citation style, you can set the corresponding style in the header of your \texttt{.rmd} document.
+To do so you have to download the corresponding \texttt{.csl} file.
 
-In the present document we use the style of the American Sociological
-Association and set it in the preamble with
-\texttt{csl:\ american-sociological-association.csl}. However, you also
-need to download the respective \texttt{.csl} file from the following
-github page: \url{https://github.com/citation-style-language/styles} and
-copy it into your working directory for it to work.
+In the present document we use the style of the American Sociological Association and set it in the preamble with \texttt{csl:\ american-sociological-association.csl}.
+However, you also need to download the respective \texttt{.csl} file from the following github page: \url{https://github.com/citation-style-language/styles} and copy it into your working directory for it to work.
 
-The github directory contains a wide variety of citation style files
-depending on what discipline you work in.
+The github directory contains a wide variety of citation style files depending on what discipline you work in.
 
-\section{Appendix}\label{appendix}
+\hypertarget{appendix}{%
+\section{Appendix}\label{appendix}}
 
-\subsection{All the code in the paper}\label{all-the-code-in-the-paper}
+\hypertarget{sec:rsessioninfo}{%
+\subsection{Attach R session info in appendix}\label{sec:rsessioninfo}}
 
-To simply attach all the code you used in the PDF file in the appendix
-see the R chunk in the underlying \texttt{.rmd} file:
+Since R and R packages are constantly evolving you might want to add the R session info that contains information on the R version as well as the packages that are loaded.
+
+\begin{verbatim}
+## R version 3.6.2 (2019-12-12)
+## Platform: x86_64-w64-mingw32/x64 (64-bit)
+## Running under: Windows 10 x64 (build 17763)
+## 
+## Matrix products: default
+## 
+## attached base packages:
+## [1] stats     graphics  grDevices utils     datasets  methods   base     
+## 
+## other attached packages:
+## [1] ggplot2_3.2.1    kableExtra_1.1.0 knitr_1.26       stargazer_5.2.2 
+## 
+## loaded via a namespace (and not attached):
+##  [1] Rcpp_1.0.3        pillar_1.4.3      compiler_3.6.2    tools_3.6.2      
+##  [5] digest_0.6.23     evaluate_0.14     tibble_2.1.3      lifecycle_0.2.0  
+##  [9] gtable_0.3.0      viridisLite_0.3.0 pkgconfig_2.0.3   rlang_0.4.5      
+## [13] rstudioapi_0.10   yaml_2.2.0        xfun_0.11         withr_2.1.2      
+## [17] dplyr_0.8.3       httr_1.4.1        stringr_1.4.0     xml2_1.2.2       
+## [21] vctrs_0.2.4       hms_0.5.2         tidyselect_0.2.5  webshot_0.5.2    
+## [25] grid_3.6.2        glue_1.3.2        R6_2.4.1          rmarkdown_2.0    
+## [29] bookdown_0.16     farver_2.0.1      purrr_0.3.3       readr_1.3.1      
+## [33] magrittr_1.5      scales_1.1.0      htmltools_0.4.0   assertthat_0.2.1 
+## [37] rvest_0.3.5       colorspace_1.4-1  labeling_0.3      stringi_1.4.3    
+## [41] lazyeval_0.2.2    munsell_0.5.0     crayon_1.3.4
+\end{verbatim}
+
+\hypertarget{all-the-code-in-the-paper}{%
+\subsection{All the code in the paper}\label{all-the-code-in-the-paper}}
+
+To simply attach all the code you used in the PDF file in the appendix see the R chunk in the underlying \texttt{.rmd} file:
 
@@
        \DataTypeTok{shape=}\StringTok{"Number of }\CharTok{\textbackslash{}n}\StringTok{ Cylinders"}\NormalTok{) }\OperatorTok{+}\StringTok{ }\KeywordTok{theme_classic}\NormalTok{()}
-\KeywordTok{library}\NormalTok{(plotly)}
-\NormalTok{p <-}\StringTok{ }\KeywordTok{plot_ly}\NormalTok{(cars, }\DataTypeTok{type =} \StringTok{"scatter"}\NormalTok{, }\DataTypeTok{mode=}\StringTok{"markers"}\NormalTok{,}
-        \DataTypeTok{x=}\OperatorTok{~}\NormalTok{speed, }
-        \DataTypeTok{y=}\OperatorTok{~}\NormalTok{dist)}
-\KeywordTok{Sys.setenv}\NormalTok{(}\StringTok{'MAPBOX_TOKEN'}\NormalTok{ =}\StringTok{ '12423423'}\NormalTok{) }\CommentTok{# set arbitrary token}
-\KeywordTok{orca}\NormalTok{(p, }\StringTok{"plotly-plot.pdf"}\NormalTok{)}
+\KeywordTok{print}\NormalTok{(}\KeywordTok{sessionInfo}\NormalTok{(), }\DataTypeTok{local =} \OtherTok{FALSE}\NormalTok{)}
 \end{Highlighting}
@@
 
-\section*{References}\label{references}
+\hypertarget{references}{%
+\section*{References}\label{references}}
 \addcontentsline{toc}{section}{References}
@@
 \hypertarget{refs}{}
-\hypertarget{ref-markdown2017}{}
-Allaire, JJ, Jeffrey Horner, Vicent Marti, and Natacha Porte. 2017.
-\emph{Markdown: 'Markdown' Rendering for R}.
+\leavevmode\hypertarget{ref-markdown2017}{}%
+Allaire, JJ, Jeffrey Horner, Vicent Marti, and Natacha Porte. 2017. \emph{Markdown: 'Markdown' Rendering for R}.
 
-\hypertarget{ref-hlavac2013stargazer}{}
-Hlavac, Marek. 2013. ``Stargazer: LaTeX Code and Ascii Text for
-Well-Formatted Regression and Summary Statistics Tables.'' \emph{URL:
-Http://CRAN. R-Project. Org/Package= Stargazer}.
+\leavevmode\hypertarget{ref-hlavac2013stargazer}{}%
+Hlavac, Marek. 2013. ``Stargazer: LaTeX Code and Ascii Text for Well-Formatted Regression and Summary Statistics Tables.'' \emph{URL: Http://CRAN. R-Project. Org/Package= Stargazer}.
 
-\hypertarget{ref-Kirsop2005-ro}{}
-Kirsop, Barbara and Leslie Chan. 2005. ``Transforming Access to Research
-Literature for Developing Countries.'' \emph{Serials Review}
-31(4):246--55.
+\leavevmode\hypertarget{ref-Kirsop2005-ro}{}%
+Kirsop, Barbara and Leslie Chan. 2005. ``Transforming Access to Research Literature for Developing Countries.'' \emph{Serials Review} 31(4):246--55.
 
-\hypertarget{ref-R2017}{}
-R Core Team. 2017. \emph{R: A Language and Environment for Statistical
-Computing}. Vienna, Austria: R Foundation for Statistical Computing.
+\leavevmode\hypertarget{ref-R2017}{}%
+R Core Team. 2017. \emph{R: A Language and Environment for Statistical Computing}. Vienna, Austria: R Foundation for Statistical Computing.
 
-\hypertarget{ref-Rstudio2015}{}
-RStudio Team. 2015. \emph{RStudio: Integrated Development Environment
-for R}. Boston, MA: RStudio, Inc.
+\leavevmode\hypertarget{ref-Rstudio2015}{}%
+RStudio Team. 2015. \emph{RStudio: Integrated Development Environment for R}. Boston, MA: RStudio, Inc.
 
-\hypertarget{ref-plotly}{}
-Sievert, Carson, Chris Parmer, Toby Hocking, Scott Chamberlain, Karthik
-Ram, Marianne Corvellec, and Pedro Despouy. 2017. \emph{Plotly: Create
-Interactive Web Graphics via 'Plotly.js'}.
+\leavevmode\hypertarget{ref-plotly}{}%
+Sievert, Carson, Chris Parmer, Toby Hocking, Scott Chamberlain, Karthik Ram, Marianne Corvellec, and Pedro Despouy. 2017. \emph{Plotly: Create Interactive Web Graphics via 'Plotly.js'}.
 
-\hypertarget{ref-knitr3}{}
-Xie, Yihui. 2014. ``Knitr: A Comprehensive Tool for Reproducible
-Research in R.'' in \emph{Implementing reproducible computational
-research}, edited by V. Stodden, F. Leisch, and R. D. Peng. Chapman;
-Hall/CRC.
+\leavevmode\hypertarget{ref-knitr3}{}%
+Xie, Yihui.
+2014.
+``Knitr: A Comprehensive Tool for Reproducible Research in R.'' in \emph{Implementing reproducible computational research}, edited by V.
+Stodden, F.
+Leisch, and R.
+D.
+Peng.
+Chapman; Hall/CRC.
 
-\hypertarget{ref-knitr2}{}
-Xie, Yihui. 2015. \emph{Dynamic Documents with R and Knitr}. 2nd ed.
-Boca Raton, Florida: Chapman; Hall/CRC.
+\leavevmode\hypertarget{ref-knitr2}{}%
+Xie, Yihui. 2015. \emph{Dynamic Documents with R and Knitr}. 2nd ed. Boca Raton, Florida: Chapman; Hall/CRC.
 
-\hypertarget{ref-bookdown2}{}
-Xie, Yihui. 2016. \emph{Bookdown: Authoring Books and Technical
-Documents with R Markdown}. Boca Raton, Florida: Chapman; Hall/CRC.
+\leavevmode\hypertarget{ref-bookdown2}{}%
+Xie, Yihui. 2016. \emph{Bookdown: Authoring Books and Technical Documents with R Markdown}. Boca Raton, Florida: Chapman; Hall/CRC.
 
-\hypertarget{ref-bookdown1}{}
-Xie, Yihui. 2017. \emph{Bookdown: Authoring Books and Technical
-Documents with R Markdown}.
+\leavevmode\hypertarget{ref-bookdown1}{}%
+Xie, Yihui. 2017. \emph{Bookdown: Authoring Books and Technical Documents with R Markdown}.
 
-\hypertarget{ref-knitr1}{}
-Xie, Yihui. 2018a. \emph{Knitr: A General-Purpose Package for Dynamic
-Report Generation in R}.
+\leavevmode\hypertarget{ref-knitr1}{}%
+Xie, Yihui. 2018a. \emph{Knitr: A General-Purpose Package for Dynamic Report Generation in R}.
 
-\hypertarget{ref-tinytex}{}
-Xie, Yihui. 2018b. \emph{Tinytex: Helper Functions to Install and
-Maintain 'Tex Live', and Compile 'Latex' Documents}.
+\leavevmode\hypertarget{ref-tinytex}{}%
+Xie, Yihui. 2018b. \emph{Tinytex: Helper Functions to Install and Maintain 'Tex Live', and Compile 'Latex' Documents}.
 
-\hypertarget{ref-kableextra}{}
-Zhu, Hao. 2017. \emph{KableExtra: Construct Complex Table with 'Kable'
-and Pipe Syntax}.
+\leavevmode\hypertarget{ref-kableextra}{}%
+Zhu, Hao. 2017. \emph{KableExtra: Construct Complex Table with 'Kable' and Pipe Syntax}.
 

### 2020-04-05 paper.Rmd
Added link to github repo.

@@
 I think I got pretty far but there is always room for improvement and more automatization, in parallel to the incredible developments in R and Rstudio (bookdown etc.).
-I intend to update this file when I discover more convenient code.\vspace{.8cm}
+I intend to update this file when I discover more convenient code (you can follow any updates through the corresponding [github repo](https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown/)).\vspace{.8cm}
 bibliography: references.bib

### 2020-04-05 paper.tex
Added link to github repo.

@@
 I think I got pretty far but there is always room for improvement and more automatization, in parallel to the incredible developments in R and Rstudio (bookdown etc.).
-I intend to update this file when I discover more convenient code.\vspace{.8cm}
+I intend to update this file when I discover more convenient code (you can follow any updates through the corresponding \href{https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown/}{github repo}).\vspace{.8cm}
 \end{abstract}

### 2020-04-05 paper.Rmd
Added appendix with different numbering

@@
 
+# Additional tricks for publishing
+* Make your script anonymous
+    + Simply put a `<!-- ... -->` around any identifying information, e.g., author names, title footnote etc.
+* Counting words
+    + Use adobe acrobat (commerical software) to convert your file to a word file.
+Then open in word and delete all the parts that shouldn't go into the word count.
+The word count is displayed in the lower right.
+    + Use an one of the online services to count your words (search for "pdf word count")
+
 # Citation styles
@@
 
-# Appendix
+# References
+
+\linespread{1}
+
+::: {#refs}
+
+:::
+
+\clearpage
+
+\appendix
+\addtocontents{toc}{\protect\setcounter{tocdepth}{2}}
+
+\renewcommand{\thesection}{A}
+
+\setcounter{page}{1}
+
+\setcounter{table}{0}
+\renewcommand{\thetable}{A\arabic{table}}
+\renewcommand{\figurename}{Table}
+
+\setcounter{figure}{0}
+\renewcommand\thefigure{A\arabic{figure}}
+\renewcommand{\figurename}{Figure}
+
+\clearpage
+\pagenumbering{gobble}
+
+\vspace*{7cm}
+
+\begin{center}
+\begin{huge}
+Online Appendix
+\end{huge}
+\end{center}
+\vspace{3cm}
+
+\clearpage
 
@@
 ```
-
-# References

### 2020-04-05 paper.tex
Added appendix with different numbering

@@
 
+\hypertarget{additional-tricks-for-publishing}{%
+\section{Additional tricks for publishing}\label{additional-tricks-for-publishing}}
+
+\begin{itemize}
+\tightlist
+\item
+  Make your script anonymous
+
+  \begin{itemize}
+  \tightlist
+  \item
+    Simply put a \texttt{\textless{}!-\/-\ ...\ -\/-\textgreater{}} around any identifying information, e.g., author names, title footnote etc.
+  \end{itemize}
+\item
+  Counting words
+
+  \begin{itemize}
+  \tightlist
+  \item
+    Use adobe acrobat (commerical software) to convert your file to a word file.
+Then open in word and delete all the parts that shouldn't go into the word count.
+The word count is displayed in the lower right.
+  \item
+    Use an one of the online services to count your words (search for ``pdf word count'')
+  \end{itemize}
+\end{itemize}
+
 \hypertarget{citation-styles}{%
@@
 
-\hypertarget{appendix}{%
-\section{Appendix}\label{appendix}}
+\hypertarget{references}{%
+\section{References}\label{references}}
+
+\linespread{1}
+
+\hypertarget{refs}{}
+\leavevmode\hypertarget{ref-markdown2017}{}%
+Allaire, JJ, Jeffrey Horner, Vicent Marti, and Natacha Porte. 2017. \emph{Markdown: 'Markdown' Rendering for R}.
+
+\leavevmode\hypertarget{ref-hlavac2013stargazer}{}%
+Hlavac, Marek. 2013. ``Stargazer: LaTeX Code and Ascii Text for Well-Formatted Regression and Summary Statistics Tables.'' \emph{URL: Http://CRAN. R-Project. Org/Package= Stargazer}.
+
+\leavevmode\hypertarget{ref-Kirsop2005-ro}{}%
+Kirsop, Barbara and Leslie Chan. 2005. ``Transforming Access to Research Literature for Developing Countries.'' \emph{Serials Review} 31(4):246--55.
+
+\leavevmode\hypertarget{ref-R2017}{}%
+R Core Team. 2017. \emph{R: A Language and Environment for Statistical Computing}. Vienna, Austria: R Foundation for Statistical Computing.
+
+\leavevmode\hypertarget{ref-Rstudio2015}{}%
+RStudio Team. 2015. \emph{RStudio: Integrated Development Environment for R}. Boston, MA: RStudio, Inc.
+
+\leavevmode\hypertarget{ref-plotly}{}%
+Sievert, Carson, Chris Parmer, Toby Hocking, Scott Chamberlain, Karthik Ram, Marianne Corvellec, and Pedro Despouy. 2017. \emph{Plotly: Create Interactive Web Graphics via 'Plotly.js'}.
+
+\leavevmode\hypertarget{ref-knitr3}{}%
+Xie, Yihui.
+2014.
+``Knitr: A Comprehensive Tool for Reproducible Research in R.'' in \emph{Implementing reproducible computational research}, edited by V.
+Stodden, F.
+Leisch, and R.
+D.
+Peng.
+Chapman; Hall/CRC.
+
+\leavevmode\hypertarget{ref-knitr2}{}%
+Xie, Yihui. 2015. \emph{Dynamic Documents with R and Knitr}. 2nd ed. Boca Raton, Florida: Chapman; Hall/CRC.
+
+\leavevmode\hypertarget{ref-bookdown2}{}%
+Xie, Yihui. 2016. \emph{Bookdown: Authoring Books and Technical Documents with R Markdown}. Boca Raton, Florida: Chapman; Hall/CRC.
+
+\leavevmode\hypertarget{ref-bookdown1}{}%
+Xie, Yihui. 2017. \emph{Bookdown: Authoring Books and Technical Documents with R Markdown}.
+
+\leavevmode\hypertarget{ref-knitr1}{}%
+Xie, Yihui. 2018a. \emph{Knitr: A General-Purpose Package for Dynamic Report Generation in R}.
+
+\leavevmode\hypertarget{ref-tinytex}{}%
+Xie, Yihui. 2018b. \emph{Tinytex: Helper Functions to Install and Maintain 'Tex Live', and Compile 'Latex' Documents}.
+
+\leavevmode\hypertarget{ref-kableextra}{}%
+Zhu, Hao. 2017. \emph{KableExtra: Construct Complex Table with 'Kable' and Pipe Syntax}.
+
+\clearpage
+
+\appendix
+\addtocontents{toc}{\protect\setcounter{tocdepth}{2}}
+
+\renewcommand{\thesection}{A}
+
+\setcounter{page}{1}
+
+\setcounter{table}{0}
+\renewcommand{\thetable}{A\arabic{table}}
+\renewcommand{\figurename}{Table}
+
+\setcounter{figure}{0}
+\renewcommand\thefigure{A\arabic{figure}}
+\renewcommand{\figurename}{Figure}
+
+\clearpage
+\pagenumbering{gobble}
+
+\vspace*{7cm}
+
+\begin{center}
+\begin{huge}
+Online Appendix
+\end{huge}
+\end{center}
+\vspace{3cm}
+
+\clearpage
 
@@
 
-\hypertarget{references}{%
-\section*{References}\label{references}}
-\addcontentsline{toc}{section}{References}
-
-\hypertarget{refs}{}
-\leavevmode\hypertarget{ref-markdown2017}{}%
-Allaire, JJ, Jeffrey Horner, Vicent Marti, and Natacha Porte. 2017. \emph{Markdown: 'Markdown' Rendering for R}.
-
-\leavevmode\hypertarget{ref-hlavac2013stargazer}{}%
-Hlavac, Marek. 2013. ``Stargazer: LaTeX Code and Ascii Text for Well-Formatted Regression and Summary Statistics Tables.'' \emph{URL: Http://CRAN. R-Project. Org/Package= Stargazer}.
-
-\leavevmode\hypertarget{ref-Kirsop2005-ro}{}%
-Kirsop, Barbara and Leslie Chan. 2005. ``Transforming Access to Research Literature for Developing Countries.'' \emph{Serials Review} 31(4):246--55.
-
-\leavevmode\hypertarget{ref-R2017}{}%
-R Core Team. 2017. \emph{R: A Language and Environment for Statistical Computing}. Vienna, Austria: R Foundation for Statistical Computing.
-
-\leavevmode\hypertarget{ref-Rstudio2015}{}%
-RStudio Team. 2015. \emph{RStudio: Integrated Development Environment for R}. Boston, MA: RStudio, Inc.
-
-\leavevmode\hypertarget{ref-plotly}{}%
-Sievert, Carson, Chris Parmer, Toby Hocking, Scott Chamberlain, Karthik Ram, Marianne Corvellec, and Pedro Despouy. 2017. \emph{Plotly: Create Interactive Web Graphics via 'Plotly.js'}.
-
-\leavevmode\hypertarget{ref-knitr3}{}%
-Xie, Yihui.
-2014.
-``Knitr: A Comprehensive Tool for Reproducible Research in R.'' in \emph{Implementing reproducible computational research}, edited by V.
-Stodden, F.
-Leisch, and R.
-D.
-Peng.
-Chapman; Hall/CRC.
-
-\leavevmode\hypertarget{ref-knitr2}{}%
-Xie, Yihui. 2015. \emph{Dynamic Documents with R and Knitr}. 2nd ed. Boca Raton, Florida: Chapman; Hall/CRC.
-
-\leavevmode\hypertarget{ref-bookdown2}{}%
-Xie, Yihui. 2016. \emph{Bookdown: Authoring Books and Technical Documents with R Markdown}. Boca Raton, Florida: Chapman; Hall/CRC.
-
-\leavevmode\hypertarget{ref-bookdown1}{}%
-Xie, Yihui. 2017. \emph{Bookdown: Authoring Books and Technical Documents with R Markdown}.
-
-\leavevmode\hypertarget{ref-knitr1}{}%
-Xie, Yihui. 2018a. \emph{Knitr: A General-Purpose Package for Dynamic Report Generation in R}.
-
-\leavevmode\hypertarget{ref-tinytex}{}%
-Xie, Yihui. 2018b. \emph{Tinytex: Helper Functions to Install and Maintain 'Tex Live', and Compile 'Latex' Documents}.
-
-\leavevmode\hypertarget{ref-kableextra}{}%
-Zhu, Hao. 2017. \emph{KableExtra: Construct Complex Table with 'Kable' and Pipe Syntax}.
-
 \end{document}

### 2020-04-05 paper.Rmd
Edits to appendix.

@@
     + Use an one of the online services to count your words (search for "pdf word count")
+* Appendix: You can change the numbering format for the appendix in the rmd file
+    + What is still not possible in this document is to automatically have separate reference sections for paper and appendix.
 
@@
 \clearpage
+\pagenumbering{arabic}
+
+# Online appendix
 

### 2020-04-05 paper.tex
Edits to appendix.
Added link to PLOS One example.

@@
   \end{itemize}
+\item
+  Appendix: You can change the numbering format for the appendix in the rmd file
+
+  \begin{itemize}
+  \tightlist
+  \item
+    What is still not possible in this document is to automatically have separate reference sections for paper and appendix.
+  \end{itemize}
+\item
+  Journals may require you to use their tex style: Sometimes you can simply use their template in your rmarkdown file.
+See \href{https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/LDUMNY}{here} for a PLOS one example.
 \end{itemize}
@@
 \clearpage
+\pagenumbering{arabic}
+
+\hypertarget{online-appendix}{%
+\section{Online appendix}\label{online-appendix}}
 

### 2020-07-08 paper.Rmd
Added link to PLOS One example.
Deleted header.tex because of errors.

@@
   |       
-  |
-  | `r gsub("^0", "", format(Sys.time(), "%d %B, %Y"))`
+  | First version: December 14, 2018
+  | This version: `r gsub("^0", "", format(Sys.time(), "%B %d, %Y"))`
   |
@@
   bookdown::pdf_document2:
-    includes:
-      in_header: header.tex
     toc: no
@@
 ```
-* ...download the 5 input files I created --- `paper.rmd`, `header.tex`, `references.bib`, `data.csv` and `american-sociological-association.csl` --- from [this folder](https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing).
+* ...download the 5 input files I created --- `paper.rmd`, `references.bib`, `data.csv` and `american-sociological-association.csl` --- from [this folder](https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing).
 Ignore the other files.
@@
 * ...a `paper.rmd` file (the underlying R Markdown file).
-* ...a `header.tex` file (a tex file for document structure).
 * ...a `references.bib` file (the bibliography).
@@
 
-```{r tab3, echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE, results="asis"}
+```{r tab3, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, results="asis"}
 library(knitr)
@@
     + What is still not possible in this document is to automatically have separate reference sections for paper and appendix.
+* Journals may require you to use their tex style: Sometimes you can simply use their template in your rmarkdown file.
+See [here](https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/LDUMNY) for a PLOS one example.
 

### 2020-07-08 paper.tex
Deleted header.tex because of errors.

@@
 \setcounter{secnumdepth}{5}
-\usepackage[english]{babel}
-\usepackage[T1]{fontenc}
-\usepackage{float}
-\usepackage{lmodern}
-\usepackage{graphicx}
-\usepackage{url}
-\usepackage{array}
-\usepackage{setspace}
-\usepackage{graphics}
-%\usepackage{amssymb}
-\usepackage{amsmath}
-\usepackage{longtable}
-\usepackage{natbib}
-\usepackage{pdflscape}
-\usepackage{caption}
-\usepackage{subcaption}
-\usepackage{fullpage}
-\usepackage{multicol}
-\usepackage{dcolumn}
-\usepackage{lscape}
-\usepackage{array}
-\usepackage{color}
-\usepackage{setspace}
-
-\usepackage{cleveref}[2012/02/15]
-\usepackage{fullpage}
-\usepackage[charter]{mathdesign}
-\usepackage{bm}
-\usepackage{tabu}
-\usepackage{wrapfig}
-
-\crefformat{footnote}{#2\footnotemark[#1]#3}
-\usepackage{color}
-\usepackage{hyperref}
-
-\newenvironment{tightcenter}{%
-  \setlength\topsep{0pt}
-  \setlength\parskip{0pt}
-  \begin{center}
-}{%
-  \end{center}
-}
-
-%\setstretch{1.1}
-% Dutch style of paragraph formatting
-\parskip 5pt
-\makeatletter
-% Separation between lines
-\doublerulesep 1pt
-
-\definecolor{lightred}{rgb}{0.7,0,0}
-\definecolor{darkgreen}{rgb}{0,0.8,0}
-\definecolor{lightblue}{rgb}{0,0,0.7}
-
-\hypersetup{colorlinks,
-  linkcolor = lightred,
-  filecolor = lightred,
-  urlcolor = lightblue,
-  citecolor = lightred}
-
-% Spaces in bibliography
-\let\oldthebibliography=\thebibliography
-\let\endoldthebibliography=\endthebibliography
-\renewenvironment{thebibliography}[1]{%
-  \begin{oldthebibliography}{#1}%
-    \setlength{\parskip}{0ex}%
-    \setlength{\itemsep}{0.1ex}%
-  }%
-  {%
-  \end{oldthebibliography}%
-}
-
-\usepackage{array}
-\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
-\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
-\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
-
-\setlength{\parindent}{0pt} % no indentation
 \usepackage{booktabs}
@@
 Mannheim Centre for European Social Research}
-\date{5 April, 2020\\
+\date{First version: December 14, 2018\\
+This version: July 08, 2020\\
 ~\\
@@
 \item
-  \ldots download the 5 input files I created --- \texttt{paper.rmd}, \texttt{header.tex}, \texttt{references.bib}, \texttt{data.csv} and \texttt{american-sociological-association.csl} --- from \href{https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing}{this folder}.
+  \ldots download the 5 input files I created --- \texttt{paper.rmd}, \texttt{references.bib}, \texttt{data.csv} and \texttt{american-sociological-association.csl} --- from \href{https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing}{this folder}.
 Ignore the other files.
@@
   \ldots a \texttt{paper.rmd} file (the underlying R Markdown file).
-\item
-  \ldots a \texttt{header.tex} file (a tex file for document structure).
 \item
@@
 See \href{https://haozhu233.github.io/kableExtra/awesome_table_in_pdf.pdf}{this overview} of all the kable stylings that are possible provided by the package author himself.
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\KeywordTok{library}\NormalTok{(knitr)}
-\KeywordTok{library}\NormalTok{(kableExtra)}
-\KeywordTok{kable}\NormalTok{(cars[}\DecValTok{1}\OperatorTok{:}\DecValTok{10}\NormalTok{,], }\DataTypeTok{row.names =} \OtherTok{TRUE}\NormalTok{, }
-      \DataTypeTok{caption =} \StringTok{'Table with kable() and kablestyling()'}\NormalTok{, }
-      \DataTypeTok{format =} \StringTok{"latex"}\NormalTok{, }\DataTypeTok{booktabs =}\NormalTok{ T) }\OperatorTok{%>%}
-\StringTok{        }\KeywordTok{kable_styling}\NormalTok{(}\DataTypeTok{full_width =}\NormalTok{ T, }
-                      \DataTypeTok{latex_options =} \KeywordTok{c}\NormalTok{(}\StringTok{"striped"}\NormalTok{, }
-                                        \StringTok{"scale_down"}\NormalTok{,}
-                                        \StringTok{"HOLD_position"}\NormalTok{),}
-                      \DataTypeTok{font_size =} \DecValTok{10}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
 
@@
 \begin{verbatim}
-## R version 3.6.2 (2019-12-12)
+## R version 4.0.0 (2020-04-24)
 ## Platform: x86_64-w64-mingw32/x64 (64-bit)
@@
 ## other attached packages:
-## [1] ggplot2_3.2.1    kableExtra_1.1.0 knitr_1.26       stargazer_5.2.2 
+## [1] ggplot2_3.3.0    kableExtra_1.1.0 knitr_1.29       stargazer_5.2.2 
 ## 
 ## loaded via a namespace (and not attached):
-##  [1] Rcpp_1.0.3        pillar_1.4.3      compiler_3.6.2    tools_3.6.2      
-##  [5] digest_0.6.23     evaluate_0.14     tibble_2.1.3      lifecycle_0.2.0  
-##  [9] gtable_0.3.0      viridisLite_0.3.0 pkgconfig_2.0.3   rlang_0.4.5      
-## [13] rstudioapi_0.10   yaml_2.2.0        xfun_0.11         withr_2.1.2      
-## [17] dplyr_0.8.3       httr_1.4.1        stringr_1.4.0     xml2_1.2.2       
-## [21] vctrs_0.2.4       hms_0.5.2         tidyselect_0.2.5  webshot_0.5.2    
-## [25] grid_3.6.2        glue_1.3.2        R6_2.4.1          rmarkdown_2.0    
-## [29] bookdown_0.16     farver_2.0.1      purrr_0.3.3       readr_1.3.1      
-## [33] magrittr_1.5      scales_1.1.0      htmltools_0.4.0   assertthat_0.2.1 
-## [37] rvest_0.3.5       colorspace_1.4-1  labeling_0.3      stringi_1.4.3    
-## [41] lazyeval_0.2.2    munsell_0.5.0     crayon_1.3.4
+##  [1] Rcpp_1.0.4.6      pillar_1.4.4      compiler_4.0.0    tools_4.0.0      
+##  [5] digest_0.6.25     evaluate_0.14     lifecycle_0.2.0   tibble_3.0.1     
+##  [9] gtable_0.3.0      viridisLite_0.3.0 pkgconfig_2.0.3   rlang_0.4.6      
+## [13] rstudioapi_0.11   yaml_2.2.1        xfun_0.15         withr_2.2.0      
+## [17] stringr_1.4.0     httr_1.4.1        dplyr_1.0.0       xml2_1.3.2       
+## [21] generics_0.0.2    vctrs_0.3.1       hms_0.5.3         tidyselect_1.1.0 
+## [25] webshot_0.5.2     grid_4.0.0        glue_1.4.1        R6_2.4.1         
+## [29] rmarkdown_2.3     bookdown_0.19     farver_2.0.3      purrr_0.3.4      
+## [33] readr_1.3.1       magrittr_1.5      scales_1.1.1      ellipsis_0.3.1   
+## [37] htmltools_0.5.0   rvest_0.3.5       colorspace_1.4-1  labeling_0.3     
+## [41] stringi_1.4.6     munsell_0.5.0     crayon_1.3.4
 \end{verbatim}

### 2020-07-08 paper.Rmd
Small edits.
Added github link.

@@
   |
-  | Feedback? 
+  | Feedback? Errors?
   | mail@paulcbauer.eu
-  |
+  | [Github repository](https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown/)
 linestretch: 1.2

### 2020-07-08 paper.tex
Small edits.
Added github link.

@@
 ~\\
-Feedback?\\
-\href{mailto:mail@paulcbauer.eu}{\nolinkurl{mail@paulcbauer.eu}}\\}
+Feedback? Errors?\\
+\href{mailto:mail@paulcbauer.eu}{\nolinkurl{mail@paulcbauer.eu}}\\
+\href{https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown/}{Github repository}}
 

### 2021-06-23 paper.Rmd
Title page update.

--- 2020-07-08 paper.Rmd
@@
   |
-  | Feedback? 
+  | Feedback? Errors?
   | mail@paulcbauer.eu
+  | [Github repository](https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown/)
   |
+  |
+  | Tired of Latex?
+  | Try [Pagedown](https://github.com/rstudio/pagedown) with our [new template](https://osf.io/k8jhx/)! :-)
 linestretch: 1.2
@@
     + "`recoding-...`" for chunks in which data is recoded
+* Ideally give chunks the labels of the figures/tables in the final publication, e.g., "`fig-1`" is the name of the chunk that produces Figure 1 in the final paper.
 * Use "really" informative variable names:

### 2021-06-23 paper.tex
Title page update.

@@
 \date{First version: December 14, 2018\\
-This version: July 08, 2020\\
+This version: June 23, 2021\\
 ~\\
@@
 \href{mailto:mail@paulcbauer.eu}{\nolinkurl{mail@paulcbauer.eu}}\\
-\href{https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown/}{Github repository}}
+\href{https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown/}{Github repository}\\
+~\\
+~\\
+Tired of Latex?\\
+Try \href{https://github.com/rstudio/pagedown}{Pagedown} with our \href{https://osf.io/k8jhx/}{new template}! :-)}
 
@@
 \midrule
-\rowcolor{gray!6}  1 & 4 & 2\\
+\cellcolor{gray!6}{1} & \cellcolor{gray!6}{4} & \cellcolor{gray!6}{2}\\
 2 & 4 & 10\\
-\rowcolor{gray!6}  3 & 7 & 4\\
+\cellcolor{gray!6}{3} & \cellcolor{gray!6}{7} & \cellcolor{gray!6}{4}\\
 4 & 7 & 22\\
-\rowcolor{gray!6}  5 & 8 & 16\\
+\cellcolor{gray!6}{5} & \cellcolor{gray!6}{8} & \cellcolor{gray!6}{16}\\
 \addlinespace
 6 & 9 & 10\\
-\rowcolor{gray!6}  7 & 10 & 18\\
+\cellcolor{gray!6}{7} & \cellcolor{gray!6}{10} & \cellcolor{gray!6}{18}\\
 8 & 10 & 26\\
-\rowcolor{gray!6}  9 & 10 & 34\\
+\cellcolor{gray!6}{9} & \cellcolor{gray!6}{10} & \cellcolor{gray!6}{34}\\
 10 & 11 & 17\\
@@
   \end{itemize}
+\item
+  Ideally give chunks the labels of the figures/tables in the final publication, e.g., ``\texttt{fig-1}'' is the name of the chunk that produces Figure 1 in the final paper.
 \item
@@
 \begin{verbatim}
-## R version 4.0.0 (2020-04-24)
+## R version 4.1.0 (2021-05-18)
 ## Platform: x86_64-w64-mingw32/x64 (64-bit)
@@
 ## other attached packages:
-## [1] ggplot2_3.3.0    kableExtra_1.1.0 knitr_1.29       stargazer_5.2.2 
+## [1] ggplot2_3.3.4    kableExtra_1.3.4 knitr_1.33       stargazer_5.2.2 
 ## 
 ## loaded via a namespace (and not attached):
-##  [1] Rcpp_1.0.4.6      pillar_1.4.4      compiler_4.0.0    tools_4.0.0      
-##  [5] digest_0.6.25     evaluate_0.14     lifecycle_0.2.0   tibble_3.0.1     
-##  [9] gtable_0.3.0      viridisLite_0.3.0 pkgconfig_2.0.3   rlang_0.4.6      
-## [13] rstudioapi_0.11   yaml_2.2.1        xfun_0.15         withr_2.2.0      
-## [17] stringr_1.4.0     httr_1.4.1        dplyr_1.0.0       xml2_1.3.2       
-## [21] generics_0.0.2    vctrs_0.3.1       hms_0.5.3         tidyselect_1.1.0 
-## [25] webshot_0.5.2     grid_4.0.0        glue_1.4.1        R6_2.4.1         
-## [29] rmarkdown_2.3     bookdown_0.19     farver_2.0.3      purrr_0.3.4      
-## [33] readr_1.3.1       magrittr_1.5      scales_1.1.1      ellipsis_0.3.1   
-## [37] htmltools_0.5.0   rvest_0.3.5       colorspace_1.4-1  labeling_0.3     
-## [41] stringi_1.4.6     munsell_0.5.0     crayon_1.3.4
+##  [1] compiler_4.1.0    pillar_1.6.1      tools_4.1.0       digest_0.6.27    
+##  [5] evaluate_0.14     lifecycle_1.0.0   tibble_3.1.2      gtable_0.3.0     
+##  [9] viridisLite_0.4.0 pkgconfig_2.0.3   rlang_0.4.11      DBI_1.1.1        
+## [13] rstudioapi_0.13   yaml_2.2.1        xfun_0.24         withr_2.4.2      
+## [17] dplyr_1.0.6       httr_1.4.2        stringr_1.4.0     xml2_1.3.2       
+## [21] generics_0.1.0    vctrs_0.3.8       systemfonts_1.0.2 tidyselect_1.1.1 
+## [25] webshot_0.5.2     grid_4.1.0        svglite_2.0.0     glue_1.4.2       
+## [29] R6_2.5.0          fansi_0.5.0       rmarkdown_2.9     bookdown_0.22    
+## [33] farver_2.1.0      purrr_0.3.4       magrittr_2.0.1    scales_1.1.1     
+## [37] htmltools_0.5.1.1 ellipsis_0.3.2    assertthat_0.2.1  rvest_1.0.0      
+## [41] colorspace_2.0-1  labeling_0.4.2    utf8_1.2.1        stringi_1.6.1    
+## [45] munsell_0.5.0     crayon_1.4.1
 \end{verbatim}

### 2021-06-23 paper.tex
Updated title footnote.

@@
 \title{\vspace{1cm}Writing a reproducible paper\\
-in R Markdown*\footnote{*Corresponding address: \href{mailto:mail@paulcbauer.eu}{\nolinkurl{mail@paulcbauer.eu}}.
+in R Markdown\footnote{Corresponding address: \href{mailto:mail@paulcbauer.eu}{\nolinkurl{mail@paulcbauer.eu}}.
 Acknowledgments: I am grateful to all those generous people that invest their time into open-source software.}\vspace{0.5cm}\\}

### 2021-06-23 paper.Rmd
Updated title footnote.
Added download link.

@@
   | \vspace{1cm}Writing a reproducible paper
-  | in R Markdown*^[*Corresponding address: mail@paulcbauer.eu. Acknowledgments: I am grateful to all those generous people that invest their time into open-source software.]\vspace{0.5cm}
+  | in R Markdown^[Corresponding address: mail@paulcbauer.eu. Acknowledgments: I am grateful to all those generous people that invest their time into open-source software.]\vspace{0.5cm}
   |
@@
   | This version: `r gsub("^0", "", format(Sys.time(), "%B %d, %Y"))`
+  | Download: https://osf.io/q395s
   |
-  | Feedback? Errors?
-  | mail@paulcbauer.eu
+  | Feedback? Errors? mail@paulcbauer.eu
   | [Github repository](https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown/)
-  |
   |

### 2021-06-23 paper.tex
Added download link.

@@
 This version: June 23, 2021\\
+Download: \url{https://osf.io/q395s}\\
 ~\\
-Feedback? Errors?\\
-\href{mailto:mail@paulcbauer.eu}{\nolinkurl{mail@paulcbauer.eu}}\\
+Feedback? Errors? \href{mailto:mail@paulcbauer.eu}{\nolinkurl{mail@paulcbauer.eu}}\\
 \href{https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown/}{Github repository}\\
-~\\
 ~\\

### 2023-03-08 paper.tex
edit author list and minor edits.

--- 2021-06-23 paper.tex
@@
 \PassOptionsToPackage{hyphens}{url}
-\PassOptionsToPackage{dvipsnames,svgnames*,x11names*}{xcolor}
+\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
 %
@@
 ]{article}
+\usepackage{amsmath,amssymb}
 \usepackage{lmodern}
 \usepackage{setspace}
-\usepackage{amssymb,amsmath}
-\usepackage{ifxetex,ifluatex}
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+\usepackage{iftex}
+\ifPDFTeX
   \usepackage[T1]{fontenc}
@@
 \usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\hypersetup{
-  colorlinks=true,
-  linkcolor=Maroon,
-  filecolor=Maroon,
-  citecolor=Blue,
-  urlcolor=Blue,
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
 \usepackage[margin=1in]{geometry}
@@
 \newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\usepackage{longtable,booktabs}
+\usepackage{longtable,booktabs,array}
+\usepackage{calc} % for calculating minipage widths
 % Correct order of tables after \paragraph or \subparagraph
@@
 \makesavenoteenv{longtable}
-\usepackage{graphicx,grffile}
+\usepackage{graphicx}
 \makeatletter
@@
 \setcounter{secnumdepth}{5}
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newlength{\cslentryspacingunit} % times entry-spacing
+\setlength{\cslentryspacingunit}{\parskip}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1
+  \let\oldpar\par
+  \def\par{\hangindent=\cslhangindent\oldpar}
+  \fi
+  % set entry spacing
+  \setlength{\parskip}{#2\cslentryspacingunit}
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 \usepackage{booktabs}
@@
 \usepackage{xcolor}
+\ifLuaTeX
+  \usepackage{selnolig}  % disable illegal ligatures
+\fi
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same} % disable monospaced font for URLs
+\hypersetup{
+  pdfauthor={Paul Bauer, Mannheim Centre for European Social Research; Camille Landesvatter, Mannheim Centre for European Social Research},
+  colorlinks=true,
+  linkcolor={Maroon},
+  filecolor={Maroon},
+  citecolor={Blue},
+  urlcolor={Blue},
+  pdfcreator={LaTeX via pandoc}}
 
-\title{\vspace{1cm}Writing a reproducible paper\\
-in R Markdown\footnote{Corresponding address: \href{mailto:mail@paulcbauer.eu}{\nolinkurl{mail@paulcbauer.eu}}.
-Acknowledgments: I am grateful to all those generous people that invest their time into open-source software.}\vspace{0.5cm}\\}
-\author{Paul C. Bauer\\
-Mannheim Centre for European Social Research}
-\date{First version: December 14, 2018\\
-This version: June 23, 2021\\
-~\\
-Feedback? Errors?\\
-\href{mailto:mail@paulcbauer.eu}{\nolinkurl{mail@paulcbauer.eu}}\\
+\title{\hfill\break
+\hfill\break
+\vspace{1cm}Writing a reproducible paper\\
+in R Markdown\footnote{Corresponding address: \href{mailto:mail@paulcbauer.de}{\nolinkurl{mail@paulcbauer.de}}.
+Acknowledgments: We are grateful to all those generous people that invest their time into open-source software.}\vspace{0.5cm}\\}
+\author{Paul Bauer, Mannheim Centre for European Social Research \and Camille Landesvatter, Mannheim Centre for European Social Research}
+\date{\hfill\break
+First version: December 14, 2018\\
+This version: March 08, 2023\\
+Download: \url{https://osf.io/q395s}\\
+\strut \\
+Feedback? Errors? \href{mailto:mail@paulcbauer.eu}{\nolinkurl{mail@paulcbauer.eu}}\\
 \href{https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown/}{Github repository}\\
-~\\
-~\\
+\strut \\
 Tired of Latex?\\
@@
 \noindent\setstretch{1}The present paper provides a template for a reproducible scientific paper written in R Markdown.
-Below I outline some of the ``tricks''/code (e.g., referencing tables, sections etc.) I had to figure out to produce this document.
+Below we outline some of the ``tricks''/code (e.g., referencing tables, sections etc.) we had to figure out to produce this document.
 The underlying files which produce this document can be downloaded \href{https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing}{here}.
-I think I got pretty far but there is always room for improvement and more automatization, in parallel to the incredible developments in R and Rstudio (bookdown etc.).
-I intend to update this file when I discover more convenient code (you can follow any updates through the corresponding \href{https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown/}{github repo}).\vspace{.8cm}
+We think we got pretty far but there is always room for improvement and more automatization, in parallel to the incredible developments in R and Rstudio (bookdown etc.).
+We intend to update this file when we discover more convenient code (you can follow any updates through the corresponding \href{https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown/}{github repo}).\vspace{.8cm}
 \end{abstract}
@@
 Hence, it should be freely accessible to everyone without any barriers, e.g., without requiring commercial software.
-Importantly, researchers from developing countries are even more dependent on free access to knowledge (Kirsop and Chan \protect\hyperlink{ref-Kirsop2005-ro}{2005}).
+Importantly, researchers from developing countries are even more dependent on free access to knowledge (\protect\hyperlink{ref-Kirsop2005-ro}{Kirsop and Chan 2005}).
 \item
@@
 
-I assume that you are using R on a day-to-day basis.
+We assume that you are using R on a day-to-day basis.
 You may have even started to work a little in R Markdown but you don't write your complete paper in R Markdown.
@@
 \item
-  \ldots install \href{https://www.r-project.org/}{R} and \href{https://www.rstudio.com/}{Rstudio} (most recent versions) (R Core Team \protect\hyperlink{ref-R2017}{2017}; RStudio Team \protect\hyperlink{ref-Rstudio2015}{2015}).
+  \ldots install \href{https://www.r-project.org/}{R} and \href{https://www.rstudio.com/}{Rstudio} (most recent versions) (\protect\hyperlink{ref-R2017}{R Core Team 2017}; \protect\hyperlink{ref-Rstudio2015}{RStudio Team 2015}).
 \item
-  \ldots install \href{https://yihui.name/tinytex/}{tinytex}, a lightweight version of Tex Live (Allaire et al.
-\protect\hyperlink{ref-markdown2017}{2017}; Xie \protect\hyperlink{ref-tinytex}{2018}\protect\hyperlink{ref-tinytex}{b}).
+  \ldots install \href{https://yihui.name/tinytex/}{tinytex}, a lightweight version of Tex Live (\protect\hyperlink{ref-markdown2017}{Allaire et al. 2017}; \protect\hyperlink{ref-tinytex}{Xie 2018b}).
 \end{itemize}
@@
 \begin{Highlighting}[]
-\KeywordTok{install.packages}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{'tinytex'}\NormalTok{, }\StringTok{'rmarkdown'}\NormalTok{))}
-\NormalTok{tinytex}\OperatorTok{::}\KeywordTok{install_tinytex}\NormalTok{()}
+\FunctionTok{install.packages}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\StringTok{\textquotesingle{}tinytex\textquotesingle{}}\NormalTok{, }\StringTok{\textquotesingle{}rmarkdown\textquotesingle{}}\NormalTok{))}
+\NormalTok{tinytex}\SpecialCharTok{::}\FunctionTok{install\_tinytex}\NormalTok{()}
 \end{Highlighting}
@@
 \item
-  \ldots install the packages below using the code below (Sievert et al.
-\protect\hyperlink{ref-plotly}{2017}; Xie \protect\hyperlink{ref-knitr3}{2014}, \protect\hyperlink{ref-knitr2}{2015}, \protect\hyperlink{ref-bookdown2}{2016}, \protect\hyperlink{ref-bookdown1}{2017}, \protect\hyperlink{ref-knitr1}{2018}\protect\hyperlink{ref-knitr1}{a}; Zhu \protect\hyperlink{ref-kableextra}{2017}).
+  \ldots install the packages below using the code below (\protect\hyperlink{ref-plotly}{Sievert et al.
+2017}; \protect\hyperlink{ref-knitr3}{Xie 2014}, \protect\hyperlink{ref-knitr2}{2015}, \protect\hyperlink{ref-bookdown2}{2016}, \protect\hyperlink{ref-bookdown1}{2017}, \protect\hyperlink{ref-knitr1}{2018a}; \protect\hyperlink{ref-kableextra}{Zhu 2017}).
 \end{itemize}
@@
 \begin{Highlighting}[]
-\KeywordTok{install.packages}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"rmarkdown"}\NormalTok{, }\StringTok{"knitr"}\NormalTok{, }\StringTok{"kableExtra"}\NormalTok{,}
+\FunctionTok{install.packages}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\StringTok{"rmarkdown"}\NormalTok{, }\StringTok{"knitr"}\NormalTok{, }\StringTok{"kableExtra"}\NormalTok{,}
                    \StringTok{"stargazer"}\NormalTok{, }\StringTok{"plotly"}\NormalTok{, }\StringTok{"knitr"}\NormalTok{,}
@@
 \item
-  \ldots download the 5 input files I created --- \texttt{paper.rmd}, \texttt{references.bib}, \texttt{data.csv} and \texttt{american-sociological-association.csl} --- from \href{https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing}{this folder}.
+  \ldots download the 5 input files we created --- \texttt{paper.rmd}, \texttt{references.bib}, \texttt{data.csv} and \texttt{american-sociological-association.csl} --- from \href{https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing}{this folder}.
 Ignore the other files.
@@
   \item
-    I use paperpile to manage my references and export the \texttt{.bib} file into the folder that contains my \texttt{.rmd} file.
+    We use paperpile to manage my references and export the \texttt{.bib} file into the folder that contains my \texttt{.rmd} file.
   \end{itemize}
@@
 For instance in Section \ref{sec:tables} you can find different ways of referencing tables.
-The code of the underlying \texttt{paper.rmd} will show you how I referenced Section \ref{sec:tables} right here namely with `\texttt{Section\ \textbackslash{}@ref(sec:tables)}'.
+The code of the underlying \texttt{paper.rmd} will show you how we referenced Section \ref{sec:tables} right here namely with `\texttt{Section\ \textbackslash{}@ref(sec:tables)}'.
 
@@
 
-I would recommend to use the command below and simply add it to the appendix as I did here in Appendix \ref{sec:rsessioninfo}.
+We would recommend to use the command below and simply add it to the appendix as we did here in Appendix \ref{sec:rsessioninfo}.
 This will make sure you always provide the package versions that you used in the last compilation of your paper.
@@
 \begin{Highlighting}[]
-\KeywordTok{cat}\NormalTok{(}\KeywordTok{paste}\NormalTok{(}\StringTok{"#"}\NormalTok{, }\KeywordTok{capture.output}\NormalTok{(}\KeywordTok{sessionInfo}\NormalTok{()), }\StringTok{"}\CharTok{\textbackslash{}n}\StringTok{"}\NormalTok{, }\DataTypeTok{collapse =}\StringTok{""}\NormalTok{)) }
-  \CommentTok{# or use message() instead of cat()}
+\FunctionTok{cat}\NormalTok{(}\FunctionTok{paste}\NormalTok{(}\StringTok{"\#"}\NormalTok{, }\FunctionTok{capture.output}\NormalTok{(}\FunctionTok{sessionInfo}\NormalTok{()), }\StringTok{"}\SpecialCharTok{\textbackslash{}n}\StringTok{"}\NormalTok{, }\AttributeTok{collapse =}\StringTok{""}\NormalTok{)) }
+  \CommentTok{\# or use message() instead of cat()}
 \end{Highlighting}
@@
 \begin{Highlighting}[]
-\NormalTok{data <-}\StringTok{ }\KeywordTok{read.csv}\NormalTok{(}\StringTok{"data.csv"}\NormalTok{)}
-\KeywordTok{head}\NormalTok{(data)}
+\NormalTok{data }\OtherTok{\textless{}{-}} \FunctionTok{read.csv}\NormalTok{(}\StringTok{"data.csv"}\NormalTok{)}
+\FunctionTok{head}\NormalTok{(data)}
 \end{Highlighting}
@@
 \begin{Highlighting}[]
-\KeywordTok{dput}\NormalTok{(data)}
+\FunctionTok{dput}\NormalTok{(data)}
 \end{Highlighting}
@@
 \begin{Highlighting}[]
-\NormalTok{data <-}\StringTok{ }\KeywordTok{structure}\NormalTok{(}\KeywordTok{list}\NormalTok{(}\DataTypeTok{X =} \DecValTok{1}\OperatorTok{:}\DecValTok{50}\NormalTok{, }\DataTypeTok{speed =} \KeywordTok{c}\NormalTok{(4L, 4L, 7L, 7L, 8L, 9L, 10L, }
+\NormalTok{data }\OtherTok{\textless{}{-}} \FunctionTok{structure}\NormalTok{(}\FunctionTok{list}\NormalTok{(}\AttributeTok{X =} \DecValTok{1}\SpecialCharTok{:}\DecValTok{50}\NormalTok{, }\AttributeTok{speed =} \FunctionTok{c}\NormalTok{(4L, 4L, 7L, 7L, 8L, 9L, 10L, }
 \NormalTok{10L, 10L, 11L, 11L, 12L, 12L, 12L, 12L, 13L, 13L, 13L, 13L, 14L, }
@@
 \NormalTok{18L, 18L, 19L, 19L, 19L, 20L, 20L, 20L, 20L, 20L, 22L, 23L, 24L, }
-\NormalTok{24L, 24L, 24L, 25L), }\DataTypeTok{dist =} \KeywordTok{c}\NormalTok{(2L, 10L, 4L, 22L, 16L, 10L, 18L, }
+\NormalTok{24L, 24L, 24L, 25L), }\AttributeTok{dist =} \FunctionTok{c}\NormalTok{(2L, 10L, 4L, 22L, 16L, 10L, 18L, }
 \NormalTok{26L, 34L, 17L, 28L, 14L, 20L, 24L, 28L, 26L, 34L, 34L, 46L, 26L, }
@@
 \NormalTok{92L, 93L, 120L, 85L)), }
-\DataTypeTok{class =} \StringTok{"data.frame"}\NormalTok{, }\DataTypeTok{row.names =} \KeywordTok{c}\NormalTok{(}\OtherTok{NA}\NormalTok{, }
-\OperatorTok{-}\NormalTok{50L))}
+\AttributeTok{class =} \StringTok{"data.frame"}\NormalTok{, }\AttributeTok{row.names =} \FunctionTok{c}\NormalTok{(}\ConstantTok{NA}\NormalTok{, }
+\SpecialCharTok{{-}}\NormalTok{50L))}
 \end{Highlighting}
@@
 
-Table \ref{tab1} shows summary stats of your data.\footnote{To reference the table where you set the identifier in the stargazer function you only need to use the actual label, i.e., ´tab1´.} I normally use \texttt{stargazer()} (Hlavac \protect\hyperlink{ref-hlavac2013stargazer}{2013}) which offers extreme flexibility regarding table output (see \texttt{?stargazer}).
+Table \ref{tab1} shows summary stats of your data.\footnote{To reference the table where you set the identifier in the stargazer function you only need to use the actual label, i.e., ´tab1´.} We normally use \texttt{stargazer()} (\protect\hyperlink{ref-hlavac2013stargazer}{Hlavac 2013}) which offers extreme flexibility regarding table output (see \texttt{?stargazer}).
 
@@
 \begin{Highlighting}[]
-\KeywordTok{library}\NormalTok{(stargazer)}
-\KeywordTok{stargazer}\NormalTok{(cars, }
-          \DataTypeTok{title =} \StringTok{"Summary table with stargazer"}\NormalTok{,}
-          \DataTypeTok{label=}\StringTok{"tab1"}\NormalTok{, }
-          \DataTypeTok{table.placement =} \StringTok{"H"}\NormalTok{, }
-          \DataTypeTok{header=}\OtherTok{FALSE}\NormalTok{)}
+\FunctionTok{library}\NormalTok{(stargazer)}
+\FunctionTok{stargazer}\NormalTok{(cars, }
+          \AttributeTok{title =} \StringTok{"Summary table with stargazer"}\NormalTok{,}
+          \AttributeTok{label=}\StringTok{"tab1"}\NormalTok{, }
+          \AttributeTok{table.placement =} \StringTok{"H"}\NormalTok{, }
+          \AttributeTok{header=}\ConstantTok{FALSE}\NormalTok{)}
 \end{Highlighting}
@@
   \label{tab1} 
-\begin{tabular}{@{\extracolsep{5pt}}lccccccc} 
+\begin{tabular}{@{\extracolsep{5pt}}lccccc} 
 \\[-1.8ex]\hline 
 \hline \\[-1.8ex] 
-Statistic & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{St.
-Dev.} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Pctl(25)} & \multicolumn{1}{c}{Pctl(75)} & \multicolumn{1}{c}{Max} \\
+Statistic & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{St. Dev.} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} \\ 
 \hline \\[-1.8ex] 
-speed & 50 & 15.400 & 5.288 & 4 & 12 & 19 & 25 \\ 
-dist & 50 & 42.980 & 25.769 & 2 & 26 & 56 & 120 \\ 
+speed & 50 & 15.400 & 5.288 & 4 & 25 \\ 
+dist & 50 & 42.980 & 25.769 & 2 & 120 \\ 
 \hline \\[-1.8ex] 
@@
 \begin{Highlighting}[]
-\KeywordTok{library}\NormalTok{(stargazer)}
-\NormalTok{model1 <-}\StringTok{ }\KeywordTok{lm}\NormalTok{(speed }\OperatorTok{~}\StringTok{ }\NormalTok{dist, }\DataTypeTok{data =}\NormalTok{ cars)}
-\NormalTok{model2 <-}\StringTok{ }\KeywordTok{lm}\NormalTok{(speed }\OperatorTok{~}\StringTok{ }\NormalTok{dist, }\DataTypeTok{data =}\NormalTok{ cars)}
-\NormalTok{model3 <-}\StringTok{ }\KeywordTok{lm}\NormalTok{(dist }\OperatorTok{~}\StringTok{ }\NormalTok{speed, }\DataTypeTok{data =}\NormalTok{ cars)}
-\KeywordTok{stargazer}\NormalTok{(model1, model2, model3,}
-          \DataTypeTok{title =} \StringTok{"Regression table with stargazer"}\NormalTok{,}
-          \DataTypeTok{label=}\StringTok{"tab2"}\NormalTok{, }
-          \DataTypeTok{table.placement =} \StringTok{"H"}\NormalTok{, }
-          \DataTypeTok{column.labels =} \KeywordTok{c}\NormalTok{(}\StringTok{"M1"}\NormalTok{, }\StringTok{"M2"}\NormalTok{, }\StringTok{"M3"}\NormalTok{),}
-          \DataTypeTok{model.numbers =} \OtherTok{FALSE}\NormalTok{,}
-          \DataTypeTok{header=}\OtherTok{FALSE}\NormalTok{)}
+\FunctionTok{library}\NormalTok{(stargazer)}
+\NormalTok{model1 }\OtherTok{\textless{}{-}} \FunctionTok{lm}\NormalTok{(speed }\SpecialCharTok{\textasciitilde{}}\NormalTok{ dist, }\AttributeTok{data =}\NormalTok{ cars)}
+\NormalTok{model2 }\OtherTok{\textless{}{-}} \FunctionTok{lm}\NormalTok{(speed }\SpecialCharTok{\textasciitilde{}}\NormalTok{ dist, }\AttributeTok{data =}\NormalTok{ cars)}
+\NormalTok{model3 }\OtherTok{\textless{}{-}} \FunctionTok{lm}\NormalTok{(dist }\SpecialCharTok{\textasciitilde{}}\NormalTok{ speed, }\AttributeTok{data =}\NormalTok{ cars)}
+\FunctionTok{stargazer}\NormalTok{(model1, model2, model3,}
+          \AttributeTok{title =} \StringTok{"Regression table with stargazer"}\NormalTok{,}
+          \AttributeTok{label=}\StringTok{"tab2"}\NormalTok{, }
+          \AttributeTok{table.placement =} \StringTok{"H"}\NormalTok{, }
+          \AttributeTok{column.labels =} \FunctionTok{c}\NormalTok{(}\StringTok{"M1"}\NormalTok{, }\StringTok{"M2"}\NormalTok{, }\StringTok{"M3"}\NormalTok{),}
+          \AttributeTok{model.numbers =} \ConstantTok{FALSE}\NormalTok{,}
+          \AttributeTok{header=}\ConstantTok{FALSE}\NormalTok{)}
 \end{Highlighting}
@@
 \begin{Highlighting}[]
-\KeywordTok{plot}\NormalTok{(cars}\OperatorTok{$}\NormalTok{speed, cars}\OperatorTok{$}\NormalTok{dist)}
+\FunctionTok{plot}\NormalTok{(cars}\SpecialCharTok{$}\NormalTok{speed, cars}\SpecialCharTok{$}\NormalTok{dist)}
 \end{Highlighting}
@@
 \begin{Highlighting}[]
-\NormalTok{mtcars}\OperatorTok{$}\NormalTok{cyl <-}\StringTok{ }\KeywordTok{as.factor}\NormalTok{(mtcars}\OperatorTok{$}\NormalTok{cyl) }\CommentTok{# Convert cyl to factor}
-\KeywordTok{library}\NormalTok{(ggplot2)}
-\KeywordTok{ggplot}\NormalTok{(mtcars, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x=}\NormalTok{wt, }\DataTypeTok{y=}\NormalTok{mpg, }\DataTypeTok{shape=}\NormalTok{cyl)) }\OperatorTok{+}\StringTok{ }\KeywordTok{geom_point}\NormalTok{() }\OperatorTok{+}
-\StringTok{  }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{x=}\StringTok{"Weight (lb/1000)"}\NormalTok{, }\DataTypeTok{y =} \StringTok{"Miles/(US) gallon"}\NormalTok{, }
-       \DataTypeTok{shape=}\StringTok{"Number of }\CharTok{\textbackslash{}n}\StringTok{ Cylinders"}\NormalTok{) }\OperatorTok{+}\StringTok{ }\KeywordTok{theme_classic}\NormalTok{()}
+\NormalTok{mtcars}\SpecialCharTok{$}\NormalTok{cyl }\OtherTok{\textless{}{-}} \FunctionTok{as.factor}\NormalTok{(mtcars}\SpecialCharTok{$}\NormalTok{cyl) }\CommentTok{\# Convert cyl to factor}
+\FunctionTok{library}\NormalTok{(ggplot2)}
+\FunctionTok{ggplot}\NormalTok{(mtcars, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x=}\NormalTok{wt, }\AttributeTok{y=}\NormalTok{mpg, }\AttributeTok{shape=}\NormalTok{cyl)) }\SpecialCharTok{+} \FunctionTok{geom\_point}\NormalTok{() }\SpecialCharTok{+}
+  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x=}\StringTok{"Weight (lb/1000)"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Miles/(US) gallon"}\NormalTok{, }
+       \AttributeTok{shape=}\StringTok{"Number of }\SpecialCharTok{\textbackslash{}n}\StringTok{ Cylinders"}\NormalTok{) }\SpecialCharTok{+} \FunctionTok{theme\_classic}\NormalTok{()}
 \end{Highlighting}
@@
 
-Every researcher has his own optimized setup. Currently I would recommend the following:
+Every researcher has his own optimized setup. Currently we would recommend the following:
 
@@
   \item
-    Data files: "data\_xxxxxx.*"
+    Data files: ``data\_xxxxxx.*''
   \item
-    Image files: "fig\_xxxxxx.*"
+    Image files: ``fig\_xxxxxx.*''
   \item
-    Tables files: "table\_xxxx.*"
+    Tables files: ``table\_xxxx.*''
   \item
@@
 \hypertarget{refs}{}
-\leavevmode\hypertarget{ref-markdown2017}{}%
-Allaire, JJ, Jeffrey Horner, Vicent Marti, and Natacha Porte. 2017. \emph{Markdown: 'Markdown' Rendering for R}.
+\begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-markdown2017}{}}%
+Allaire, JJ, Jeffrey Horner, Vicent Marti, and Natacha Porte. 2017. \emph{\href{https://CRAN.R-project.org/package=markdown}{Markdown: 'Markdown' Rendering for r}}.
 
-\leavevmode\hypertarget{ref-hlavac2013stargazer}{}%
-Hlavac, Marek. 2013. ``Stargazer: LaTeX Code and Ascii Text for Well-Formatted Regression and Summary Statistics Tables.'' \emph{URL: Http://CRAN. R-Project. Org/Package= Stargazer}.
+\leavevmode\vadjust pre{\hypertarget{ref-hlavac2013stargazer}{}}%
+Hlavac, Marek. 2013. {``Stargazer: LaTeX Code and ASCII Text for Well-Formatted Regression and Summary Statistics Tables.''} \emph{URL: Http://CRAN. R-Project. Org/Package= Stargazer}.
 
-\leavevmode\hypertarget{ref-Kirsop2005-ro}{}%
-Kirsop, Barbara and Leslie Chan. 2005. ``Transforming Access to Research Literature for Developing Countries.'' \emph{Serials Review} 31(4):246--55.
+\leavevmode\vadjust pre{\hypertarget{ref-Kirsop2005-ro}{}}%
+Kirsop, Barbara and Leslie Chan. 2005. {``Transforming Access to Research Literature for Developing Countries.''} \emph{Serials Review} 31(4):246--55.
 
-\leavevmode\hypertarget{ref-R2017}{}%
-R Core Team. 2017. \emph{R: A Language and Environment for Statistical Computing}. Vienna, Austria: R Foundation for Statistical Computing.
+\leavevmode\vadjust pre{\hypertarget{ref-R2017}{}}%
+R Core Team. 2017. \emph{\href{https://www.R-project.org/}{R: A Language and Environment for Statistical Computing}}. Vienna, Austria: R Foundation for Statistical Computing.
 
-\leavevmode\hypertarget{ref-Rstudio2015}{}%
-RStudio Team. 2015. \emph{RStudio: Integrated Development Environment for R}. Boston, MA: RStudio, Inc.
+\leavevmode\vadjust pre{\hypertarget{ref-Rstudio2015}{}}%
+RStudio Team. 2015. \emph{\href{http://www.rstudio.com/}{RStudio: Integrated Development Environment for r}}. Boston, MA: RStudio, Inc.
 
-\leavevmode\hypertarget{ref-plotly}{}%
-Sievert, Carson, Chris Parmer, Toby Hocking, Scott Chamberlain, Karthik Ram, Marianne Corvellec, and Pedro Despouy. 2017. \emph{Plotly: Create Interactive Web Graphics via 'Plotly.js'}.
+\leavevmode\vadjust pre{\hypertarget{ref-plotly}{}}%
+Sievert, Carson, Chris Parmer, Toby Hocking, Scott Chamberlain, Karthik Ram, Marianne Corvellec, and Pedro Despouy.
+2017.
+\emph{\href{https://CRAN.R-project.org/package=plotly}{Plotly: Create Interactive Web Graphics via 'Plotly.js'}}.
 
-\leavevmode\hypertarget{ref-knitr3}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-knitr3}{}}%
 Xie, Yihui.
 2014.
-``Knitr: A Comprehensive Tool for Reproducible Research in R.'' in \emph{Implementing reproducible computational research}, edited by V.
+{``\href{http://www.crcpress.com/product/isbn/9781466561595}{Knitr: A Comprehensive Tool for Reproducible Research in {R}}.''} in \emph{Implementing reproducible computational research}, edited by V.
 Stodden, F.
@@
 
-\leavevmode\hypertarget{ref-knitr2}{}%
-Xie, Yihui. 2015. \emph{Dynamic Documents with R and Knitr}. 2nd ed. Boca Raton, Florida: Chapman; Hall/CRC.
+\leavevmode\vadjust pre{\hypertarget{ref-knitr2}{}}%
+Xie, Yihui. 2015. \emph{\href{https://yihui.name/knitr/}{Dynamic Documents with {R} and Knitr}}. 2nd ed. Boca Raton, Florida: Chapman; Hall/CRC.
 
-\leavevmode\hypertarget{ref-bookdown2}{}%
-Xie, Yihui. 2016. \emph{Bookdown: Authoring Books and Technical Documents with R Markdown}. Boca Raton, Florida: Chapman; Hall/CRC.
+\leavevmode\vadjust pre{\hypertarget{ref-bookdown2}{}}%
+Xie, Yihui. 2016. \emph{\href{https://github.com/rstudio/bookdown}{Bookdown: Authoring Books and Technical Documents with {R} Markdown}}. Boca Raton, Florida: Chapman; Hall/CRC.
 
-\leavevmode\hypertarget{ref-bookdown1}{}%
-Xie, Yihui. 2017. \emph{Bookdown: Authoring Books and Technical Documents with R Markdown}.
+\leavevmode\vadjust pre{\hypertarget{ref-bookdown1}{}}%
+Xie, Yihui. 2017. \emph{\href{https://github.com/rstudio/bookdown}{Bookdown: Authoring Books and Technical Documents with r Markdown}}.
 
-\leavevmode\hypertarget{ref-knitr1}{}%
-Xie, Yihui. 2018a. \emph{Knitr: A General-Purpose Package for Dynamic Report Generation in R}.
+\leavevmode\vadjust pre{\hypertarget{ref-knitr1}{}}%
+Xie, Yihui. 2018a. \emph{\href{https://yihui.name/knitr/}{Knitr: A General-Purpose Package for Dynamic Report Generation in r}}.
 
-\leavevmode\hypertarget{ref-tinytex}{}%
-Xie, Yihui. 2018b. \emph{Tinytex: Helper Functions to Install and Maintain 'Tex Live', and Compile 'Latex' Documents}.
+\leavevmode\vadjust pre{\hypertarget{ref-tinytex}{}}%
+Xie, Yihui. 2018b. \emph{\href{https://CRAN.R-project.org/package=tinytex}{Tinytex: Helper Functions to Install and Maintain 'TeX Live', and Compile 'LaTeX' Documents}}.
 
-\leavevmode\hypertarget{ref-kableextra}{}%
-Zhu, Hao. 2017. \emph{KableExtra: Construct Complex Table with 'Kable' and Pipe Syntax}.
+\leavevmode\vadjust pre{\hypertarget{ref-kableextra}{}}%
+Zhu, Hao. 2017. \emph{\href{https://CRAN.R-project.org/package=kableExtra}{kableExtra: Construct Complex Table with 'Kable' and Pipe Syntax}}.
+
+\end{CSLReferences}
 
@@
 \begin{verbatim}
-## R version 4.1.0 (2021-05-18)
-## Platform: x86_64-w64-mingw32/x64 (64-bit)
-## Running under: Windows 10 x64 (build 17763)
+## R version 4.2.2 (2022-10-31)
+## Platform: aarch64-apple-darwin20 (64-bit)
+## Running under: macOS Ventura 13.0.1
 ## 
 ## Matrix products: default
+## BLAS:   /Library/Frameworks/R.framework/Versions/4.2-arm64/Resources/lib/libRblas.0.dylib
+## LAPACK: /Library/Frameworks/R.framework/Versions/4.2-arm64/Resources/lib/libRlapack.dylib
 ## 
@@
 ## other attached packages:
-## [1] ggplot2_3.3.4    kableExtra_1.3.4 knitr_1.33       stargazer_5.2.2 
+## [1] ggplot2_3.3.6    kableExtra_1.3.4 knitr_1.39       stargazer_5.2.3 
 ## 
 ## loaded via a namespace (and not attached):
-##  [1] compiler_4.1.0    pillar_1.6.1      tools_4.1.0       digest_0.6.27    
-##  [5] evaluate_0.14     lifecycle_1.0.0   tibble_3.1.2      gtable_0.3.0     
-##  [9] viridisLite_0.4.0 pkgconfig_2.0.3   rlang_0.4.11      DBI_1.1.1        
-## [13] rstudioapi_0.13   yaml_2.2.1        xfun_0.24         withr_2.4.2      
-## [17] dplyr_1.0.6       httr_1.4.2        stringr_1.4.0     xml2_1.3.2       
-## [21] generics_0.1.0    vctrs_0.3.8       systemfonts_1.0.2 tidyselect_1.1.1 
-## [25] webshot_0.5.2     grid_4.1.0        svglite_2.0.0     glue_1.4.2       
-## [29] R6_2.5.0          fansi_0.5.0       rmarkdown_2.9     bookdown_0.22    
-## [33] farver_2.1.0      purrr_0.3.4       magrittr_2.0.1    scales_1.1.1     
-## [37] htmltools_0.5.1.1 ellipsis_0.3.2    assertthat_0.2.1  rvest_1.0.0      
-## [41] colorspace_2.0-1  labeling_0.4.2    utf8_1.2.1        stringi_1.6.1    
-## [45] munsell_0.5.0     crayon_1.4.1
+##  [1] compiler_4.2.2    pillar_1.7.0      tools_4.2.2       digest_0.6.29    
+##  [5] evaluate_0.15     lifecycle_1.0.1   tibble_3.1.7      gtable_0.3.0     
+##  [9] viridisLite_0.4.0 pkgconfig_2.0.3   rlang_1.0.6       DBI_1.1.2        
+## [13] cli_3.3.0         rstudioapi_0.13   yaml_2.3.5        xfun_0.37        
+## [17] fastmap_1.1.0     withr_2.5.0       dplyr_1.0.9       httr_1.4.3       
+## [21] stringr_1.4.0     xml2_1.3.3        generics_0.1.2    vctrs_0.4.1      
+## [25] systemfonts_1.0.4 tidyselect_1.1.2  webshot_0.5.3     grid_4.2.2       
+## [29] svglite_2.1.0     glue_1.6.2        R6_2.5.1          fansi_1.0.3      
+## [33] rmarkdown_2.20    bookdown_0.27     farver_2.1.0      purrr_0.3.4      
+## [37] magrittr_2.0.3    scales_1.2.0      htmltools_0.5.2   ellipsis_0.3.2   
+## [41] assertthat_0.2.1  rvest_1.0.2       colorspace_2.0-3  labeling_0.4.2   
+## [45] utf8_1.2.2        stringi_1.7.6     munsell_0.5.0     crayon_1.5.1
 \end{verbatim}
@@
 \begin{Highlighting}[]
-\NormalTok{knitr}\OperatorTok{::}\NormalTok{opts_chunk}\OperatorTok{$}\KeywordTok{set}\NormalTok{(}\DataTypeTok{cache =} \OtherTok{FALSE}\NormalTok{)}
-\CommentTok{# Use chache = TRUE if you want to speed up compilation}
+\NormalTok{knitr}\SpecialCharTok{::}\NormalTok{opts\_chunk}\SpecialCharTok{$}\FunctionTok{set}\NormalTok{(}\AttributeTok{cache =} \ConstantTok{FALSE}\NormalTok{)}
+\CommentTok{\# Use chache = TRUE if you want to speed up compilation}
 
-\CommentTok{# A function to allow for showing some of the inline code}
-\NormalTok{rinline <-}\StringTok{ }\ControlFlowTok{function}\NormalTok{(code)\{}
-\NormalTok{  html <-}\StringTok{ '<code  class="r">``` `r CODE` ```</code>'}
-  \KeywordTok{sub}\NormalTok{(}\StringTok{"CODE"}\NormalTok{, code, html)}
+\CommentTok{\# A function to allow for showing some of the inline code}
+\NormalTok{rinline }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(code)\{}
+\NormalTok{  html }\OtherTok{\textless{}{-}} \StringTok{\textquotesingle{}\textless{}code  class="r"\textgreater{}\textasciigrave{}\textasciigrave{}\textasciigrave{} \textasciigrave{}r CODE\textasciigrave{} \textasciigrave{}\textasciigrave{}\textasciigrave{}\textless{}/code\textgreater{}\textquotesingle{}}
+  \FunctionTok{sub}\NormalTok{(}\StringTok{"CODE"}\NormalTok{, code, html)}
 \NormalTok{\}}
-\KeywordTok{install.packages}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{'tinytex'}\NormalTok{, }\StringTok{'rmarkdown'}\NormalTok{))}
-\NormalTok{tinytex}\OperatorTok{::}\KeywordTok{install_tinytex}\NormalTok{()}
-\KeywordTok{install.packages}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"rmarkdown"}\NormalTok{, }\StringTok{"knitr"}\NormalTok{, }\StringTok{"kableExtra"}\NormalTok{,}
+\FunctionTok{install.packages}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\StringTok{\textquotesingle{}tinytex\textquotesingle{}}\NormalTok{, }\StringTok{\textquotesingle{}rmarkdown\textquotesingle{}}\NormalTok{))}
+\NormalTok{tinytex}\SpecialCharTok{::}\FunctionTok{install\_tinytex}\NormalTok{()}
+\FunctionTok{install.packages}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\StringTok{"rmarkdown"}\NormalTok{, }\StringTok{"knitr"}\NormalTok{, }\StringTok{"kableExtra"}\NormalTok{,}
                    \StringTok{"stargazer"}\NormalTok{, }\StringTok{"plotly"}\NormalTok{, }\StringTok{"knitr"}\NormalTok{,}
                    \StringTok{"bookdown"}\NormalTok{))}
-\KeywordTok{cat}\NormalTok{(}\KeywordTok{paste}\NormalTok{(}\StringTok{"#"}\NormalTok{, }\KeywordTok{capture.output}\NormalTok{(}\KeywordTok{sessionInfo}\NormalTok{()), }\StringTok{"}\CharTok{\textbackslash{}n}\StringTok{"}\NormalTok{, }\DataTypeTok{collapse =}\StringTok{""}\NormalTok{)) }
-  \CommentTok{# or use message() instead of cat()}
-\NormalTok{data <-}\StringTok{ }\KeywordTok{read.csv}\NormalTok{(}\StringTok{"data.csv"}\NormalTok{)}
-\KeywordTok{head}\NormalTok{(data)}
-\KeywordTok{dput}\NormalTok{(data)}
-\NormalTok{data <-}\StringTok{ }\KeywordTok{structure}\NormalTok{(}\KeywordTok{list}\NormalTok{(}\DataTypeTok{X =} \DecValTok{1}\OperatorTok{:}\DecValTok{50}\NormalTok{, }\DataTypeTok{speed =} \KeywordTok{c}\NormalTok{(4L, 4L, 7L, 7L, 8L, 9L, 10L, }
+\FunctionTok{cat}\NormalTok{(}\FunctionTok{paste}\NormalTok{(}\StringTok{"\#"}\NormalTok{, }\FunctionTok{capture.output}\NormalTok{(}\FunctionTok{sessionInfo}\NormalTok{()), }\StringTok{"}\SpecialCharTok{\textbackslash{}n}\StringTok{"}\NormalTok{, }\AttributeTok{collapse =}\StringTok{""}\NormalTok{)) }
+  \CommentTok{\# or use message() instead of cat()}
+\NormalTok{data }\OtherTok{\textless{}{-}} \FunctionTok{read.csv}\NormalTok{(}\StringTok{"data.csv"}\NormalTok{)}
+\FunctionTok{head}\NormalTok{(data)}
+\FunctionTok{dput}\NormalTok{(data)}
+\NormalTok{data }\OtherTok{\textless{}{-}} \FunctionTok{structure}\NormalTok{(}\FunctionTok{list}\NormalTok{(}\AttributeTok{X =} \DecValTok{1}\SpecialCharTok{:}\DecValTok{50}\NormalTok{, }\AttributeTok{speed =} \FunctionTok{c}\NormalTok{(4L, 4L, 7L, 7L, 8L, 9L, 10L, }
 \NormalTok{10L, 10L, 11L, 11L, 12L, 12L, 12L, 12L, 13L, 13L, 13L, 13L, 14L, }
@@
 \NormalTok{92L, 93L, 120L, 85L)), }
-\DataTypeTok{class =} \StringTok{"data.frame"}\NormalTok{, }\DataTypeTok{row.names =} \KeywordTok{c}\NormalTok{(}\OtherTok{NA}\NormalTok{, }
-\OperatorTok{-}\NormalTok{50L))}
-\KeywordTok{library}\NormalTok{(stargazer)}
-\KeywordTok{stargazer}\NormalTok{(cars, }
-          \DataTypeTok{title =} \StringTok{"Summary table with stargazer"}\NormalTok{,}
-          \DataTypeTok{label=}\StringTok{"tab1"}\NormalTok{, }
-          \DataTypeTok{table.placement =} \StringTok{"H"}\NormalTok{, }
-          \DataTypeTok{header=}\OtherTok{FALSE}\NormalTok{)}
-\KeywordTok{library}\NormalTok{(stargazer)}
-\NormalTok{model1 <-}\StringTok{ }\KeywordTok{lm}\NormalTok{(speed }\OperatorTok{~}\StringTok{ }\NormalTok{dist, }\DataTypeTok{data =}\NormalTok{ cars)}
-\NormalTok{model2 <-}\StringTok{ }\KeywordTok{lm}\NormalTok{(speed }\OperatorTok{~}\StringTok{ }\NormalTok{dist, }\DataTypeTok{data =}\NormalTok{ cars)}
-\NormalTok{model3 <-}\StringTok{ }\KeywordTok{lm}\NormalTok{(dist }\OperatorTok{~}\StringTok{ }\NormalTok{speed, }\DataTypeTok{data =}\NormalTok{ cars)}
-\KeywordTok{stargazer}\NormalTok{(model1, model2, model3,}
-          \DataTypeTok{title =} \StringTok{"Regression table with stargazer"}\NormalTok{,}
-          \DataTypeTok{label=}\StringTok{"tab2"}\NormalTok{, }
-          \DataTypeTok{table.placement =} \StringTok{"H"}\NormalTok{, }
-          \DataTypeTok{column.labels =} \KeywordTok{c}\NormalTok{(}\StringTok{"M1"}\NormalTok{, }\StringTok{"M2"}\NormalTok{, }\StringTok{"M3"}\NormalTok{),}
-          \DataTypeTok{model.numbers =} \OtherTok{FALSE}\NormalTok{,}
-          \DataTypeTok{header=}\OtherTok{FALSE}\NormalTok{)}
-\KeywordTok{library}\NormalTok{(knitr)}
-\KeywordTok{library}\NormalTok{(kableExtra)}
-\KeywordTok{kable}\NormalTok{(cars[}\DecValTok{1}\OperatorTok{:}\DecValTok{10}\NormalTok{,], }\DataTypeTok{row.names =} \OtherTok{TRUE}\NormalTok{, }
-      \DataTypeTok{caption =} \StringTok{'Table with kable() and kablestyling()'}\NormalTok{, }
-      \DataTypeTok{format =} \StringTok{"latex"}\NormalTok{, }\DataTypeTok{booktabs =}\NormalTok{ T) }\OperatorTok{%>%}
-\StringTok{        }\KeywordTok{kable_styling}\NormalTok{(}\DataTypeTok{full_width =}\NormalTok{ T, }
-                      \DataTypeTok{latex_options =} \KeywordTok{c}\NormalTok{(}\StringTok{"striped"}\NormalTok{, }
-                                        \StringTok{"scale_down"}\NormalTok{,}
-                                        \StringTok{"HOLD_position"}\NormalTok{),}
-                      \DataTypeTok{font_size =} \DecValTok{10}\NormalTok{)}
-\KeywordTok{plot}\NormalTok{(cars}\OperatorTok{$}\NormalTok{speed, cars}\OperatorTok{$}\NormalTok{dist)}
-\NormalTok{mtcars}\OperatorTok{$}\NormalTok{cyl <-}\StringTok{ }\KeywordTok{as.factor}\NormalTok{(mtcars}\OperatorTok{$}\NormalTok{cyl) }\CommentTok{# Convert cyl to factor}
-\KeywordTok{library}\NormalTok{(ggplot2)}
-\KeywordTok{ggplot}\NormalTok{(mtcars, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x=}\NormalTok{wt, }\DataTypeTok{y=}\NormalTok{mpg, }\DataTypeTok{shape=}\NormalTok{cyl)) }\OperatorTok{+}\StringTok{ }\KeywordTok{geom_point}\NormalTok{() }\OperatorTok{+}
-\StringTok{  }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{x=}\StringTok{"Weight (lb/1000)"}\NormalTok{, }\DataTypeTok{y =} \StringTok{"Miles/(US) gallon"}\NormalTok{, }
-       \DataTypeTok{shape=}\StringTok{"Number of }\CharTok{\textbackslash{}n}\StringTok{ Cylinders"}\NormalTok{) }\OperatorTok{+}\StringTok{ }\KeywordTok{theme_classic}\NormalTok{()}
-\KeywordTok{print}\NormalTok{(}\KeywordTok{sessionInfo}\NormalTok{(), }\DataTypeTok{local =} \OtherTok{FALSE}\NormalTok{)}
+\AttributeTok{class =} \StringTok{"data.frame"}\NormalTok{, }\AttributeTok{row.names =} \FunctionTok{c}\NormalTok{(}\ConstantTok{NA}\NormalTok{, }
+\SpecialCharTok{{-}}\NormalTok{50L))}
+\FunctionTok{library}\NormalTok{(stargazer)}
+\FunctionTok{stargazer}\NormalTok{(cars, }
+          \AttributeTok{title =} \StringTok{"Summary table with stargazer"}\NormalTok{,}
+          \AttributeTok{label=}\StringTok{"tab1"}\NormalTok{, }
+          \AttributeTok{table.placement =} \StringTok{"H"}\NormalTok{, }
+          \AttributeTok{header=}\ConstantTok{FALSE}\NormalTok{)}
+\FunctionTok{library}\NormalTok{(stargazer)}
+\NormalTok{model1 }\OtherTok{\textless{}{-}} \FunctionTok{lm}\NormalTok{(speed }\SpecialCharTok{\textasciitilde{}}\NormalTok{ dist, }\AttributeTok{data =}\NormalTok{ cars)}
+\NormalTok{model2 }\OtherTok{\textless{}{-}} \FunctionTok{lm}\NormalTok{(speed }\SpecialCharTok{\textasciitilde{}}\NormalTok{ dist, }\AttributeTok{data =}\NormalTok{ cars)}
+\NormalTok{model3 }\OtherTok{\textless{}{-}} \FunctionTok{lm}\NormalTok{(dist }\SpecialCharTok{\textasciitilde{}}\NormalTok{ speed, }\AttributeTok{data =}\NormalTok{ cars)}
+\FunctionTok{stargazer}\NormalTok{(model1, model2, model3,}
+          \AttributeTok{title =} \StringTok{"Regression table with stargazer"}\NormalTok{,}
+          \AttributeTok{label=}\StringTok{"tab2"}\NormalTok{, }
+          \AttributeTok{table.placement =} \StringTok{"H"}\NormalTok{, }
+          \AttributeTok{column.labels =} \FunctionTok{c}\NormalTok{(}\StringTok{"M1"}\NormalTok{, }\StringTok{"M2"}\NormalTok{, }\StringTok{"M3"}\NormalTok{),}
+          \AttributeTok{model.numbers =} \ConstantTok{FALSE}\NormalTok{,}
+          \AttributeTok{header=}\ConstantTok{FALSE}\NormalTok{)}
+\FunctionTok{library}\NormalTok{(knitr)}
+\FunctionTok{library}\NormalTok{(kableExtra)}
+\FunctionTok{kable}\NormalTok{(cars[}\DecValTok{1}\SpecialCharTok{:}\DecValTok{10}\NormalTok{,], }\AttributeTok{row.names =} \ConstantTok{TRUE}\NormalTok{, }
+      \AttributeTok{caption =} \StringTok{\textquotesingle{}Table with kable() and kablestyling()\textquotesingle{}}\NormalTok{, }
+      \AttributeTok{format =} \StringTok{"latex"}\NormalTok{, }\AttributeTok{booktabs =}\NormalTok{ T) }\SpecialCharTok{\%\textgreater{}\%}
+        \FunctionTok{kable\_styling}\NormalTok{(}\AttributeTok{full\_width =}\NormalTok{ T, }
+                      \AttributeTok{latex\_options =} \FunctionTok{c}\NormalTok{(}\StringTok{"striped"}\NormalTok{, }
+                                        \StringTok{"scale\_down"}\NormalTok{,}
+                                        \StringTok{"HOLD\_position"}\NormalTok{),}
+                      \AttributeTok{font\_size =} \DecValTok{10}\NormalTok{)}
+\FunctionTok{plot}\NormalTok{(cars}\SpecialCharTok{$}\NormalTok{speed, cars}\SpecialCharTok{$}\NormalTok{dist)}
+\NormalTok{mtcars}\SpecialCharTok{$}\NormalTok{cyl }\OtherTok{\textless{}{-}} \FunctionTok{as.factor}\NormalTok{(mtcars}\SpecialCharTok{$}\NormalTok{cyl) }\CommentTok{\# Convert cyl to factor}
+\FunctionTok{library}\NormalTok{(ggplot2)}
+\FunctionTok{ggplot}\NormalTok{(mtcars, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x=}\NormalTok{wt, }\AttributeTok{y=}\NormalTok{mpg, }\AttributeTok{shape=}\NormalTok{cyl)) }\SpecialCharTok{+} \FunctionTok{geom\_point}\NormalTok{() }\SpecialCharTok{+}
+  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x=}\StringTok{"Weight (lb/1000)"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Miles/(US) gallon"}\NormalTok{, }
+       \AttributeTok{shape=}\StringTok{"Number of }\SpecialCharTok{\textbackslash{}n}\StringTok{ Cylinders"}\NormalTok{) }\SpecialCharTok{+} \FunctionTok{theme\_classic}\NormalTok{()}
+\FunctionTok{print}\NormalTok{(}\FunctionTok{sessionInfo}\NormalTok{(), }\AttributeTok{local =} \ConstantTok{FALSE}\NormalTok{)}
 \end{Highlighting}

### 2023-03-10 paper.Rmd

@@
   | \vspace{1cm}Writing a reproducible paper
-  | in R Markdown^[Corresponding address: mail@paulcbauer.eu. Acknowledgments: I am grateful to all those generous people that invest their time into open-source software.]\vspace{0.5cm}
+  | in R Markdown^[Corresponding address: mail@paulcbauer.de. Acknowledgments: We are grateful to all those generous people that invest their time into open-source software.]\vspace{0.5cm}
   |
-author: |
-  | Paul C. Bauer
-  | Mannheim Centre for European Social Research
+author:
+  - Paul Bauer, Mannheim Centre for European Social Research
+  - Camille Landesvatter, Mannheim Centre for European Social Research
 date: |
@@
 abstract: \noindent\setstretch{1}The present paper provides a template for a reproducible scientific paper written in R Markdown.
-Below I outline some of the "tricks"/code (e.g., referencing tables, sections etc.) I had to figure out to produce this document.
+Below we outline some of the "tricks"/code (e.g., referencing tables, sections etc.) we had to figure out to produce this document.
 The underlying files which produce this document can be downloaded [here](https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing).
-I think I got pretty far but there is always room for improvement and more automatization, in parallel to the incredible developments in R and Rstudio (bookdown etc.).
-I intend to update this file when I discover more convenient code (you can follow any updates through the corresponding [github repo](https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown/)).\vspace{.8cm}
+We think we got pretty far but there is always room for improvement and more automatization, in parallel to the incredible developments in R and Rstudio (bookdown etc.).
+We intend to update this file when we discover more convenient code (you can follow any updates through the corresponding [github repo](https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown/)).\vspace{.8cm}
 bibliography: references.bib
@@
 # Prerequesites
-I assume that you are using R on a day-to-day basis.
+We assume that you are using R on a day-to-day basis.
 You may have even started to work a little in R Markdown but you don't write your complete paper in R Markdown.
@@
 ```
-* ...download the 5 input files I created --- `paper.rmd`, `references.bib`, `data.csv` and `american-sociological-association.csl` --- from [this folder](https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing).
+* ...download the 5 input files we created --- `paper.rmd`, `references.bib`, `data.csv` and `american-sociological-association.csl` --- from [this folder](https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing).
 Ignore the other files.
@@
 * ...a `references.bib` file (the bibliography).
-    + I use paperpile to manage my references and export the `.bib` file into the folder that contains my `.rmd` file.
+    + We use paperpile to manage my references and export the `.bib` file into the folder that contains my `.rmd` file.
 * ...a `data.csv` file (some raw data).
@@
 For instance in Section \@ref(sec:tables) you can find different ways of referencing tables.
-The code of the underlying `paper.rmd` will show you how I referenced Section \@ref(sec:tables) right here namely with '`Section \@ref(sec:tables)`'.
+The code of the underlying `paper.rmd` will show you how we referenced Section \@ref(sec:tables) right here namely with '`Section \@ref(sec:tables)`'.
 
@@
 
-I would recommend to use the command below and simply add it to the appendix as I did here in Appendix \@ref(sec:rsessioninfo).
+We would recommend to use the command below and simply add it to the appendix as we did here in Appendix \@ref(sec:rsessioninfo).
 This will make sure you always provide the package versions that you used in the last compilation of your paper.
@@
 
-Table \@ref(tab1) shows summary stats of your data.^[To reference the table where you set the identifier in the stargazer function you only need to use the actual label, i.e., ´tab1´.] I normally use `stargazer()` [@hlavac2013stargazer] which offers extreme flexibility regarding table output (see `?stargazer`).
+Table \@ref(tab1) shows summary stats of your data.^[To reference the table where you set the identifier in the stargazer function you only need to use the actual label, i.e., ´tab1´.] We normally use `stargazer()` [@hlavac2013stargazer] which offers extreme flexibility regarding table output (see `?stargazer`).
 
@@
 # Good practices
-Every researcher has his own optimized setup. Currently I would recommend the following:
+Every researcher has his own optimized setup. Currently we would recommend the following:
 

### 2023-04-05 paper.Rmd
Update Links/URLs.

@@
   |
-  | Feedback? Errors? mail@paulcbauer.eu
+  | Feedback? Errors? mail@paulcbauer.de
   | [Github repository](https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown/)
@@
 Below we outline some of the "tricks"/code (e.g., referencing tables, sections etc.) we had to figure out to produce this document.
-The underlying files which produce this document can be downloaded [here](https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing).
+The underlying files which produce this document can be downloaded [here](https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown) (click on Code -> Download ZIP).
 We think we got pretty far but there is always room for improvement and more automatization, in parallel to the incredible developments in R and Rstudio (bookdown etc.).
-We intend to update this file when we discover more convenient code (you can follow any updates through the corresponding [github repo](https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown/)).\vspace{.8cm}
+We intend to update this file when we discover more convenient code (you can follow any updates through the corresponding [Github repo](https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown/)).\vspace{.8cm}
 bibliography: references.bib
@@
 ```
-* ...download the 5 input files we created --- `paper.rmd`, `references.bib`, `data.csv` and `american-sociological-association.csl` --- from [this folder](https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing).
+* ...download the 5 input files we created --- `paper.rmd`, `references.bib`, `data.csv` and `american-sociological-association.csl` --- from [Github](https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown) (click on Code -> Download ZIP).
 Ignore the other files.
@@
 
-[Download these files](https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing) and save them into a folder.
+[Download these files from Github](https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown) (click on Code -> Download ZIP) and save them into a folder.
 Close R/Rstudio and directly open `paper.rmd` with RStudio.
@@
 In the present document we use the style of the American Sociological Association and set it in the preamble with `csl: american-sociological-association.csl`.
-However, you also need to download the respective `.csl` file from the following github page: https://github.com/citation-style-language/styles and copy it into your working directory for it to work.
+However, you also need to download the respective `.csl` file from the following Github page: https://github.com/citation-style-language/styles and copy it into your working directory for it to work.
 
-The github directory contains a wide variety of citation style files depending on what discipline you work in.
+The Github directory contains a wide variety of citation style files depending on what discipline you work in.
 

### 2023-04-05 paper.tex
Update Links/URLs.

@@
 First version: December 14, 2018\\
-This version: March 08, 2023\\
+This version: April 05, 2023\\
 Download: \url{https://osf.io/q395s}\\
 \strut \\
-Feedback? Errors? \href{mailto:mail@paulcbauer.eu}{\nolinkurl{mail@paulcbauer.eu}}\\
+Feedback? Errors? \href{mailto:mail@paulcbauer.de}{\nolinkurl{mail@paulcbauer.de}}\\
 \href{https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown/}{Github repository}\\
@@
 Below we outline some of the ``tricks''/code (e.g., referencing tables, sections etc.) we had to figure out to produce this document.
-The underlying files which produce this document can be downloaded \href{https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing}{here}.
+The underlying files which produce this document can be downloaded \href{https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown}{here} (click on Code -\textgreater{} Download ZIP).
 We think we got pretty far but there is always room for improvement and more automatization, in parallel to the incredible developments in R and Rstudio (bookdown etc.).
-We intend to update this file when we discover more convenient code (you can follow any updates through the corresponding \href{https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown/}{github repo}).\vspace{.8cm}
+We intend to update this file when we discover more convenient code (you can follow any updates through the corresponding \href{https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown/}{Github repo}).\vspace{.8cm}
 \end{abstract}
@@
 \item
-  \ldots download the 5 input files we created --- \texttt{paper.rmd}, \texttt{references.bib}, \texttt{data.csv} and \texttt{american-sociological-association.csl} --- from \href{https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing}{this folder}.
+  \ldots download the 5 input files we created --- \texttt{paper.rmd}, \texttt{references.bib}, \texttt{data.csv} and \texttt{american-sociological-association.csl} --- from \href{https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown}{Github} (click on Code -\textgreater{} Download ZIP).
 Ignore the other files.
@@
 
-\href{https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing}{Download these files} and save them into a folder.
+\href{https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown}{Download these files from Github} (click on Code -\textgreater{} Download ZIP) and save them into a folder.
 Close R/Rstudio and directly open \texttt{paper.rmd} with RStudio.
@@
 In the present document we use the style of the American Sociological Association and set it in the preamble with \texttt{csl:\ american-sociological-association.csl}.
-However, you also need to download the respective \texttt{.csl} file from the following github page: \url{https://github.com/citation-style-language/styles} and copy it into your working directory for it to work.
+However, you also need to download the respective \texttt{.csl} file from the following Github page: \url{https://github.com/citation-style-language/styles} and copy it into your working directory for it to work.
 
-The github directory contains a wide variety of citation style files depending on what discipline you work in.
+The Github directory contains a wide variety of citation style files depending on what discipline you work in.
 
@@
 ## other attached packages:
-## [1] ggplot2_3.3.6    kableExtra_1.3.4 knitr_1.39       stargazer_5.2.3 
+## [1] ggplot2_3.4.2    kableExtra_1.3.4 knitr_1.42       stargazer_5.2.3 
 ## 
 ## loaded via a namespace (and not attached):
-##  [1] compiler_4.2.2    pillar_1.7.0      tools_4.2.2       digest_0.6.29    
-##  [5] evaluate_0.15     lifecycle_1.0.1   tibble_3.1.7      gtable_0.3.0     
-##  [9] viridisLite_0.4.0 pkgconfig_2.0.3   rlang_1.0.6       DBI_1.1.2        
-## [13] cli_3.3.0         rstudioapi_0.13   yaml_2.3.5        xfun_0.37        
-## [17] fastmap_1.1.0     withr_2.5.0       dplyr_1.0.9       httr_1.4.3       
-## [21] stringr_1.4.0     xml2_1.3.3        generics_0.1.2    vctrs_0.4.1      
-## [25] systemfonts_1.0.4 tidyselect_1.1.2  webshot_0.5.3     grid_4.2.2       
-## [29] svglite_2.1.0     glue_1.6.2        R6_2.5.1          fansi_1.0.3      
-## [33] rmarkdown_2.20    bookdown_0.27     farver_2.1.0      purrr_0.3.4      
-## [37] magrittr_2.0.3    scales_1.2.0      htmltools_0.5.2   ellipsis_0.3.2   
-## [41] assertthat_0.2.1  rvest_1.0.2       colorspace_2.0-3  labeling_0.4.2   
-## [45] utf8_1.2.2        stringi_1.7.6     munsell_0.5.0     crayon_1.5.1
+##  [1] compiler_4.2.2    pillar_1.9.0      tools_4.2.2       digest_0.6.31    
+##  [5] evaluate_0.20     lifecycle_1.0.3   tibble_3.2.1      gtable_0.3.3     
+##  [9] viridisLite_0.4.1 pkgconfig_2.0.3   rlang_1.1.0       cli_3.6.1        
+## [13] rstudioapi_0.14   yaml_2.3.7        xfun_0.38         fastmap_1.1.1    
+## [17] withr_2.5.0       dplyr_1.1.1       httr_1.4.5        stringr_1.5.0    
+## [21] xml2_1.3.3        generics_0.1.3    vctrs_0.6.1       systemfonts_1.0.4
+## [25] tidyselect_1.2.0  webshot_0.5.4     grid_4.2.2        svglite_2.1.1    
+## [29] glue_1.6.2        R6_2.5.1          fansi_1.0.4       rmarkdown_2.21   
+## [33] bookdown_0.33     farver_2.1.1      magrittr_2.0.3    scales_1.2.1     
+## [37] htmltools_0.5.5   rvest_1.0.3       colorspace_2.1-0  labeling_0.4.2   
+## [41] utf8_1.2.3        stringi_1.7.12    munsell_0.5.0
 \end{verbatim}

### 2023-06-19 paper.Rmd
YAML: change from output: bookdown::pdf_document2 to pdf_document
It is more straightforward and offers the same features (creates a toc, keep_tex, etc).

@@
 output:
-  bookdown::pdf_document2:
+  pdf_document:
     toc: no

### 2023-06-19 paper.tex
YAML: change from output: bookdown::pdf_document2 to pdf_document
It is more straightforward and offers the same features (creates a toc, keep_tex, etc).

@@
 \usepackage{amsmath,amssymb}
-\usepackage{lmodern}
 \usepackage{setspace}
@@
 \else % if luatex or xetex
-  \usepackage{unicode-math}
+  \usepackage{unicode-math} % this also loads fontspec
   \defaultfontfeatures{Scale=MatchLowercase}
   \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+\usepackage{lmodern}
+\ifPDFTeX\else
+  % xetex/luatex font selection
   \setmainfont[]{Times New Roman}
@@
 \newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
+\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
 \newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
@@
 \newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
 \newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
@@
 \newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
 \newcommand{\ImportTok}[1]{#1}
@@
 \newcommand{\RegionMarkerTok}[1]{#1}
-\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
 \newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
@@
 \newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\usepackage{longtable,booktabs,array}
-\usepackage{calc} % for calculating minipage widths
-% Correct order of tables after \paragraph or \subparagraph
-\usepackage{etoolbox}
-\makeatletter
-\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
-\makeatother
-% Allow footnotes in longtable head/foot
-\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
-\makesavenoteenv{longtable}
 \usepackage{graphicx}
@@
   \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{5}
+\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
 \newlength{\cslhangindent}
@@
 \IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
+\urlstyle{same}
 \hypersetup{
@@
 \vspace{1cm}Writing a reproducible paper\\
-in R Markdown\footnote{Corresponding address: \href{mailto:mail@paulcbauer.de}{\nolinkurl{mail@paulcbauer.de}}.
-Acknowledgments: We are grateful to all those generous people that invest their time into open-source software.}\vspace{0.5cm}\\}
-\author{Paul Bauer, Mannheim Centre for European Social Research \and Camille Landesvatter, Mannheim Centre for European Social Research}
+in R Markdown\footnote{Corresponding address:
+  \href{mailto:mail@paulcbauer.de}{\nolinkurl{mail@paulcbauer.de}}.
+  Acknowledgments: We are grateful to all those generous people that
+  invest their time into open-source software.}\vspace{0.5cm}\\}
+\author{Paul Bauer, Mannheim Centre for European Social
+Research \and Camille Landesvatter, Mannheim Centre for European Social
+Research}
 \date{\hfill\break
 First version: December 14, 2018\\
-This version: April 05, 2023\\
+This version: June 19, 2023\\
 Download: \url{https://osf.io/q395s}\\
 \strut \\
-Feedback? Errors? \href{mailto:mail@paulcbauer.de}{\nolinkurl{mail@paulcbauer.de}}\\
-\href{https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown/}{Github repository}\\
+Feedback? Errors?
+\href{mailto:mail@paulcbauer.de}{\nolinkurl{mail@paulcbauer.de}}\\
+\href{https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown/}{Github
+repository}\\
 \strut \\
 Tired of Latex?\\
-Try \href{https://github.com/rstudio/pagedown}{Pagedown} with our \href{https://osf.io/k8jhx/}{new template}! :-)}
+Try \href{https://github.com/rstudio/pagedown}{Pagedown} with our
+\href{https://osf.io/k8jhx/}{new template}! :-)}
 
@@
 \begin{abstract}
-\noindent\setstretch{1}The present paper provides a template for a reproducible scientific paper written in R Markdown.
-Below we outline some of the ``tricks''/code (e.g., referencing tables, sections etc.) we had to figure out to produce this document.
-The underlying files which produce this document can be downloaded \href{https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown}{here} (click on Code -\textgreater{} Download ZIP).
-We think we got pretty far but there is always room for improvement and more automatization, in parallel to the incredible developments in R and Rstudio (bookdown etc.).
-We intend to update this file when we discover more convenient code (you can follow any updates through the corresponding \href{https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown/}{Github repo}).\vspace{.8cm}
+\noindent\setstretch{1}The present paper provides a template for a
+reproducible scientific paper written in R Markdown. Below we outline
+some of the ``tricks''/code (e.g., referencing tables, sections etc.) we
+had to figure out to produce this document. The underlying files which
+produce this document can be downloaded
+\href{https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown}{here}
+(click on Code -\textgreater{} Download ZIP). We think we got pretty far
+but there is always room for improvement and more automatization, in
+parallel to the incredible developments in R and Rstudio (bookdown
+etc.). We intend to update this file when we discover more convenient
+code (you can follow any updates through the corresponding
+\href{https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown/}{Github
+repo}).\vspace{.8cm}
 \end{abstract}
@@
 \hypertarget{why-reproducible-research-in-r}{%
-\section{Why reproducible research (in R)?}\label{why-reproducible-research-in-r}}
+\section{Why reproducible research (in
+R)?}\label{why-reproducible-research-in-r}}
 
@@
 \item
-  \textbf{Access}: Research is normally funded by taxpayers (researchers are also taxpayers).
-Hence, it should be freely accessible to everyone without any barriers, e.g., without requiring commercial software.
-Importantly, researchers from developing countries are even more dependent on free access to knowledge (\protect\hyperlink{ref-Kirsop2005-ro}{Kirsop and Chan 2005}).
+  \textbf{Access}: Research is normally funded by taxpayers (researchers
+  are also taxpayers). Hence, it should be freely accessible to everyone
+  without any barriers, e.g., without requiring commercial software.
+  Importantly, researchers from developing countries are even more
+  dependent on free access to knowledge
+  (\protect\hyperlink{ref-Kirsop2005-ro}{Kirsop and Chan 2005}).
 \item
-  \textbf{Reproducability}: Even if you have written a study and analyzed the data yourself you will forget what you did after a few months.
-A fully reproducible setup will help you to trace back your own steps.
-Obviously, the same is true for other researchers who may want to understand your work and built on it.
-It may sound like a joke but why not aim for a document that can be used to reproduce your findings in 500 years.
+  \textbf{Reproducability}: Even if you have written a study and
+  analyzed the data yourself you will forget what you did after a few
+  months. A fully reproducible setup will help you to trace back your
+  own steps. Obviously, the same is true for other researchers who may
+  want to understand your work and built on it. It may sound like a joke
+  but why not aim for a document that can be used to reproduce your
+  findings in 500 years.
 \item
-  \textbf{Errors}: Manual steps in data analysis (e.g., manually copy/pasting values into a table etc.) may introduce errors. R Markdown allows you to \textbf{automatize} such steps and/or avoid them.
+  \textbf{Errors}: Manual steps in data analysis (e.g., manually
+  copy/pasting values into a table etc.) may introduce errors. R
+  Markdown allows you to \textbf{automatize} such steps and/or avoid
+  them.
 \item
-  \textbf{Revisions}: Revising a paper takes much less time if you have all the code you need in one place, i.e., one \texttt{.rmd} file.
-For instance, if you decide to exclude a subset of your data you simply need to insert one line of your code at the beginning and everything is rebuilt/re-estimated automatically.
+  \textbf{Revisions}: Revising a paper takes much less time if you have
+  all the code you need in one place, i.e., one \texttt{.rmd} file. For
+  instance, if you decide to exclude a subset of your data you simply
+  need to insert one line of your code at the beginning and everything
+  is rebuilt/re-estimated automatically.
 \end{itemize}
@@
 
-We assume that you are using R on a day-to-day basis.
-You may have even started to work a little in R Markdown but you don't write your complete paper in R Markdown.
-If you don't know what R Markdown is watch \href{https://vimeo.com/178485416}{this short video}.
-Then\ldots{}
+We assume that you are using R on a day-to-day basis. You may have even
+started to work a little in R Markdown but you don't write your complete
+paper in R Markdown. If you don't know what R Markdown is watch
+\href{https://vimeo.com/178485416}{this short video}. Then\ldots{}
 
@@
 \item
-  \ldots install \href{https://www.r-project.org/}{R} and \href{https://www.rstudio.com/}{Rstudio} (most recent versions) (\protect\hyperlink{ref-R2017}{R Core Team 2017}; \protect\hyperlink{ref-Rstudio2015}{RStudio Team 2015}).
+  \ldots install \href{https://www.r-project.org/}{R} and
+  \href{https://www.rstudio.com/}{Rstudio} (most recent versions)
+  (\protect\hyperlink{ref-R2017}{R Core Team 2017};
+  \protect\hyperlink{ref-Rstudio2015}{RStudio Team 2015}).
 \item
-  \ldots install \href{https://yihui.name/tinytex/}{tinytex}, a lightweight version of Tex Live (\protect\hyperlink{ref-markdown2017}{Allaire et al. 2017}; \protect\hyperlink{ref-tinytex}{Xie 2018b}).
+  \ldots install \href{https://yihui.name/tinytex/}{tinytex}, a
+  lightweight version of Tex Live
+  (\protect\hyperlink{ref-markdown2017}{Allaire et al. 2017};
+  \protect\hyperlink{ref-tinytex}{Xie 2018b}).
 \end{itemize}
@@
 \item
-  \ldots install the packages below using the code below (\protect\hyperlink{ref-plotly}{Sievert et al.
-2017}; \protect\hyperlink{ref-knitr3}{Xie 2014}, \protect\hyperlink{ref-knitr2}{2015}, \protect\hyperlink{ref-bookdown2}{2016}, \protect\hyperlink{ref-bookdown1}{2017}, \protect\hyperlink{ref-knitr1}{2018a}; \protect\hyperlink{ref-kableextra}{Zhu 2017}).
+  \ldots install the packages below using the code below
+  (\protect\hyperlink{ref-plotly}{Sievert et al. 2017};
+  \protect\hyperlink{ref-knitr3}{Xie 2014},
+  \protect\hyperlink{ref-knitr2}{2015},
+  \protect\hyperlink{ref-bookdown2}{2016},
+  \protect\hyperlink{ref-bookdown1}{2017},
+  \protect\hyperlink{ref-knitr1}{2018a};
+  \protect\hyperlink{ref-kableextra}{Zhu 2017}).
 \end{itemize}
@@
 \item
-  \ldots download the 5 input files we created --- \texttt{paper.rmd}, \texttt{references.bib}, \texttt{data.csv} and \texttt{american-sociological-association.csl} --- from \href{https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown}{Github} (click on Code -\textgreater{} Download ZIP).
-Ignore the other files.
+  \ldots download the 5 input files we created --- \texttt{paper.rmd},
+  \texttt{references.bib}, \texttt{data.csv} and
+  \texttt{american-sociological-association.csl} --- from
+  \href{https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown}{Github}
+  (click on Code -\textgreater{} Download ZIP). Ignore the other files.
 \item
-  \ldots learn R and read about the other underlying components namely \href{https://en.wikipedia.org/wiki/Markdown}{Markdown}, \href{https://rmarkdown.rstudio.com/lesson-1.html}{R Markdown} and \href{https://en.wikipedia.org/wiki/LaTeX}{Latex}.
+  \ldots learn R and read about the other underlying components namely
+  \href{https://en.wikipedia.org/wiki/Markdown}{Markdown},
+  \href{https://rmarkdown.rstudio.com/lesson-1.html}{R Markdown} and
+  \href{https://en.wikipedia.org/wiki/LaTeX}{Latex}.
 \end{itemize}
@@
 \hypertarget{basics-input-and-output-files}{%
-\section{Basics: Input and output files}\label{basics-input-and-output-files}}
+\section{Basics: Input and output
+files}\label{basics-input-and-output-files}}
 
-All the files you need to produce the present PDF file are the input files\ldots{}
+All the files you need to produce the present PDF file are the input
+files\ldots{}
 
@@
   \item
-    We use paperpile to manage my references and export the \texttt{.bib} file into the folder that contains my \texttt{.rmd} file.
+    We use paperpile to manage my references and export the
+    \texttt{.bib} file into the folder that contains my \texttt{.rmd}
+    file.
   \end{itemize}
@@
 \item
-  \ldots{} a \texttt{american-sociological-association.csl} file that defines the style of your bibliography.\footnote{You can download various citation style files from this webpage: \url{https://github.com/citation-style-language/styles}.}
+  \ldots{} a \texttt{american-sociological-association.csl} file that
+  defines the style of your bibliography.\footnote{You can download
+    various citation style files from this webpage:
+    \url{https://github.com/citation-style-language/styles}.}
 \end{itemize}
 
-\href{https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown}{Download these files from Github} (click on Code -\textgreater{} Download ZIP) and save them into a folder.
-Close R/Rstudio and directly open \texttt{paper.rmd} with RStudio.
-Doing so assures that the working directory is set to the folder that contains \texttt{paper.rmd} and the other files.\footnote{You can always check your working directory in R with \texttt{getwd()}.}
+\href{https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown}{Download
+these files from Github} (click on Code -\textgreater{} Download ZIP)
+and save them into a folder. Close R/Rstudio and directly open
+\texttt{paper.rmd} with RStudio. Doing so assures that the working
+directory is set to the folder that contains \texttt{paper.rmd} and the
+other files.\footnote{You can always check your working directory in R
+  with \texttt{getwd()}.}
 
-Once you run/compile the \texttt{paper.rmd} file in Rstudio it creates mainly two output files:
+Once you run/compile the \texttt{paper.rmd} file in Rstudio it creates
+mainly two output files:
 
@@
 
-In addition, there may be files that you generate and store locally in the folder during the compilation process. This is the case for some of the Plotly graphs below.
+In addition, there may be files that you generate and store locally in
+the folder during the compilation process. This is the case for some of
+the Plotly graphs below.
 
-Ideally, we can simply provide others with a \texttt{zip} folder that contains both our input files and our output files.
-Then it's possible to reproduce the process from managing/analyzing some raw data to producing the final scientific article.
+Ideally, we can simply provide others with a \texttt{zip} folder that
+contains both our input files and our output files. Then it's possible
+to reproduce the process from managing/analyzing some raw data to
+producing the final scientific article.
 
-Below we always display the R code in the chunks that produce the output.
-In your paper you will normally only present outputs (e.g., tables, figures etc.) by choosing the chunk option ``Show output only'' in R Studio.
-The chunk commands itself are not displayed but they do matter for referencing etc.
-So simply orient yourself at the underlying \texttt{paper.rmd} file.
+Below we always display the R code in the chunks that produce the
+output. In your paper you will normally only present outputs (e.g.,
+tables, figures etc.) by choosing the chunk option ``Show output only''
+in R Studio. The chunk commands itself are not displayed but they do
+matter for referencing etc. So simply orient yourself at the underlying
+\texttt{paper.rmd} file.
 
 \hypertarget{referencing-within-your-document}{%
-\section{Referencing within your document}\label{referencing-within-your-document}}
+\section{Referencing within your
+document}\label{referencing-within-your-document}}
 
-To see how referencing works simply see the different examples for figures, tables and sections below.
-For instance in Section \ref{sec:tables} you can find different ways of referencing tables.
-The code of the underlying \texttt{paper.rmd} will show you how we referenced Section \ref{sec:tables} right here namely with `\texttt{Section\ \textbackslash{}@ref(sec:tables)}'.
+To see how referencing works simply see the different examples for
+figures, tables and sections below. For instance in Section
+@ref(sec:tables) you can find different ways of referencing tables. The
+code of the underlying \texttt{paper.rmd} will show you how we
+referenced Section @ref(sec:tables) right here namely with
+`\texttt{Section\ \textbackslash{}@ref(sec:tables)}'.
 
@@
 
-Software changes and gets updated, especially with an active developer community like that of R.
-Luckily you can always access \href{https://cran.r-project.org/bin/windows/base/old/}{old versions of R} and old version of R packages in \href{https://cran.r-project.org/src/contrib/Archive/}{the archive}.
-In the archive you need to choose a particular package, e.g dplyr and search for the right version, e.g., \texttt{dplyr\_0.2.tar.gz}.
-Then insert the path in the following function: \texttt{install.packages("https://....../dplyr\_0.2.tar.gz",\ repos=NULL,\ type="source")}.
-Ideally, however, results will be simply reproducible in the most current R and package versions.
+Software changes and gets updated, especially with an active developer
+community like that of R. Luckily you can always access
+\href{https://cran.r-project.org/bin/windows/base/old/}{old versions of
+R} and old version of R packages in
+\href{https://cran.r-project.org/src/contrib/Archive/}{the archive}. In
+the archive you need to choose a particular package, e.g dplyr and
+search for the right version, e.g., \texttt{dplyr\_0.2.tar.gz}. Then
+insert the path in the following function:
+\texttt{install.packages("https://....../dplyr\_0.2.tar.gz",\ repos=NULL,\ type="source")}.
+Ideally, however, results will be simply reproducible in the most
+current R and package versions.
 
-We would recommend to use the command below and simply add it to the appendix as we did here in Appendix \ref{sec:rsessioninfo}.
-This will make sure you always provide the package versions that you used in the last compilation of your paper.
-For more advanced tools see \href{https://rstudio.github.io/packrat/}{packrat}.
+We would recommend to use the command below and simply add it to the
+appendix as we did here in Appendix @ref(sec:rsessioninfo). This will
+make sure you always provide the package versions that you used in the
+last compilation of your paper. For more advanced tools see
+\href{https://rstudio.github.io/packrat/}{packrat}.
 
@@
 \hypertarget{putting-your-entire-data-into-the-.rmd-file}{%
-\subsection{Putting your entire data into the .rmd file}\label{putting-your-entire-data-into-the-.rmd-file}}
+\subsection{Putting your entire data into the .rmd
+file}\label{putting-your-entire-data-into-the-.rmd-file}}
 
-Applying the function \texttt{dput()} to an object gives you the code needed to reproduce that object.
-So you could paste that code into your \texttt{.rmd} file if you don't want to have extra data files.
-This makes sense were data files are small.
+Applying the function \texttt{dput()} to an object gives you the code
+needed to reproduce that object. So you could paste that code into your
+\texttt{.rmd} file if you don't want to have extra data files. This
+makes sense were data files are small.
 
@@
 
-Producing good tables and referencing these tables within a R Markdown PDF has been a hassle but got much better.
-Examples that you may use are shown below.
-The way you reference tables is slightly different, e.g., for \texttt{stargazer} the label is contained in the function, for \texttt{kable} it's contained in the chunk name.
+Producing good tables and referencing these tables within a R Markdown
+PDF has been a hassle but got much better. Examples that you may use are
+shown below. The way you reference tables is slightly different, e.g.,
+for \texttt{stargazer} the label is contained in the function, for
+\texttt{kable} it's contained in the chunk name.
 
 \hypertarget{stargazer-summary-and-regression-tables}{%
-\subsection{stargazer(): Summary and regression tables}\label{stargazer-summary-and-regression-tables}}
+\subsection{stargazer(): Summary and regression
+tables}\label{stargazer-summary-and-regression-tables}}
 
-Table \ref{tab1} shows summary stats of your data.\footnote{To reference the table where you set the identifier in the stargazer function you only need to use the actual label, i.e., ´tab1´.} We normally use \texttt{stargazer()} (\protect\hyperlink{ref-hlavac2013stargazer}{Hlavac 2013}) which offers extreme flexibility regarding table output (see \texttt{?stargazer}).
+Table @ref(tab1) shows summary stats of your data.\footnote{To reference
+  the table where you set the identifier in the stargazer function you
+  only need to use the actual label, i.e., ´tab1´.} We normally use
+\texttt{stargazer()} (\protect\hyperlink{ref-hlavac2013stargazer}{Hlavac
+2013}) which offers extreme flexibility regarding table output (see
+\texttt{?stargazer}).
 
@@
 
-Table \ref{tab2} shows the output for a regression table. Make sure you name all your models and explicitly refer to model names (M1, M2 etc.) in the text.
+Table @ref(tab2) shows the output for a regression table. Make sure you
+name all your models and explicitly refer to model names (M1, M2 etc.)
+in the text.
 
@@
 \hypertarget{kable-and-kable_styling}{%
-\subsection{kable() and kable\_styling()}\label{kable-and-kable_styling}}
+\subsection{kable() and
+kable\_styling()}\label{kable-and-kable_styling}}
 
-Another great function is \texttt{kable()} (\texttt{knitr} package) in combination with \texttt{kableExtra}.
-Table \ref{tab:tab3} provides an example.\footnote{To reference the table produced by the chunk you need to add ´tab:´ to the chunk name, i.e., ´tab:tab3´.} Again you can modify so many things in both the \texttt{kable()} and the \texttt{kable\_styling()} function.
-See \href{https://haozhu233.github.io/kableExtra/awesome_table_in_pdf.pdf}{this overview} of all the kable stylings that are possible provided by the package author himself.
+Another great function is \texttt{kable()} (\texttt{knitr} package) in
+combination with \texttt{kableExtra}. Table @ref(tab:tab3) provides an
+example.\footnote{To reference the table produced by the chunk you need
+  to add ´tab:´ to the chunk name, i.e., ´tab:tab3´.} Again you can
+modify so many things in both the \texttt{kable()} and the
+\texttt{kable\_styling()} function. See
+\href{https://haozhu233.github.io/kableExtra/awesome_table_in_pdf.pdf}{this
+overview} of all the kable stylings that are possible provided by the
+package author himself.
 
@@
 
-Reproduction reaches new heights when you work with inline code.
-For instance, you can automatize the display of certain coefficients within the text.
-An example is to include estimates, e.g., the coefficient of \texttt{dist} of the model we ran above.
-\texttt{\textasciigrave{}r\ round(coef(model1){[}2{]},\ 2)\textasciigrave{}} will insert the coefficient as follows: 0.17.
-Or \texttt{\textasciigrave{}r\ 3\ +\ 7\textasciigrave{}} will insert a 10 in the text.\\
-Inline code/results that depend on earlier objects in your document will automatically be updated once you change those objects.
-For instance, imagine a reviewer asks you to omit certain observations from your sample.
-You can simply do so in the beginning of your code and push play subsequently..
-at time you might have to set \texttt{cache\ =\ FALSE} at the beginning so that all the code chunks are rerun.\\
-Researchers often avoid referring to results in-text etc.
-because you easily forget to change them when revising a manuscript.
-At the same it can make an article much more informative and easier to read, e.g., if you discuss a coefficient in the text you can directly show it in the section in which you discuss it.
-Inline code allows you to do just that.
-R Markdown allows you to that do so in a reproducible and automatized manner.
+Reproduction reaches new heights when you work with inline code. For
+instance, you can automatize the display of certain coefficients within
+the text. An example is to include estimates, e.g., the coefficient of
+\texttt{dist} of the model we ran above.
+\texttt{\textasciigrave{}r\ round(coef(model1){[}2{]},\ 2)\textasciigrave{}}
+will insert the coefficient as follows: 0.17. Or
+\texttt{\textasciigrave{}r\ 3\ +\ 7\textasciigrave{}} will insert a 10
+in the text.\\
+Inline code/results that depend on earlier objects in your document will
+automatically be updated once you change those objects. For instance,
+imagine a reviewer asks you to omit certain observations from your
+sample. You can simply do so in the beginning of your code and push play
+subsequently.. at time you might have to set \texttt{cache\ =\ FALSE} at
+the beginning so that all the code chunks are rerun.\\
+Researchers often avoid referring to results in-text etc. because you
+easily forget to change them when revising a manuscript. At the same it
+can make an article much more informative and easier to read, e.g., if
+you discuss a coefficient in the text you can directly show it in the
+section in which you discuss it. Inline code allows you to do just that.
+R Markdown allows you to that do so in a reproducible and automatized
+manner.
 
@@
 
-Inserting figures can be slightly more complicated.
-Ideally, we would produce and insert them directly in the \texttt{.rmd} file.
-It's relatively simple to insert R base graphs as you can see in Figure \ref{fig:fig-1}.
+Inserting figures can be slightly more complicated. Ideally, we would
+produce and insert them directly in the \texttt{.rmd} file. It's
+relatively simple to insert R base graphs as you can see in Figure
+@ref(fig:fig-1).
 
@@
 
-Same is true for ggplot2 as you can see in Figure \ref{fig:fig-2}.
+Same is true for ggplot2 as you can see in Figure @ref(fig:fig-2).
 
@@
 
-Every researcher has his own optimized setup. Currently we would recommend the following:
+Every researcher has his own optimized setup. Currently we would
+recommend the following:
 
@@
 \item
-  Keep all files of your project (that matter for producing the PDF) in one folder without subfolders.
-You can zip and directly upload that folder to the \href{https://dataverse.harvard.edu/}{Harvard dataverse}.
+  Keep all files of your project (that matter for producing the PDF) in
+  one folder without subfolders. You can zip and directly upload that
+  folder to the \href{https://dataverse.harvard.edu/}{Harvard
+  dataverse}.
 \item
@@
   \item
-    Ideally, your filenames will correspond to the names in the paper. For instance, Figure 1 in the paper may have a corresponding file called \texttt{fig\_1\_xxxxx.pdf}.
+    Ideally, your filenames will correspond to the names in the paper.
+    For instance, Figure 1 in the paper may have a corresponding file
+    called \texttt{fig\_1\_xxxxx.pdf}.
   \end{itemize}
 \item
-  Use the document outline in R studio (Ctrl + Shift + O) when you work with R Markdown.
+  Use the document outline in R studio (Ctrl + Shift + O) when you work
+  with R Markdown.
 \item
@@
 \item
-  Ideally give chunks the labels of the figures/tables in the final publication, e.g., ``\texttt{fig-1}'' is the name of the chunk that produces Figure 1 in the final paper.
+  Ideally give chunks the labels of the figures/tables in the final
+  publication, e.g., ``\texttt{fig-1}'' is the name of the chunk that
+  produces Figure 1 in the final paper.
 \item
@@
   \item
-    Q: What do you think does the variable \emph{trstep} measure? It actually measures trust in the European parliament.
+    Q: What do you think does the variable \emph{trstep} measure? It
+    actually measures trust in the European parliament.
 
@@
     \item
-      How could we call this variable instead? Yes, \texttt{trust.european.parliament} which is longer but will probably be understood by another researcher.
+      How could we call this variable instead? Yes,
+      \texttt{trust.european.parliament} which is longer but will
+      probably be understood by another researcher.
     \end{itemize}
   \item
-    If your setup is truly reproducible you will probably re-use the variable names that you generate as variable names in the tables you produce. Hence, there is an incentive to use good names.
+    If your setup is truly reproducible you will probably re-use the
+    variable names that you generate as variable names in the tables you
+    produce. Hence, there is an incentive to use good names.
   \end{itemize}
@@
   \item
-    Think of someone who wants to produce Figure 1/Model 1 in your paper but doesn't find it in your code\ldots{}
+    Think of someone who wants to produce Figure 1/Model 1 in your paper
+    but doesn't find it in your code\ldots{}
   \end{itemize}
@@
 \hypertarget{additional-tricks-for-publishing}{%
-\section{Additional tricks for publishing}\label{additional-tricks-for-publishing}}
+\section{Additional tricks for
+publishing}\label{additional-tricks-for-publishing}}
 
@@
   \item
-    Simply put a \texttt{\textless{}!-\/-\ ...\ -\/-\textgreater{}} around any identifying information, e.g., author names, title footnote etc.
+    Simply put a \texttt{\textless{}!-\/-\ ...\ -\/-\textgreater{}}
+    around any identifying information, e.g., author names, title
+    footnote etc.
   \end{itemize}
@@
   \item
-    Use adobe acrobat (commerical software) to convert your file to a word file.
-Then open in word and delete all the parts that shouldn't go into the word count.
-The word count is displayed in the lower right.
+    Use adobe acrobat (commerical software) to convert your file to a
+    word file. Then open in word and delete all the parts that shouldn't
+    go into the word count. The word count is displayed in the lower
+    right.
   \item
-    Use an one of the online services to count your words (search for ``pdf word count'')
+    Use an one of the online services to count your words (search for
+    ``pdf word count'')
   \end{itemize}
 \item
-  Appendix: You can change the numbering format for the appendix in the rmd file
+  Appendix: You can change the numbering format for the appendix in the
+  rmd file
 
@@
   \item
-    What is still not possible in this document is to automatically have separate reference sections for paper and appendix.
+    What is still not possible in this document is to automatically have
+    separate reference sections for paper and appendix.
   \end{itemize}
 \item
-  Journals may require you to use their tex style: Sometimes you can simply use their template in your rmarkdown file.
-See \href{https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/LDUMNY}{here} for a PLOS one example.
+  Journals may require you to use their tex style: Sometimes you can
+  simply use their template in your rmarkdown file. See
+  \href{https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/LDUMNY}{here}
+  for a PLOS one example.
 \end{itemize}
@@
 
-If your study needs to follow a particular citation style, you can set the corresponding style in the header of your \texttt{.rmd} document.
-To do so you have to download the corresponding \texttt{.csl} file.
+If your study needs to follow a particular citation style, you can set
+the corresponding style in the header of your \texttt{.rmd} document. To
+do so you have to download the corresponding \texttt{.csl} file.
 
-In the present document we use the style of the American Sociological Association and set it in the preamble with \texttt{csl:\ american-sociological-association.csl}.
-However, you also need to download the respective \texttt{.csl} file from the following Github page: \url{https://github.com/citation-style-language/styles} and copy it into your working directory for it to work.
+In the present document we use the style of the American Sociological
+Association and set it in the preamble with
+\texttt{csl:\ american-sociological-association.csl}. However, you also
+need to download the respective \texttt{.csl} file from the following
+Github page: \url{https://github.com/citation-style-language/styles} and
+copy it into your working directory for it to work.
 
-The Github directory contains a wide variety of citation style files depending on what discipline you work in.
+The Github directory contains a wide variety of citation style files
+depending on what discipline you work in.
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-markdown2017}{}}%
-Allaire, JJ, Jeffrey Horner, Vicent Marti, and Natacha Porte. 2017. \emph{\href{https://CRAN.R-project.org/package=markdown}{Markdown: 'Markdown' Rendering for r}}.
+Allaire, JJ, Jeffrey Horner, Vicent Marti, and Natacha Porte. 2017.
+\emph{\href{https://CRAN.R-project.org/package=markdown}{Markdown:
+'Markdown' Rendering for r}}.
 
 \leavevmode\vadjust pre{\hypertarget{ref-hlavac2013stargazer}{}}%
-Hlavac, Marek. 2013. {``Stargazer: LaTeX Code and ASCII Text for Well-Formatted Regression and Summary Statistics Tables.''} \emph{URL: Http://CRAN. R-Project. Org/Package= Stargazer}.
+Hlavac, Marek. 2013. {``Stargazer: LaTeX Code and ASCII Text for
+Well-Formatted Regression and Summary Statistics Tables.''} \emph{URL:
+Http://CRAN. R-Project. Org/Package= Stargazer}.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Kirsop2005-ro}{}}%
-Kirsop, Barbara and Leslie Chan. 2005. {``Transforming Access to Research Literature for Developing Countries.''} \emph{Serials Review} 31(4):246--55.
+Kirsop, Barbara and Leslie Chan. 2005. {``Transforming Access to
+Research Literature for Developing Countries.''} \emph{Serials Review}
+31(4):246--55.
 
 \leavevmode\vadjust pre{\hypertarget{ref-R2017}{}}%
-R Core Team. 2017. \emph{\href{https://www.R-project.org/}{R: A Language and Environment for Statistical Computing}}. Vienna, Austria: R Foundation for Statistical Computing.
+R Core Team. 2017. \emph{\href{https://www.R-project.org/}{R: A Language
+and Environment for Statistical Computing}}. Vienna, Austria: R
+Foundation for Statistical Computing.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Rstudio2015}{}}%
-RStudio Team. 2015. \emph{\href{http://www.rstudio.com/}{RStudio: Integrated Development Environment for r}}. Boston, MA: RStudio, Inc.
+RStudio Team. 2015. \emph{\href{http://www.rstudio.com/}{RStudio:
+Integrated Development Environment for r}}. Boston, MA: RStudio, Inc.
 
 \leavevmode\vadjust pre{\hypertarget{ref-plotly}{}}%
-Sievert, Carson, Chris Parmer, Toby Hocking, Scott Chamberlain, Karthik Ram, Marianne Corvellec, and Pedro Despouy.
-2017.
-\emph{\href{https://CRAN.R-project.org/package=plotly}{Plotly: Create Interactive Web Graphics via 'Plotly.js'}}.
+Sievert, Carson, Chris Parmer, Toby Hocking, Scott Chamberlain, Karthik
+Ram, Marianne Corvellec, and Pedro Despouy. 2017.
+\emph{\href{https://CRAN.R-project.org/package=plotly}{Plotly: Create
+Interactive Web Graphics via 'Plotly.js'}}.
 
 \leavevmode\vadjust pre{\hypertarget{ref-knitr3}{}}%
-Xie, Yihui.
-2014.
-{``\href{http://www.crcpress.com/product/isbn/9781466561595}{Knitr: A Comprehensive Tool for Reproducible Research in {R}}.''} in \emph{Implementing reproducible computational research}, edited by V.
-Stodden, F.
-Leisch, and R.
-D.
-Peng.
+Xie, Yihui. 2014.
+{``\href{http://www.crcpress.com/product/isbn/9781466561595}{Knitr: A
+Comprehensive Tool for Reproducible Research in {R}}.''} in
+\emph{Implementing reproducible computational research}, edited by V.
+Stodden, F. Leisch, and R. D. Peng. Chapman; Hall/CRC.
+
+\leavevmode\vadjust pre{\hypertarget{ref-knitr2}{}}%
+Xie, Yihui. 2015. \emph{\href{https://yihui.name/knitr/}{Dynamic
+Documents with {R} and Knitr}}. 2nd ed. Boca Raton, Florida: Chapman;
+Hall/CRC.
+
+\leavevmode\vadjust pre{\hypertarget{ref-bookdown2}{}}%
+Xie, Yihui. 2016.
+\emph{\href{https://github.com/rstudio/bookdown}{Bookdown: Authoring
+Books and Technical Documents with {R} Markdown}}. Boca Raton, Florida:
 Chapman; Hall/CRC.
 
-\leavevmode\vadjust pre{\hypertarget{ref-knitr2}{}}%
-Xie, Yihui. 2015. \emph{\href{https://yihui.name/knitr/}{Dynamic Documents with {R} and Knitr}}. 2nd ed. Boca Raton, Florida: Chapman; Hall/CRC.
-
-\leavevmode\vadjust pre{\hypertarget{ref-bookdown2}{}}%
-Xie, Yihui. 2016. \emph{\href{https://github.com/rstudio/bookdown}{Bookdown: Authoring Books and Technical Documents with {R} Markdown}}. Boca Raton, Florida: Chapman; Hall/CRC.
-
 \leavevmode\vadjust pre{\hypertarget{ref-bookdown1}{}}%
-Xie, Yihui. 2017. \emph{\href{https://github.com/rstudio/bookdown}{Bookdown: Authoring Books and Technical Documents with r Markdown}}.
+Xie, Yihui. 2017.
+\emph{\href{https://github.com/rstudio/bookdown}{Bookdown: Authoring
+Books and Technical Documents with r Markdown}}.
 
 \leavevmode\vadjust pre{\hypertarget{ref-knitr1}{}}%
-Xie, Yihui. 2018a. \emph{\href{https://yihui.name/knitr/}{Knitr: A General-Purpose Package for Dynamic Report Generation in r}}.
+Xie, Yihui. 2018a. \emph{\href{https://yihui.name/knitr/}{Knitr: A
+General-Purpose Package for Dynamic Report Generation in r}}.
 
 \leavevmode\vadjust pre{\hypertarget{ref-tinytex}{}}%
-Xie, Yihui. 2018b. \emph{\href{https://CRAN.R-project.org/package=tinytex}{Tinytex: Helper Functions to Install and Maintain 'TeX Live', and Compile 'LaTeX' Documents}}.
+Xie, Yihui. 2018b.
+\emph{\href{https://CRAN.R-project.org/package=tinytex}{Tinytex: Helper
+Functions to Install and Maintain 'TeX Live', and Compile 'LaTeX'
+Documents}}.
 
 \leavevmode\vadjust pre{\hypertarget{ref-kableextra}{}}%
-Zhu, Hao. 2017. \emph{\href{https://CRAN.R-project.org/package=kableExtra}{kableExtra: Construct Complex Table with 'Kable' and Pipe Syntax}}.
+Zhu, Hao. 2017.
+\emph{\href{https://CRAN.R-project.org/package=kableExtra}{kableExtra:
+Construct Complex Table with 'Kable' and Pipe Syntax}}.
 
@@
 
-Since R and R packages are constantly evolving you might want to add the R session info that contains information on the R version as well as the packages that are loaded.
+Since R and R packages are constantly evolving you might want to add the
+R session info that contains information on the R version as well as the
+packages that are loaded.
 
@@
 ## Platform: aarch64-apple-darwin20 (64-bit)
-## Running under: macOS Ventura 13.0.1
+## Running under: macOS Ventura 13.2.1
 ## 
@@
 ## other attached packages:
-## [1] ggplot2_3.4.2    kableExtra_1.3.4 knitr_1.42       stargazer_5.2.3 
+## [1] ggplot2_3.4.2         kableExtra_1.3.4.9000 knitr_1.42           
+## [4] stargazer_5.2.3      
 ## 
@@
 ## [29] glue_1.6.2        R6_2.5.1          fansi_1.0.4       rmarkdown_2.21   
-## [33] bookdown_0.33     farver_2.1.1      magrittr_2.0.3    scales_1.2.1     
-## [37] htmltools_0.5.5   rvest_1.0.3       colorspace_2.1-0  labeling_0.4.2   
-## [41] utf8_1.2.3        stringi_1.7.12    munsell_0.5.0
+## [33] farver_2.1.1      magrittr_2.0.3    scales_1.2.1      htmltools_0.5.5  
+## [37] rvest_1.0.3       colorspace_2.1-0  labeling_0.4.2    utf8_1.2.3       
+## [41] stringi_1.7.12    munsell_0.5.0
 \end{verbatim}
@@
 
-To simply attach all the code you used in the PDF file in the appendix see the R chunk in the underlying \texttt{.rmd} file:
+To simply attach all the code you used in the PDF file in the appendix
+see the R chunk in the underlying \texttt{.rmd} file:
 

### 2023-06-19 paper.Rmd
small edits.
and revert back to using bookdown::pdf_document2 for cross-references.

@@
   | 
-  | 
-  | \vspace{1cm}Writing a reproducible paper
+  | \vspace{0.7cm}Writing a reproducible paper
   | in R Markdown^[Corresponding address: mail@paulcbauer.de. Acknowledgments: We are grateful to all those generous people that invest their time into open-source software.]\vspace{0.5cm}
@@
   | This version: `r gsub("^0", "", format(Sys.time(), "%B %d, %Y"))`
-  | Download: https://osf.io/q395s
+  | Download this Paper on OSF: https://osf.io/q395s
   |
@@
 abstract: \noindent\setstretch{1}The present paper provides a template for a reproducible scientific paper written in R Markdown.
-Below we outline some of the "tricks"/code (e.g., referencing tables, sections etc.) we had to figure out to produce this document.
+Below, we outline some of the "tricks"/code (e.g., referencing tables, sections, etc.) we had to figure out to produce this document.
 The underlying files which produce this document can be downloaded [here](https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown) (click on Code -> Download ZIP).
-We think we got pretty far but there is always room for improvement and more automatization, in parallel to the incredible developments in R and Rstudio (bookdown etc.).
-We intend to update this file when we discover more convenient code (you can follow any updates through the corresponding [Github repo](https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown/)).\vspace{.8cm}
+We think we got pretty far, but there is always room for improvement and more automatization, in parallel to the incredible developments in R and Rstudio (e.g., bookdown).
+We intend to update this file when we discover more convenient code and you can follow any updates through the corresponding [Github repo](https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown/).\vspace{.8cm}
 bibliography: references.bib
@@
 output:
-  pdf_document:
+  bookdown::pdf_document2:
     toc: no
@@
 
-* **Access**: Research is normally funded by taxpayers (researchers are also taxpayers).
-Hence, it should be freely accessible to everyone without any barriers, e.g., without requiring commercial software.
-Importantly, researchers from developing countries are even more dependent on free access to knowledge [@Kirsop2005-ro].
-* **Reproducability**: Even if you have written a study and analyzed the data yourself you will forget what you did after a few months.
-A fully reproducible setup will help you to trace back your own steps.
-Obviously, the same is true for other researchers who may want to understand your work and built on it.
-It may sound like a joke but why not aim for a document that can be used to reproduce your findings in 500 years.
-* **Errors**: Manual steps in data analysis (e.g., manually copy/pasting values into a table etc.) may introduce errors. R Markdown allows you to **automatize** such steps and/or avoid them.
-* **Revisions**: Revising a paper takes much less time if you have all the code you need in one place, i.e., one `.rmd` file.
-For instance, if you decide to exclude a subset of your data you simply need to insert one line of your code at the beginning and everything is rebuilt/re-estimated automatically.
+* **Access**: Research is typically funded by taxpayers (and researchers are also taxpayers).
+Hence, it should be freely accessible to everyone without any barriers, such as the requirement of commercial software.
+Importantly, researchers from developing countries are particularly dependent on free access to knowledge [@Kirsop2005-ro].
+* **Reproducibility**: Even if you have conducted a study and analyzed the data yourself, you may forget the steps taken after a few months.
+A fully reproducible setup will help you retrace your own steps.
+Additionally, other researchers who wish to understand and build upon your work will benefit from reproducibility.
+It may sound like a joke, but why not aim for a document that can be used to reproduce your findings even after 500 years?
+* **Errors**: Manual steps in data analysis, such as manually copying/pasting values into a table, can introduce errors. R Markdown allows you to automate such steps and/or avoid them.
+* **Revisions**: Revising a paper takes much less time if you have all the code you need in one place, i.e., one .rmd file.
+For instance, if you decide to exclude a subset of your data, you simply need to insert one line of code at the beginning, and everything is automatically rebuilt/re-estimated.
 
-# Prerequesites
+# Prerequisites
 We assume that you are using R on a day-to-day basis.
-You may have even started to work a little in R Markdown but you don't write your complete paper in R Markdown.
-If you don't know what R Markdown is watch [this short video](https://vimeo.com/178485416).
+You may have even started to work a little in R Markdown, but you don't write your complete paper in R Markdown.
+If you don't know what R Markdown is, watch [this short video](https://vimeo.com/178485416).
 Then...
@@
 
-```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE, results="asis"}
+```{r tab1, echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE, results="asis"}
 library(stargazer)
@@
 
+# Figures
+
+## R base graphs
+
+Inserting figures can be slightly more complicated.
+Ideally, we would produce and insert them directly in the `.rmd` file.
+It's relatively simple to insert R base graphs as you can see in Figure \@ref(fig:fig-1))
+
+```{r fig-1, fig.align="center", fig.cap="Scatterplot of Speed and Distance", fig.pos="H", message=FALSE, warning=FALSE, paged.print=FALSE}
+plot(cars$speed, cars$dist)
+```
+
+But it turns out that it doesn't always work so well.
+
+## ggplot2 graphs
+Same is true for ggplot2 as you can see in Figure \@ref(fig:fig-2).
+
+```{r fig-2, fig.align="center", fig.cap="Miles per gallon according to the weight", fig.pos="H", fig.width=6, fig.height=3, message=FALSE, warning=FALSE, paged.print=FALSE, echo=F}
+mtcars$cyl <- as.factor(mtcars$cyl) # Convert cyl to factor
+library(ggplot2)
+ggplot(mtcars, aes(x=wt, y=mpg, shape=cyl)) + geom_point() +
+  labs(x="Weight (lb/1000)", y = "Miles/(US) gallon", 
+       shape="Number of \n Cylinders") + theme_classic()
+```
+
 # Inline code & results
@@
 R Markdown allows you to that do so in a reproducible and automatized manner.
-
-# Figures
-
-## R base graphs
-Inserting figures can be slightly more complicated.
-Ideally, we would produce and insert them directly in the `.rmd` file.
-It's relatively simple to insert R base graphs as you can see in Figure \@ref(fig:fig-1).
-
-```{r fig-1, fig.align="center", fig.cap="Scatterplot of Speed and Distance", fig.pos="H", message=FALSE, warning=FALSE, paged.print=FALSE}
-plot(cars$speed, cars$dist)
-```
-
-But it turns out that it doesn't always work so well.
-
-## ggplot2 graphs
-Same is true for ggplot2 as you can see in Figure \@ref(fig:fig-2).
-
-```{r fig-2, fig.align="center", fig.cap="Miles per gallon according to the weight", fig.pos="H", fig.width=6, fig.height=3, message=FALSE, warning=FALSE, paged.print=FALSE}
-mtcars$cyl <- as.factor(mtcars$cyl) # Convert cyl to factor
-library(ggplot2)
-ggplot(mtcars, aes(x=wt, y=mpg, shape=cyl)) + geom_point() +
-  labs(x="Weight (lb/1000)", y = "Miles/(US) gallon", 
-       shape="Number of \n Cylinders") + theme_classic()
-```
 

### 2023-06-19 paper.tex
small edits.
and revert back to using bookdown::pdf_document2 for cross-references.

--- 2023-04-05 paper.tex
@@
 \title{\hfill\break
-\hfill\break
-\vspace{1cm}Writing a reproducible paper\\
+\vspace{0.7cm}Writing a reproducible paper\\
 in R Markdown\footnote{Corresponding address: \href{mailto:mail@paulcbauer.de}{\nolinkurl{mail@paulcbauer.de}}.
@@
 First version: December 14, 2018\\
-This version: April 05, 2023\\
-Download: \url{https://osf.io/q395s}\\
+This version: June 19, 2023\\
+Download this Paper on OSF: \url{https://osf.io/q395s}\\
 \strut \\
@@
 \noindent\setstretch{1}The present paper provides a template for a reproducible scientific paper written in R Markdown.
-Below we outline some of the ``tricks''/code (e.g., referencing tables, sections etc.) we had to figure out to produce this document.
+Below, we outline some of the ``tricks''/code (e.g., referencing tables, sections, etc.) we had to figure out to produce this document.
 The underlying files which produce this document can be downloaded \href{https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown}{here} (click on Code -\textgreater{} Download ZIP).
-We think we got pretty far but there is always room for improvement and more automatization, in parallel to the incredible developments in R and Rstudio (bookdown etc.).
-We intend to update this file when we discover more convenient code (you can follow any updates through the corresponding \href{https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown/}{Github repo}).\vspace{.8cm}
+We think we got pretty far, but there is always room for improvement and more automatization, in parallel to the incredible developments in R and Rstudio (e.g., bookdown).
+We intend to update this file when we discover more convenient code and you can follow any updates through the corresponding \href{https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown/}{Github repo}.\vspace{.8cm}
 \end{abstract}
@@
 \item
-  \textbf{Access}: Research is normally funded by taxpayers (researchers are also taxpayers).
-Hence, it should be freely accessible to everyone without any barriers, e.g., without requiring commercial software.
-Importantly, researchers from developing countries are even more dependent on free access to knowledge (\protect\hyperlink{ref-Kirsop2005-ro}{Kirsop and Chan 2005}).
+  \textbf{Access}: Research is typically funded by taxpayers (and researchers are also taxpayers).
+Hence, it should be freely accessible to everyone without any barriers, such as the requirement of commercial software.
+Importantly, researchers from developing countries are particularly dependent on free access to knowledge (\protect\hyperlink{ref-Kirsop2005-ro}{Kirsop and Chan 2005}).
 \item
-  \textbf{Reproducability}: Even if you have written a study and analyzed the data yourself you will forget what you did after a few months.
-A fully reproducible setup will help you to trace back your own steps.
-Obviously, the same is true for other researchers who may want to understand your work and built on it.
-It may sound like a joke but why not aim for a document that can be used to reproduce your findings in 500 years.
+  \textbf{Reproducibility}: Even if you have conducted a study and analyzed the data yourself, you may forget the steps taken after a few months.
+A fully reproducible setup will help you retrace your own steps.
+Additionally, other researchers who wish to understand and build upon your work will benefit from reproducibility.
+It may sound like a joke, but why not aim for a document that can be used to reproduce your findings even after 500 years?
 \item
-  \textbf{Errors}: Manual steps in data analysis (e.g., manually copy/pasting values into a table etc.) may introduce errors. R Markdown allows you to \textbf{automatize} such steps and/or avoid them.
+  \textbf{Errors}: Manual steps in data analysis, such as manually copying/pasting values into a table, can introduce errors. R Markdown allows you to automate such steps and/or avoid them.
 \item
-  \textbf{Revisions}: Revising a paper takes much less time if you have all the code you need in one place, i.e., one \texttt{.rmd} file.
-For instance, if you decide to exclude a subset of your data you simply need to insert one line of your code at the beginning and everything is rebuilt/re-estimated automatically.
+  \textbf{Revisions}: Revising a paper takes much less time if you have all the code you need in one place, i.e., one .rmd file.
+For instance, if you decide to exclude a subset of your data, you simply need to insert one line of code at the beginning, and everything is automatically rebuilt/re-estimated.
 \end{itemize}
 
-\hypertarget{prerequesites}{%
-\section{Prerequesites}\label{prerequesites}}
+\hypertarget{prerequisites}{%
+\section{Prerequisites}\label{prerequisites}}
 
 We assume that you are using R on a day-to-day basis.
-You may have even started to work a little in R Markdown but you don't write your complete paper in R Markdown.
-If you don't know what R Markdown is watch \href{https://vimeo.com/178485416}{this short video}.
+You may have even started to work a little in R Markdown, but you don't write your complete paper in R Markdown.
+If you don't know what R Markdown is, watch \href{https://vimeo.com/178485416}{this short video}.
 Then\ldots{}
@@
 
-\hypertarget{inline-code-results}{%
-\section{Inline code \& results}\label{inline-code-results}}
-
-Reproduction reaches new heights when you work with inline code.
-For instance, you can automatize the display of certain coefficients within the text.
-An example is to include estimates, e.g., the coefficient of \texttt{dist} of the model we ran above.
-\texttt{\textasciigrave{}r\ round(coef(model1){[}2{]},\ 2)\textasciigrave{}} will insert the coefficient as follows: 0.17.
-Or \texttt{\textasciigrave{}r\ 3\ +\ 7\textasciigrave{}} will insert a 10 in the text.\\
-Inline code/results that depend on earlier objects in your document will automatically be updated once you change those objects.
-For instance, imagine a reviewer asks you to omit certain observations from your sample.
-You can simply do so in the beginning of your code and push play subsequently..
-at time you might have to set \texttt{cache\ =\ FALSE} at the beginning so that all the code chunks are rerun.\\
-Researchers often avoid referring to results in-text etc.
-because you easily forget to change them when revising a manuscript.
-At the same it can make an article much more informative and easier to read, e.g., if you discuss a coefficient in the text you can directly show it in the section in which you discuss it.
-Inline code allows you to do just that.
-R Markdown allows you to that do so in a reproducible and automatized manner.
-
 \hypertarget{figures}{%
@@
 Ideally, we would produce and insert them directly in the \texttt{.rmd} file.
-It's relatively simple to insert R base graphs as you can see in Figure \ref{fig:fig-1}.
+It's relatively simple to insert R base graphs as you can see in Figure \ref{fig:fig-1})
 
@@
 
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{mtcars}\SpecialCharTok{$}\NormalTok{cyl }\OtherTok{\textless{}{-}} \FunctionTok{as.factor}\NormalTok{(mtcars}\SpecialCharTok{$}\NormalTok{cyl) }\CommentTok{\# Convert cyl to factor}
-\FunctionTok{library}\NormalTok{(ggplot2)}
-\FunctionTok{ggplot}\NormalTok{(mtcars, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x=}\NormalTok{wt, }\AttributeTok{y=}\NormalTok{mpg, }\AttributeTok{shape=}\NormalTok{cyl)) }\SpecialCharTok{+} \FunctionTok{geom\_point}\NormalTok{() }\SpecialCharTok{+}
-  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x=}\StringTok{"Weight (lb/1000)"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Miles/(US) gallon"}\NormalTok{, }
-       \AttributeTok{shape=}\StringTok{"Number of }\SpecialCharTok{\textbackslash{}n}\StringTok{ Cylinders"}\NormalTok{) }\SpecialCharTok{+} \FunctionTok{theme\_classic}\NormalTok{()}
-\end{Highlighting}
-\end{Shaded}
-
 \begin{figure}[H]
@@
 \end{figure}
+
+\hypertarget{inline-code-results}{%
+\section{Inline code \& results}\label{inline-code-results}}
+
+Reproduction reaches new heights when you work with inline code.
+For instance, you can automatize the display of certain coefficients within the text.
+An example is to include estimates, e.g., the coefficient of \texttt{dist} of the model we ran above.
+\texttt{\textasciigrave{}r\ round(coef(model1){[}2{]},\ 2)\textasciigrave{}} will insert the coefficient as follows: 0.17.
+Or \texttt{\textasciigrave{}r\ 3\ +\ 7\textasciigrave{}} will insert a 10 in the text.\\
+Inline code/results that depend on earlier objects in your document will automatically be updated once you change those objects.
+For instance, imagine a reviewer asks you to omit certain observations from your sample.
+You can simply do so in the beginning of your code and push play subsequently..
+at time you might have to set \texttt{cache\ =\ FALSE} at the beginning so that all the code chunks are rerun.\\
+Researchers often avoid referring to results in-text etc.
+because you easily forget to change them when revising a manuscript.
+At the same it can make an article much more informative and easier to read, e.g., if you discuss a coefficient in the text you can directly show it in the section in which you discuss it.
+Inline code allows you to do just that.
+R Markdown allows you to that do so in a reproducible and automatized manner.
 

### 2023-06-19 paper.Rmd
small edits.

@@
 knitr::opts_chunk$set(cache = FALSE)
-# Use chache = TRUE if you want to speed up compilation
+# Use cache = TRUE if you want to speed up compilation
+```
 
+```{r inline, include=FALSE}
 # A function to allow for showing some of the inline code
@@
 * ...install [tinytex](https://yihui.name/tinytex/), a lightweight version of Tex Live [@markdown2017; @tinytex].
-```{r eval=FALSE, include=TRUE}
+```{r packages-1, eval=FALSE, include=TRUE}
 install.packages(c('tinytex', 'rmarkdown'))
@@
 ```
-* ...install the packages below using the code below [@bookdown1; @bookdown2; @knitr1; @knitr2; @knitr3; @kableextra; @plotly].
-```{r eval=FALSE, include=TRUE}
+* ...install the packages below using the code below [@bookdown1; @bookdown2; @knitr1; @knitr2; @knitr3; @kableextra].
+```{r packages-2, eval=FALSE, include=TRUE}
 install.packages(c("rmarkdown", "knitr", "kableExtra",
-                   "stargazer", "plotly", "knitr",
+                   "stargazer", "knitr",
                    "bookdown"))
@@
 
-In addition, there may be files that you generate and store locally in the folder during the compilation process. This is the case for some of the Plotly graphs below.
+In addition, there may be files that you generate and store locally in the folder during the compilation process (e.g., plotly graphs).
 
-Ideally, we can simply provide others with a `zip` folder that contains both our input files and our output files.
-Then it's possible to reproduce the process from managing/analyzing some raw data to producing the final scientific article.
+Ideally, we can share a `zip` folder that includes both our input and output files, allowing others to replicate the entire process from managing and analyzing raw data to producing the final scientific article.
 
-Below we always display the R code in the chunks that produce the output.
-In your paper you will normally only present outputs (e.g., tables, figures etc.) by choosing the chunk option "Show output only" in R Studio.
-The chunk commands itself are not displayed but they do matter for referencing etc.
-So simply orient yourself at the underlying `paper.rmd` file.
+# Code Chunk Options
+In the examples provided below, we always display the R code within the chunks that produce the respective output.
+In your own paper, you would typically present only the outputs such as tables and figures.
+To achieve this, you can choose the "Show output only" option for code chunks in R Studio.
+To configure the display options, locate the specific code chunk and click the gear icon in the top-right corner to open the chunk options menu.
+
+Alternatively, you can manually edit the code chunk options, which is a quicker approach.
+For example, to hide the underlying code and display only the output, you can use the option "echo=False" within the chunk options.
+
+The chunk options themselves are not displayed in the manuscript, but they matter for referencing etc. For more guidance, please refer to the underlying `paper.rmd` file.
 
@@
 ## Import
-```{r, echo=TRUE}
+```{r data-import, echo=TRUE}
 data <- read.csv("data.csv")
@@
 ## Putting your entire data into the .rmd file
-Applying the function `dput()` to an object gives you the code needed to reproduce that object.
-So you could paste that code into your `.rmd` file if you don't want to have extra data files.
-This makes sense were data files are small.
+By applying the function `dput()` to an object, you can obtain the code needed to reproduce that object.
 
-```{r}
+```{r dput-1}
 dput(data)
@@
 
-You can then insert the dput output in your `.rmd` as below.
+This code can be directly pasted into your `.rmd` file (see below), eliminating the need for separate data files. This approach is particularly useful when working with small data files.
 
-```{r eval=FALSE, include=TRUE}
+```{r dput-2, eval=FALSE, include=TRUE}
 data <- structure(list(X = 1:50, speed = c(4L, 4L, 7L, 7L, 8L, 9L, 10L, 
@@
 
-Table \@ref(tab1) shows summary stats of your data.^[To reference the table where you set the identifier in the stargazer function you only need to use the actual label, i.e., ´tab1´.] We normally use `stargazer()` [@hlavac2013stargazer] which offers extreme flexibility regarding table output (see `?stargazer`).
+Table \@ref(tab-1) shows summary stats of your data.^[To reference the table where you set the identifier in the stargazer function you only need to use the actual label, i.e., ´tab-1´.] Here, we use `stargazer()` [@hlavac2013stargazer], which offers extreme flexibility regarding table output (see `?stargazer`).
 
-```{r tab1, echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE, results="asis"}
+```{r tab-1, echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE, results="asis"}
 library(stargazer)
@@
           title = "Summary table with stargazer",
-          label="tab1", 
+          label="tab-1", 
           table.placement = "H", 
@@
 
-Table \@ref(tab2) shows the output for a regression table. Make sure you name all your models and explicitly refer to model names (M1, M2 etc.) in the text.
+Table \@ref(tab-2) shows the output for a regression table. Make sure you name all your models and explicitly refer to model names (M1, M2 etc.) in the text.
 
-```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE, results="asis"}
+```{r tab-2, echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE, results="asis"}
 library(stargazer)
@@
           title = "Regression table with stargazer",
-          label="tab2", 
+          label="tab-2", 
           table.placement = "H", 
@@
 Another great function is `kable()` (`knitr` package) in combination with `kableExtra`.
-Table \@ref(tab:tab3) provides an example.^[To reference the table produced by the chunk you need to add ´tab:´ to the chunk name, i.e., ´tab:tab3´.] Again you can modify so many things in both the `kable()` and the `kable_styling()` function.
+Table \@ref(tab:tab-3) provides an example.^[To reference the table produced by the chunk you need to add ´tab:´ to the chunk name, i.e., ´tab:tab-3´.] Again, you can modify various aspects of the table output using both the `kable()` and the `kable_styling()` functions.
 See [this overview](https://haozhu233.github.io/kableExtra/awesome_table_in_pdf.pdf) of all the kable stylings that are possible provided by the package author himself.
 
-```{r tab3, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, results="asis"}
+```{r tab-3, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, results="asis"}
 library(knitr)
@@
 
-Inserting figures can be slightly more complicated.
-Ideally, we would produce and insert them directly in the `.rmd` file.
-It's relatively simple to insert R base graphs as you can see in Figure \@ref(fig:fig-1))
+Ideally, we also produce and insert our figures directly in the `.rmd` file. Below, in Figure \@ref(fig:fig-1), we insert a R base graph.
 
@@
 
-But it turns out that it doesn't always work so well.
-
 ## ggplot2 graphs
-Same is true for ggplot2 as you can see in Figure \@ref(fig:fig-2).
+We can also generate and insert a ggplot2 graph, as demonstrated in Figure \@ref(fig:fig-2).
 
@@
 Reproduction reaches new heights when you work with inline code.
-For instance, you can automatize the display of certain coefficients within the text.
-An example is to include estimates, e.g., the coefficient of `dist` of the model we ran above.
+For instance, you can automate the display of certain coefficients within the text.
+An example is to include estimates, such as the coefficient of `dist` of the model we ran above.
 `r rinline("round(coef(model1)[2], 2)")` will insert the coefficient as follows: `r round(coef(model1)[2], 2)`.
-Or `r rinline("3 + 7")` will insert a `r 3 + 7` in the text.
-Inline code/results that depend on earlier objects in your document will automatically be updated once you change those objects.
+Similarly, using inlince code like `r rinline("3 + 7")` will insert a `r 3 + 7` in the text.
+Inline code and results that depend on earlier objects in your document will automatically be updated once you change those objects.
 For instance, imagine a reviewer asks you to omit certain observations from your sample.
-You can simply do so in the beginning of your code and push play subsequently..
-at time you might have to set `cache = FALSE` at the beginning so that all the code chunks are rerun.
-Researchers often avoid referring to results in-text etc.
-because you easily forget to change them when revising a manuscript.
-At the same it can make an article much more informative and easier to read, e.g., if you discuss a coefficient in the text you can directly show it in the section in which you discuss it.
+You can simply do so at the beginning of your code and then proceed.
+However, at times, you might need to set `cache = FALSE` at the beginning so that all the code chunks are rerun.
+Researchers often avoid referring to results in-text because it's easy to forget to change them when revising a manuscript.
+However, it can make an article much more informative and easier to read.
+For example, if you discuss a coefficient in the text, you can directly show it in the section where you discuss it.
 Inline code allows you to do just that.
-R Markdown allows you to that do so in a reproducible and automatized manner.
+R Markdown enables you to do so in a reproducible and automated manner.
 
@@
 * Keep all files of your project (that matter for producing the PDF) in one folder without subfolders.
-You can zip and directly upload that folder to the [Harvard dataverse](https://dataverse.harvard.edu/).
-* Make sure that filenames have a logic to them.
+Once you have done so, you can conveniently package the files by zipping the folder.
+This compressed file can then be directly uploaded to platforms such as the [Harvard dataverse](https://dataverse.harvard.edu/).
+In addition, it is beneficial to create a .Rproj file for your project.
+* Make sure that filenames are logical and meaningful.
     + Main file with text/code: "paper.rmd", "report.rmd" 
@@
 * Use the document outline in R studio (Ctrl + Shift + O) when you work with R Markdown.
-* Name rchunks according to what they do or produce:
+* Name code chunks according to what they do or produce:
     + "`fig-...`" for chunks producing figures
@@
     + "`recoding-...`" for chunks in which data is recoded
-* Ideally give chunks the labels of the figures/tables in the final publication, e.g., "`fig-1`" is the name of the chunk that produces Figure 1 in the final paper.
-* Use "really" informative variable names:
+* Ideally give code chunks the labels of the figures/tables in the final publication, e.g., "`fig-1`" is the name of the chunk that produces Figure 1 in the final paper.
+* Use informative variable names:
     + Q: What do you think does the variable *trstep* measure? It actually measures trust in the European parliament. 
         + How could we call this variable instead? Yes, `trust.european.parliament` which is longer but will probably be understood by another researcher. 
-    + If your setup is truly reproducible you will probably re-use the variable names that you generate as variable names in the tables you produce. Hence, there is an incentive to use good names.
+    + If your setup is reproducible, it's likely that you'll reuse the variable names you generate as column names in the tables you produce.
+Therefore, there's an incentive to use descriptive and meaningful variable names.
 * Use unique identifiers in the final document:
@@
 * Counting words
-    + Use adobe acrobat (commerical software) to convert your file to a word file.
-Then open in word and delete all the parts that shouldn't go into the word count.
-The word count is displayed in the lower right.
-    + Use an one of the online services to count your words (search for "pdf word count")
-* Appendix: You can change the numbering format for the appendix in the rmd file
+    + Knit your .Rmd to a Word (.docx) file, open it in Word, and delete any parts that should not be included in the word count.
+You can find the word count displayed in the lower right corner of the document.
+    + Use a online service to count your words (search for "pdf word count")
+* Appendix: You can change the numbering format for the appendix in the .Rmd file
     + What is still not possible in this document is to automatically have separate reference sections for paper and appendix.
@@
 
-```{r echo=FALSE}
+```{r session-info, echo=FALSE}
 print(sessionInfo(), local = FALSE)
@@
 
-```{r, ref.label=knitr::all_labels(),echo=TRUE,eval=FALSE}
+```{r appendix-code, ref.label=knitr::all_labels(),echo=TRUE,eval=FALSE}
 ```

### 2023-06-19 paper.tex
small edits.

@@
 \item
-  \ldots install the packages below using the code below (\protect\hyperlink{ref-plotly}{Sievert et al.
-2017}; \protect\hyperlink{ref-knitr3}{Xie 2014}, \protect\hyperlink{ref-knitr2}{2015}, \protect\hyperlink{ref-bookdown2}{2016}, \protect\hyperlink{ref-bookdown1}{2017}, \protect\hyperlink{ref-knitr1}{2018a}; \protect\hyperlink{ref-kableextra}{Zhu 2017}).
+  \ldots install the packages below using the code below (\protect\hyperlink{ref-knitr3}{Xie 2014}, \protect\hyperlink{ref-knitr2}{2015}, \protect\hyperlink{ref-bookdown2}{2016}, \protect\hyperlink{ref-bookdown1}{2017}, \protect\hyperlink{ref-knitr1}{2018a}; \protect\hyperlink{ref-kableextra}{Zhu 2017}).
 \end{itemize}
@@
 \FunctionTok{install.packages}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\StringTok{"rmarkdown"}\NormalTok{, }\StringTok{"knitr"}\NormalTok{, }\StringTok{"kableExtra"}\NormalTok{,}
-                   \StringTok{"stargazer"}\NormalTok{, }\StringTok{"plotly"}\NormalTok{, }\StringTok{"knitr"}\NormalTok{,}
+                   \StringTok{"stargazer"}\NormalTok{, }\StringTok{"knitr"}\NormalTok{,}
                    \StringTok{"bookdown"}\NormalTok{))}
@@
 
-In addition, there may be files that you generate and store locally in the folder during the compilation process. This is the case for some of the Plotly graphs below.
+In addition, there may be files that you generate and store locally in the folder during the compilation process (e.g., plotly graphs).
 
-Ideally, we can simply provide others with a \texttt{zip} folder that contains both our input files and our output files.
-Then it's possible to reproduce the process from managing/analyzing some raw data to producing the final scientific article.
+Ideally, we can share a \texttt{zip} folder that includes both our input and output files, allowing others to replicate the entire process from managing and analyzing raw data to producing the final scientific article.
 
-Below we always display the R code in the chunks that produce the output.
-In your paper you will normally only present outputs (e.g., tables, figures etc.) by choosing the chunk option ``Show output only'' in R Studio.
-The chunk commands itself are not displayed but they do matter for referencing etc.
-So simply orient yourself at the underlying \texttt{paper.rmd} file.
+\hypertarget{code-chunk-options}{%
+\section{Code Chunk Options}\label{code-chunk-options}}
+
+In the examples provided below, we always display the R code within the chunks that produce the respective output.
+In your own paper, you would typically present only the outputs such as tables and figures.
+To achieve this, you can choose the ``Show output only'' option for code chunks in R Studio.
+To configure the display options, locate the specific code chunk and click the gear icon in the top-right corner to open the chunk options menu.
+
+Alternatively, you can manually edit the code chunk options, which is a quicker approach.
+For example, to hide the underlying code and display only the output, you can use the option ``echo=False'' within the chunk options.
+
+The chunk options themselves are not displayed in the manuscript, but they matter for referencing etc. For more guidance, please refer to the underlying \texttt{paper.rmd} file.
 
@@
 
-Applying the function \texttt{dput()} to an object gives you the code needed to reproduce that object.
-So you could paste that code into your \texttt{.rmd} file if you don't want to have extra data files.
-This makes sense were data files are small.
+By applying the function \texttt{dput()} to an object, you can obtain the code needed to reproduce that object.
 
@@
 
-You can then insert the dput output in your \texttt{.rmd} as below.
+This code can be directly pasted into your \texttt{.rmd} file (see below), eliminating the need for separate data files. This approach is particularly useful when working with small data files.
 
@@
 
-Table \ref{tab1} shows summary stats of your data.\footnote{To reference the table where you set the identifier in the stargazer function you only need to use the actual label, i.e., ´tab1´.} We normally use \texttt{stargazer()} (\protect\hyperlink{ref-hlavac2013stargazer}{Hlavac 2013}) which offers extreme flexibility regarding table output (see \texttt{?stargazer}).
+Table \ref{tab-1} shows summary stats of your data.\footnote{To reference the table where you set the identifier in the stargazer function you only need to use the actual label, i.e., ´tab-1´.} Here, we use \texttt{stargazer()} (\protect\hyperlink{ref-hlavac2013stargazer}{Hlavac 2013}), which offers extreme flexibility regarding table output (see \texttt{?stargazer}).
 
@@
           \AttributeTok{title =} \StringTok{"Summary table with stargazer"}\NormalTok{,}
-          \AttributeTok{label=}\StringTok{"tab1"}\NormalTok{, }
+          \AttributeTok{label=}\StringTok{"tab{-}1"}\NormalTok{, }
           \AttributeTok{table.placement =} \StringTok{"H"}\NormalTok{, }
@@
   \caption{Summary table with stargazer} 
-  \label{tab1} 
+  \label{tab-1} 
 \begin{tabular}{@{\extracolsep{5pt}}lccccc} 
@@
 
-Table \ref{tab2} shows the output for a regression table. Make sure you name all your models and explicitly refer to model names (M1, M2 etc.) in the text.
+Table \ref{tab-2} shows the output for a regression table. Make sure you name all your models and explicitly refer to model names (M1, M2 etc.) in the text.
 
@@
           \AttributeTok{title =} \StringTok{"Regression table with stargazer"}\NormalTok{,}
-          \AttributeTok{label=}\StringTok{"tab2"}\NormalTok{, }
+          \AttributeTok{label=}\StringTok{"tab{-}2"}\NormalTok{, }
           \AttributeTok{table.placement =} \StringTok{"H"}\NormalTok{, }
@@
   \caption{Regression table with stargazer} 
-  \label{tab2} 
+  \label{tab-2} 
 \begin{tabular}{@{\extracolsep{5pt}}lccc} 
@@
 Another great function is \texttt{kable()} (\texttt{knitr} package) in combination with \texttt{kableExtra}.
-Table \ref{tab:tab3} provides an example.\footnote{To reference the table produced by the chunk you need to add ´tab:´ to the chunk name, i.e., ´tab:tab3´.} Again you can modify so many things in both the \texttt{kable()} and the \texttt{kable\_styling()} function.
+Table \ref{tab:tab-3} provides an example.\footnote{To reference the table produced by the chunk you need to add ´tab:´ to the chunk name, i.e., ´tab:tab-3´.} Again, you can modify various aspects of the table output using both the \texttt{kable()} and the \texttt{kable\_styling()} functions.
 See \href{https://haozhu233.github.io/kableExtra/awesome_table_in_pdf.pdf}{this overview} of all the kable stylings that are possible provided by the package author himself.
@@
 
-\caption{\label{tab:tab3}Table with kable() and kablestyling()}
+\caption{\label{tab:tab-3}Table with kable() and kablestyling()}
 \centering
@@
 
-Inserting figures can be slightly more complicated.
-Ideally, we would produce and insert them directly in the \texttt{.rmd} file.
-It's relatively simple to insert R base graphs as you can see in Figure \ref{fig:fig-1})
+Ideally, we also produce and insert our figures directly in the \texttt{.rmd} file. Below, in Figure \ref{fig:fig-1}, we insert a R base graph.
 
@@
 
-But it turns out that it doesn't always work so well.
-
 \hypertarget{ggplot2-graphs}{%
@@
 
-Same is true for ggplot2 as you can see in Figure \ref{fig:fig-2}.
+We can also generate and insert a ggplot2 graph, as demonstrated in Figure \ref{fig:fig-2}.
 
@@
 Reproduction reaches new heights when you work with inline code.
-For instance, you can automatize the display of certain coefficients within the text.
-An example is to include estimates, e.g., the coefficient of \texttt{dist} of the model we ran above.
+For instance, you can automate the display of certain coefficients within the text.
+An example is to include estimates, such as the coefficient of \texttt{dist} of the model we ran above.
 \texttt{\textasciigrave{}r\ round(coef(model1){[}2{]},\ 2)\textasciigrave{}} will insert the coefficient as follows: 0.17.
-Or \texttt{\textasciigrave{}r\ 3\ +\ 7\textasciigrave{}} will insert a 10 in the text.\\
-Inline code/results that depend on earlier objects in your document will automatically be updated once you change those objects.
+Similarly, using inlince code like \texttt{\textasciigrave{}r\ 3\ +\ 7\textasciigrave{}} will insert a 10 in the text.\\
+Inline code and results that depend on earlier objects in your document will automatically be updated once you change those objects.
 For instance, imagine a reviewer asks you to omit certain observations from your sample.
-You can simply do so in the beginning of your code and push play subsequently..
-at time you might have to set \texttt{cache\ =\ FALSE} at the beginning so that all the code chunks are rerun.\\
-Researchers often avoid referring to results in-text etc.
-because you easily forget to change them when revising a manuscript.
-At the same it can make an article much more informative and easier to read, e.g., if you discuss a coefficient in the text you can directly show it in the section in which you discuss it.
+You can simply do so at the beginning of your code and then proceed.
+However, at times, you might need to set \texttt{cache\ =\ FALSE} at the beginning so that all the code chunks are rerun.\\
+Researchers often avoid referring to results in-text because it's easy to forget to change them when revising a manuscript.
+However, it can make an article much more informative and easier to read.
+For example, if you discuss a coefficient in the text, you can directly show it in the section where you discuss it.
 Inline code allows you to do just that.
-R Markdown allows you to that do so in a reproducible and automatized manner.
+R Markdown enables you to do so in a reproducible and automated manner.
 
@@
   Keep all files of your project (that matter for producing the PDF) in one folder without subfolders.
-You can zip and directly upload that folder to the \href{https://dataverse.harvard.edu/}{Harvard dataverse}.
+Once you have done so, you can conveniently package the files by zipping the folder.
+This compressed file can then be directly uploaded to platforms such as the \href{https://dataverse.harvard.edu/}{Harvard dataverse}.
+In addition, it is beneficial to create a .Rproj file for your project.
 \item
-  Make sure that filenames have a logic to them.
+  Make sure that filenames are logical and meaningful.
 
@@
 \item
-  Name rchunks according to what they do or produce:
+  Name code chunks according to what they do or produce:
 
@@
 \item
-  Ideally give chunks the labels of the figures/tables in the final publication, e.g., ``\texttt{fig-1}'' is the name of the chunk that produces Figure 1 in the final paper.
+  Ideally give code chunks the labels of the figures/tables in the final publication, e.g., ``\texttt{fig-1}'' is the name of the chunk that produces Figure 1 in the final paper.
 \item
-  Use ``really'' informative variable names:
+  Use informative variable names:
 
@@
   \item
-    If your setup is truly reproducible you will probably re-use the variable names that you generate as variable names in the tables you produce. Hence, there is an incentive to use good names.
+    If your setup is reproducible, it's likely that you'll reuse the variable names you generate as column names in the tables you produce.
+Therefore, there's an incentive to use descriptive and meaningful variable names.
   \end{itemize}
@@
   \item
-    Use adobe acrobat (commerical software) to convert your file to a word file.
-Then open in word and delete all the parts that shouldn't go into the word count.
-The word count is displayed in the lower right.
+    Knit your .Rmd to a Word (.docx) file, open it in Word, and delete any parts that should not be included in the word count.
+You can find the word count displayed in the lower right corner of the document.
   \item
-    Use an one of the online services to count your words (search for ``pdf word count'')
+    Use a online service to count your words (search for ``pdf word count'')
   \end{itemize}
 \item
-  Appendix: You can change the numbering format for the appendix in the rmd file
+  Appendix: You can change the numbering format for the appendix in the .Rmd file
 
@@
 RStudio Team. 2015. \emph{\href{http://www.rstudio.com/}{RStudio: Integrated Development Environment for r}}. Boston, MA: RStudio, Inc.
-
-\leavevmode\vadjust pre{\hypertarget{ref-plotly}{}}%
-Sievert, Carson, Chris Parmer, Toby Hocking, Scott Chamberlain, Karthik Ram, Marianne Corvellec, and Pedro Despouy.
-2017.
-\emph{\href{https://CRAN.R-project.org/package=plotly}{Plotly: Create Interactive Web Graphics via 'Plotly.js'}}.
 
@@
 \NormalTok{knitr}\SpecialCharTok{::}\NormalTok{opts\_chunk}\SpecialCharTok{$}\FunctionTok{set}\NormalTok{(}\AttributeTok{cache =} \ConstantTok{FALSE}\NormalTok{)}
-\CommentTok{\# Use chache = TRUE if you want to speed up compilation}
-
+\CommentTok{\# Use cache = TRUE if you want to speed up compilation}
 \CommentTok{\# A function to allow for showing some of the inline code}
